### 2022-06-07 presentation/refining_relationships.tex
added presentation

\documentclass[10pt]{beamer}
\usetheme[progressbar=frametitle]{metropolis}

\usepackage [autostyle, english = american]{csquotes}
\DeclareFontShape{OT1}{cmss}{b}{n}{<->ssub * cmss/bx/n}{} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm} 
\usepackage{multicol}

\MakeOuterQuote{"}
\newcommand{\imp}[1]{\textbf{\color{cyan}#1}}

%---------------------------------------------------
% Title

\title{Refining Character Relationships in a Textual Narrative using Embeddings of Interactions}
\date{}
\author{Guillaume Guex}
\institute{University of Lausanne}

\begin{document}

	%------------------------------------------------------------------

	\maketitle

	%------------------------------------------------------------------

	\begin{frame}{Table of contents}
		\setbeamertemplate{section in toc}[sections numbered]
		\tableofcontents%[hideallsubsections]
	\end{frame}

	%------------------------------------------------------------------

	\section[Introduction]{Introduction}

	%------------------------------------------------------------------

	\begin{frame}{The construction of a character network}
		The construction of a character network takes generally 3 steps \cite{labatut_extraction_2019}:
		\begin{itemize}
			\item Identification of \imp{characters} 
			\item Detection of \imp{interactions}
			\item Construction of the \imp{graph}
		\end{itemize}
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{The construction of a character network}
		When dealing with \imp{textual narrative}, a frequently used method is to count \imp{character co-occurrences} in \imp{textual units} (e.g., \cite{elsner_character-based_2012, rochat_analyse_2014}). \\
		\vspace{-0.4cm}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				\begin{figure}
					\centering
					\includegraphics[width=1.4\textwidth]{img/textual_units.png}
				\end{figure}
			\end{column}
			\begin{column}{0.5\textwidth}
				\vspace{-4cm}
				\begin{table}
					\centering
					\scriptsize
					\begin{tabular}{|c|c|c|} 
						\hline
						Character 1 & Character 2 & Co-occurrences \\ 
						\hline
						Cosette & Marius & 1 \\
						Cosette & Valjean & 2 \\ 
						Fantine & Javert & 1 \\
						Fantine & Valjean & 1 \\
						Javert & Valjean & 1 \\
						Marius & Valjean & 1 \\
						\hline
					\end{tabular}
				\end{table}
				\begin{figure}
					\centering
					\includegraphics[width=0.8\textwidth]{img/mini_graph.png}
				\end{figure}
			\end{column}
		\end{columns}
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{Dataset}
		In this context, the \imp{dataset} used to construct the character network has the following form
		\begin{figure}
			\centering
			\includegraphics[width=\textwidth]{img/data_table.png}
		\end{figure}
		However, apart from a few exceptions \cite{nalisnick_character--character_2013, trovati_towards_2014, min_modeling_2019}, the content of the \imp{text column} is not used. \imp{Edges in the resulting graph aggregate blindly various kind of interactions}.
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{Approaches}
		In this presentation, we propose to \imp{refine character relationships} by using the \imp{textual data}. Quantities of approaches can be undertaken, but we focus on:
		\begin{itemize}
			\item \imp{Bag-of-paths} approaches, a corpus is represented by an \imp{unit-term matrix}. \\
			\vspace{0.3cm}
			\begin{figure}
				\centering
				\includegraphics[width=0.8\textwidth]{img/unit_term.png}
			\end{figure}
			\item \imp{Embeddings of textual units}. The unit-term matrix is used to construct \imp{vectors} representing units. 
			\item \imp{Embeddings of character relationships}, which derives from the embedding of textual unit.
		\end{itemize}
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{Approaches}
		More specifically, three approaches are made:
		\begin{itemize}
			\item \imp{Correspondence Analysis (CA)}.
			\item \imp{Pre-trained Word Embeddings (WE)}.
			\item "Topic" vectors from \imp{Non-negative Matrix Factorization (NMF)}.
		\end{itemize}
	\end{frame}

	%------------------------------------------------------------------

	\section[Correspondence Analysis (CA)]{Correspondence Analysis (CA)}

	%------------------------------------------------------------------

	\begin{frame}{Principles}
		Correspondence Analysis is the natural tool for analyzing textual resources if data are organized in a $(n \times p)$ \imp{document-term matrix} \cite{lebart_analyse_2019} (here, documents are our textual units). It gives:
		\begin{itemize}
			\item $\min(n, p) - 1$ \imp{factorial axes}, by decreasing order of importance, which can be interpreted as latent variables.
			\item \imp{Coordinates of each document} along these factors, where proximity can be interpreted as similar profile in term of words.
			\item \imp{Coordinates of each word} along the same factors, where proximity can be interpreted as similar profile in term of documents.
			\item \imp{Affinities between a document and a term}, which is computed by the \imp{scalar product} between their vectors.
		\end{itemize}
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{Principles}
		If we plot units and words on the first two axes, we get the usual \imp{biplot}:
		\begin{figure}
			\centering
			\includegraphics[width=\textwidth]{img/biplot.png}
		\end{figure}
	\end{frame}

	%------------------------------------------------------------------

	\begin{frame}{Relationship embeddings}
		If we plot units and words on the first two axes, we get the usual \imp{biplot}:
		\begin{figure}
			\centering
			\includegraphics[width=\textwidth]{img/biplot.png}
		\end{figure}
	\end{frame}

	%------------------------------------------------------------------

	\appendix

	\begin{frame}[shrink=40, fragile]{References}
		\begin{multicols}{2}
			\bibliographystyle{apalike}
			\bibliography{charnet}
		\end{multicols}
	\end{frame}

\end{document}

### 2022-06-08 2.0_CA_lesMiserables.py
presentation code

@@ -1,5 +1,3 @@
-import numpy as np
-
 from local_functions import *
 
 # -------------------------------
@@ -17,11 +15,11 @@ min_word_frequency = 20
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 3
+min_occurrences = 1
 # Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
+meta_for_occurrences = "tome"
 # Regularization parameter (0.1)
-regularization_parameter = 0.1
+regularization_parameter = 1
 
 # -------------------------------
 #  Loading
@@ -130,8 +128,8 @@ axes_vs_occurrences = axes_vs_occurrences.reindex(sorted(axes_vs_occurrences.col
 # ---- Explore the desired relationships
 
 # Objects to explore
-object_names = ["Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean", "Marius-Valjean", "Javert",
-                "Javert-Valjean", "Myriel", "Myriel-Valjean"]
+object_names = ["T1", "T2", "T3", "T4", "T5", "Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean",
+                "Marius-Valjean", "Javert", "Javert-Valjean", "Myriel", "Myriel-Valjean"]
 if meta_for_occurrences is not None:
     separation_name = list(set(corpus.meta_variables[meta_for_occurrences]))
     for i in range(len(separation_name)):
@@ -147,7 +145,64 @@ for obj in object_names:
 A_occurrence = words_vs_occurrences[present_object_names]
 A_regression = words_vs_regressions[present_object_names]
 
-# ---- Plot
+occ_v_word = pd.DataFrame(index=range(10))
+for object_name in present_object_names:
+    object_largest = A_occurrence[object_name].nlargest()
+    object_smallest = A_occurrence[object_name].nsmallest()
+    object_col = []
+    for i in range(object_largest.shape[0]):
+        object_col.append(f"{object_largest.index[i]} ({np.round(object_largest.iloc[i], 2)})")
+    for i in range(object_smallest.shape[0]):
+        object_col.append(f"{object_smallest.index[i]} ({np.round(object_smallest.iloc[i], 2)})")
+    object_df = pd.DataFrame({object_name: object_col})
+    occ_v_word = pd.concat([occ_v_word, object_df], axis=1)
[…]

### 2022-06-08 3.1_WV_NotreDame.py

@@ -6,9 +6,9 @@ from gensim.models import KeyedVectors
 # -------------------------------
 
 # Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+corpus_tsv_path = "corpora/NotreDame_fr/NotreDame.tsv"
 # Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
 # Word vectors to use
 word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
 # Set aggregation level (None for each line)
@@ -18,7 +18,7 @@ min_word_frequency = 5
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 3
+min_occurrences = 1
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter
@@ -134,7 +134,6 @@ first_eigen_vec = scipy.sparse.linalg.svds(unit_coord.T, 1)[0]
 first_eigen_residual = first_eigen_vec @ first_eigen_vec.T @ unit_coord.T
 unit_coord = unit_coord - first_eigen_residual.T
 
-
 # ----------------------------------------
 # ---- Occurrences vectors
 # ----------------------------------------
@@ -164,8 +163,9 @@ words_vs_regressions = words_vs_regressions.reindex(sorted(words_vs_regressions.
 # ---- Explore the desired relationships
 
 # Objects to explore
-object_names = ["Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean", "Marius-Valjean", "Javert",
-                "Javert-Valjean", "Myriel", "Myriel-Valjean"]
+object_names = ["Esmeralda", "Claude Frollo-Esmeralda", "Esmeralda-Quasimodo", "Claude Frollo", "Quasimodo",
+                "Gringoire", "Esmeralda-Gringoire", "Châteaupers-Emeralada", "Châteaupers-Claude Frollo",
+                "Châteaupers-Quasimodo", "Claude Frollo-Quasimodo"]
 object_names_tome = ["1", "2", "3", "4", "5"]
 for i in range(5):
[…]

### 2022-06-08 4.0_NMF_lesMiserables.py

@@ -1,4 +1,4 @@
-from sklearn.decomposition import NMF
+from sklearn.decomposition import NMF, LatentDirichletAllocation
 from sklearn.feature_extraction.text import TfidfVectorizer
 from local_functions import *
 
@@ -12,16 +12,12 @@ corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
 aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
 # Set aggregation level (None for each line)
 aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 20
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 3
+min_occurrences = 5
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
 
 # -------------------------------
 #  Loading
@@ -55,9 +51,6 @@ corpus.aggregate_on(aggregation_level)
 # Construct the unit-term matrix and remove rare words
 corpus.build_units_words(TfidfVectorizer(max_df=0.95, min_df=2, max_features=1000, stop_words=used_stop_words))
 
-# Make a threshold for the minimum vocabulary and remove units without words
-#corpus.remove_words_with_frequency(min_word_frequency)
-
 # Remove characters from words
 corpus.remove_words(character_names)
 
@@ -73,7 +66,7 @@ corpus.update_occurrences_across_meta(meta_for_occurrences)
 
 # Make sure no units are empty
 corpus.remove_units_without_words()
-corpus.remove_units_without_occurrences()
+#corpus.remove_units_without_occurrences()
 corpus.remove_occurrences_with_frequency(1e-10)
 corpus.remove_words_with_frequency(1e-10)
 
@@ -85,14 +78,16 @@ tfidf_sums = corpus.units_words.sum(axis=1).to_numpy()
 # -------------------------------
 
 # --- Make the NMF model
-n_groups = 10
+n_groups = 20
 
 nmf_model = NMF(n_components=n_groups, init="nndsvd", max_iter=2000)
+#nmf_model = LatentDirichletAllocation(n_components=n_groups)
 nmf_model.fit(corpus.units_words.to_numpy())
 
 # Getting components for units and words
[…]

### 2022-06-08 local_functions.py

@@ -216,11 +216,13 @@ class CharacterCorpus:
         meta_columns = self.meta_variables.columns
         # If the name is in the columns, do the update
         if meta_name in meta_columns:
-            # Get dummies for tomes
+            # Get dummies for metavariable
             dummies = pd.get_dummies(self.meta_variables[meta_name], columns=[meta_name])
 
             # Build new occurrences
             new_occurrences = pd.DataFrame(index=self.occurrences.index)
+            new_occurrences = pd.concat([new_occurrences, dummies], axis=1)
+            new_occurrences.columns = [f"T{col_name}" for col_name in new_occurrences.columns]
             for dummy in dummies.columns:
                 # Get the presence of occurrences relative to dummy, transform them, rename them
                 dummy_occurrences = self.occurrences * np.outer(dummies[dummy].to_numpy(),
@@ -572,7 +574,6 @@ def build_logistic_regression_vectors(occurrences, unit_prob, unit_sizes, reg_ty
     :param unit_prob: the (units x dim) matrix containing probabilities vectors with dim dimensions.
     :param unit_sizes: the (units) vector containing unit weights.
     :param reg_type: the type of regression, between "multinomial", "auto", or "ovr" (default = "multinomial")
-    :param regularization_parameter: the regularization parameter for the regression (default = 1)
     :return: regression_vectors: a (objects x dim) dataframe containing regression vectors of objects.
     """
 
@@ -580,7 +581,7 @@ def build_logistic_regression_vectors(occurrences, unit_prob, unit_sizes, reg_ty
     norm_unit_prob = unit_prob / unit_prob.sum(axis=1).reshape(-1, 1)
 
     # Make the regression model
-    reg = linear_model.LogisticRegression(multi_class=reg_type, max_iter=1e4)
+    reg = linear_model.LogisticRegression(multi_class=reg_type, max_iter=2000)
 
     # Construct the dataset for regression
     constructed_unit_size = []

### 2022-06-08 presentation/refining_relationships.tex
presentation code

@@
 \title{Refining Character Relationships in a Textual Narrative using Embeddings of Interactions}
+\subtitle{With case studies on \emph{Les Misérables}}
 \date{}
@@
 	\begin{frame}{The construction of a character network}
-		When dealing with \imp{textual narrative}, a frequently used method is to count \imp{character co-occurrences} in \imp{textual units} (e.g., \cite{elsner_character-based_2012, rochat_analyse_2014}).
+		When dealing with \imp{textual narratives}, a frequently used method is to count \imp{character co-occurrences} in predefined \imp{textual units} \\(see, e.g., \cite{elsner_character-based_2012, rochat_analyse_2014}).
 \\
@@
 			\item \imp{Embeddings of textual units}. The unit-term matrix is used to construct \imp{vectors} representing units. 
-			\item \imp{Embeddings of character relationships}, which derives from the embedding of textual unit.
+			\item \imp{Embeddings of characters and relationships}, which derive from the embedding of textual units.
 		\end{itemize}
@@
 	\begin{frame}{Approaches}
-		More specifically, three approaches are made:
+		More specifically, two types "embeddings" are studied:
 		\begin{itemize}
 			\item \imp{Correspondence Analysis (CA)}.
-			\item \imp{Pre-trained Word Embeddings (WE)}.
-			\item "Topic" vectors from \imp{Non-negative Matrix Factorization (NMF)}.
+			\item \imp{"Topic Modeling vectors"} build from \imp{Non-negative Matrix Factorization (NMF)}.
+		\end{itemize}
+		With two methods for constructing character/relationship vectors:
+		\begin{itemize}
+			\item \imp{Centroids}.
+			\item \imp{Regression coefficients}.
 		\end{itemize}
@@
 
-	\section[Correspondence Analysis (CA)]{Correspondence Analysis (CA)}
+	\section[Correspondence Analysis (CA) - centroids]{Correspondence Analysis (CA) - centroids}
 
@@
 
-	\begin{frame}{Relationship embeddings}
-		If we plot units and words on the first two axes, we get the usual \imp{biplot}:
+	\begin{frame}{Characters embeddings - centroids}
+		The \imp{textual units} have natural embedding in CA. For characters, the most intuitive idea is to compute them as \imp{centroids} of units where they appear.
 		\begin{figure}
 			\centering
-			\includegraphics[width=\textwidth]{img/biplot.png}
+			\includegraphics[width=\textwidth]{img/char_embeddings.png}
 		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - centroids}
+		The same idea can be applied to \imp{relationships}, In fact, in our data table, we can extend our table to include \imp{interactions}.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/occurences_data.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - centroids}
+		This leads us with embeddings of \imp{relationships}:
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/occ_embeddings.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Character/relationship embeddings - usages}
+		What can we do with these character/relationship embeddings ? As they are in the same space as textual units, we can: 
+		\begin{itemize}
+			\item Get the Euclidean distance between \imp{relationships}.
+			\item Get the Euclidean distance between \imp{relationships and the textual units}.
+			\item Observe their values on the different \imp{factorial axes}. 
+			\item Observe similarities (scalar product) between \imp{relationships and words (or group of words)}.
+		\end{itemize}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Characters/relationships vs axes}
+		Sometimes, \imp{factorial axes can be interpreted with coordinates of the words}. \imp{Positions of characters/relationships on this axis} reflect their affinity with this particular scale:
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/relationship_vs_axes.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Characters/relationships vs words}
+		We can also get the \imp{similarities between characters/relationships vs words} with the help of the \imp{scalar product}:
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.8\textwidth]{img/relationships_vs_words.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Words vs characters/relationships}
+		By transposing the previous table, particular words (or group of words, i.e. a query) can give a ranking of characters/relationships:
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/word_vs_occ.png}
+		\end{figure}
+		In this case, the centroid method seems to show its limit.
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\section[Correspondence Analysis (CA) - regressions]{Correspondence Analysis (CA) - regressions}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - 1st idea problems}
+		In fact, building these character/relationship vectors as \imp{centroids} is like considering them as \imp{additional variables} in the CA.
+It leads to \imp{additive relationships}, i.e., for a character $c$
+		$$
+		v_{c} = \sum_{d \in \text{characters}} v_{cd}
+		$$
+		where $v_{cd}$ is the vector of relationship between $c$ and $d$, and $v_{cc}$ is defined as the centroid of units where $c$ is alone. This means
+		\begin{itemize}
+			\item If a character have \imp{contrasted relationships}, its vector might represent it poorly.
+			\item If \imp{two characters are often together}, their respective specificities might be hidden.
+			\item If \imp{two relationships are often together}, their respective specificities might be hidden.
+		\end{itemize}
+		\emph{Are we the sum of our relationships (+ ourself alone)?} 
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - 2nd idea}
+		A way to avoid this problem, is to consider that
+		\begin{itemize}
+			\item The appearance of character \imp{$c$ alone} gives a particular profile to units.
+			\item The appearance of character \imp{$d$ alone} gives another profile to units.
+			\item The appearance of character \imp{$c$ and $d$} might give a totally \imp{different profile} to units.
+		\end{itemize}
+		We can use a \imp{regression model with interaction}.
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - 2nd idea}
+		Let $(y_1, \ldots, y_n)$ be the coordinates of the $n$ units on the \imp{first factorial axis}, $\delta(c)$ the indicator variable of character $c$ presence, and $\delta(c,d)$ the indicator variable of relationship $c,d$ presence.
+We can fit the model:
+		$$
+		\hat{y} = \beta_0 + \sum_{c} \beta_c \delta(c) + \sum_{c,d} \beta_{cd} \delta(c,d)
+		$$
+		with a \imp{Ridge (L2) regularization term}, parameterized by $\lambda$, to avoid overfitting.
+		\begin{itemize}
+		\item The first coordinate of a \imp{character-vector $c$ is given by $\beta_c$}.
+		\item The first coordinate of a \imp{relationship-vector $(c,d)$ is given by $\beta_{cd}$}.
+		\end{itemize}
+		We do a \imp{similar regression on all axis to get vectors}.
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - 2nd idea}
+		Resulting coordinates of opposite characters point at \imp{different directions}:
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/reg_embeddings.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Relationship embeddings - 2nd idea}
+		The \imp{regularizing parameter $\lambda$} has an interesting effect on resulting vectors:
+		\begin{itemize}
+			\item When $\lambda$ is \imp{high}, the \imp{vectors are similar to centroids} (with a different scaling).
+			\item When $\lambda$ is \imp{low}, the solution focuses on \imp{very specific, small parts of the text} to define characters and relationships.
+			\item An \imp{average} $\lambda$ (but which one?) is able to \imp{highlight character/relationship specificities relatively to corpus size.}
+		\end{itemize}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Characters/relationships vs words - comparisons}
+		With regressions, there is more \imp{variety} in words defining characters/relationships:
+		\vspace{-0.2cm}
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.7\textwidth]{img/reg_vs_word.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Words vs characters/relationships - regression}
+		And relationships according to words are more coherent:
+		\vspace{-0.2cm}
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/word_vs_reg.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Words vs characters/relationships - regression}
+		This method give also good results if regressors are constructed according to a \imp{narrative timeline} (here, the \emph{Tomes}):
+		\vspace{-0.2cm}
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/reg_vs_word_long.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{CA quick summary}
+		To recap the CA method:
+		\begin{itemize}
+			\item \imp{Words and units vectors} are obtained from the \imp{unit-term matrix}.
+			\item \imp{Characters/Relationships vectors} are obtained with 2 different methods:
+			\begin{itemize}
+				\item \imp{Centroids}
+				\item \imp{Regressions}
+			\end{itemize}
+			\item These characters/relationships vectors can be \imp{explored} regarding:
+			\begin{itemize}
+				\item \imp{Axes}
+				\item \imp{Words} (or group of words)
+			\end{itemize}
+			\item Moreover, we can explore characters/relationships vectors according to a \imp{Timeline}.
+		\end{itemize}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\section[Pre-trained Word Embeddings]{Pre-trained Word Embeddings}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Pre-trained Word Embeddings - justifications}
+
+		CA is a \imp{constrastive} analysis: the units, words, and characters/relationships are constructed \imp{relatively to the author style and subject}. \\
+		\vspace{0.4cm}
+		It can be interesting to get insights on \imp{how characters/relationships are perceived in an absolute referential}. \\
+		\vspace{0.4cm}
+		An idea to overcome this problem is to embed units/characters/relationships in a \imp{absolute referential} such as a \imp{pre-trained word embedding space}.
+
 	\end{frame}

### 2022-06-08 2.0_CA_lesMiserables.py
presentation code

@@ -201,7 +201,7 @@ word_vs_reg.to_csv("word_vs_reg.csv")
 
 
 # -------------------------------
-#  Analyses
+#  Plots
 # -------------------------------
 
 # Selection of axes

### 2022-06-08 2.0_CA_lesMiserables_withNetwork.py

@@ -1,0 +1,189 @@
+from local_functions import *
+import pickle
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 1
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter (0.1)
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Get the main characters
+main_char_idx = np.where((corpus.occurrences >= min_occurrences).to_numpy().sum(axis=0) > 10)
+main_char_names = np.array(corpus.occurrences.columns)[main_char_idx]
[…]

### 2022-06-08 local_functions.py

@@ -617,29 +617,12 @@ def compute_cosine(vectors_1, vectors_2):
     return norm_vectors_1 @ norm_vectors_2.T
 
 
-def display_char_network(interact_list, edge_polarity_list, edge_weight_list, color="polarity", width="weight",
-                         width_rank=False, node_min_width=50, node_max_width=1000, edge_min_width=0.2, edge_max_width=5,
-                         string_strength="weight", min_alpha=0.5, max_alpha=1, cmap=plt.cm.coolwarm,
-                         node_pos=None):
+def display_char_o_network(interact_list, edge_polarity_list, edge_weight_list, color="polarity", width="weight",
+                           width_rank=False, node_min_width=50, node_max_width=1000, edge_min_width=0.2, edge_max_width=5,
+                           string_strength="weight", min_alpha=0.5, max_alpha=1, cmap=plt.cm.coolwarm,
+                           node_pos=None, font_size=10, arrowsize=10):
     """
     A function to diplay a graph between character interactions
-
-    :param width_rank:
-    :param min_alpha:
-    :param interact_list:
-    :param edge_polarity_list:
-    :param edge_weight_list:
-    :param color:
-    :param width:
-    :param node_min_width:
-    :param node_max_width:
-    :param edge_min_width:
-    :param edge_max_width:
-    :param string_strength:
-    :param max_alpha:
-    :param cmap:
-    :param node_pos:
-    :return:
     """
 
     # Make sure quantities are in numpy array
@@ -735,7 +718,7 @@ def display_char_network(interact_list, edge_polarity_list, edge_weight_list, co
                            vmax=max(edge_color_list),
                            alpha=0.8)
     # Draw labels
-    nx.draw_networkx_labels(graph, pos=node_pos, font_size=25, font_weight="bold")
+    nx.draw_networkx_labels(graph, pos=node_pos, font_size=font_size, font_weight="bold")
     # Create the edges
     edges = nx.draw_networkx_edges(graph,
                                    pos=node_pos,
@@ -748,7 +731,133 @@ def display_char_network(interact_list, edge_polarity_list, edge_weight_list, co
                                    edge_vmax=max(edge_color_list),
                                    alpha=edge_alpha_list,
                                    connectionstyle="arc3,rad=0.2",
-                                   arrowsize=40)
+                                   arrowsize=arrowsize)
+
+    pc = PatchCollection(edges, cmap=cmap)
+    pc.set_array(edge_color_list)
+
+    ax = plt.gca()
[…]

### 2022-06-08 old_scripts/4_wv_test.py

@@ -15,7 +15,7 @@ from local_functions import display_char_network
 # -------------------------------
 
 # Corpus tsv path
-corpus_tsv_path = "../corpora/Romeo&Juliet/Romeo&Juliet_old.tsv"
+corpus_tsv_path = "corpora/Romeo&Juliet/Romeo&Juliet_old.tsv"
 # File for node position
 corpus_node_pos = "corpora/Romeo&Juliet.pkl"
 # Global or per_act

### 2022-06-08 presentation/refining_relationships.tex
presentation over

@@
 \usepackage{multicol}
+\usepackage{hyperref}
 
@@
 
-\title{Refining Character Relationships in a Textual Narrative using Embeddings of Interactions}
+\title{Refining Character Relationships using Embeddings of Textual Units}
 \subtitle{With case studies on \emph{Les Misérables}}
 \date{}
-\author{Guillaume Guex}
-\institute{University of Lausanne}
+\author{Guillaume Guex \\ \href{mailto:guillaume.guex@unil.ch}{\color{blue} guillaume.guex@unil.ch}}
+\institute{Departement of Language and Information Sciences \\ University of Lausanne}
 
@@
 		\begin{itemize}
-			\item Identification of \imp{characters} 
-			\item Detection of \imp{interactions}
-			\item Construction of the \imp{graph}
+			\item Identification of \imp{characters}.
+			\item Detection of \imp{interactions}.
+			\item Construction of the \imp{graph}.
 		\end{itemize}
@@
 	\begin{frame}{The construction of a character network}
-		When dealing with \imp{textual narratives}, a frequently used method is to count \imp{character co-occurrences} in predefined \imp{textual units} \\(see, e.g., \cite{elsner_character-based_2012, rochat_analyse_2014}).
+		When dealing with \imp{text}, a frequently used method is to count \imp{character co-occurrences} in predefined \imp{textual units} \\(see, e.g., \cite{elsner_character-based_2012, rochat_analyse_2014}).
 \\
@@
 			\end{figure}
-			\item \imp{Embeddings of textual units}. The unit-term matrix is used to construct \imp{vectors} representing units. 
-			\item \imp{Embeddings of characters and relationships}, which derive from the embedding of textual units.
+			\item \imp{Embeddings of textual units}. The unit-term matrix is used to construct vectors representing units. 
+			\item \imp{Embeddings of characters and relationships}, which derive from unit vectors.
 		\end{itemize}
@@
 	\begin{frame}{Approaches}
-		More specifically, two types "embeddings" are studied:
+		More specifically, three types embeddings are studied:
 		\begin{itemize}
-			\item \imp{Correspondence Analysis (CA)}.
-			\item \imp{"Topic Modeling vectors"} build from \imp{Non-negative Matrix Factorization (NMF)}.
+			\item \imp{Correspondence Analysis (CA)} (main work).
+			\item \imp{Pre-trained word embeddings (WE)} (work in progress).
+			\item "Topical" vectors build from \imp{Non-negative Matrix Factorization (NMF)} (work in progress).
 		\end{itemize}
-		With two methods for constructing character/relationship vectors:
+		There also is two methods for constructing character/relationship vectors:
 		\begin{itemize}
@@
 
-	\section[Correspondence Analysis (CA) - centroids]{Correspondence Analysis (CA) - centroids}
+	\section[Correspondence Analysis - Centroids]{Correspondence Analysis - Centroids}
 
@@
 	\begin{frame}{Principles}
-		Correspondence Analysis is the natural tool for analyzing textual resources if data are organized in a $(n \times p)$ \imp{document-term matrix} \cite{lebart_analyse_2019} (here, documents are our textual units).
+		Correspondence Analysis is the natural tool for analyzing textual resources if data is organized in a $(n \times p)$ \imp{document-term matrix} \cite{lebart_analyse_2019} (here, documents are our textual units).
 It gives:
 		\begin{itemize}
-			\item $\min(n, p) - 1$ \imp{factorial axes}, by decreasing order of importance, which can be interpreted as latent variables.
-			\item \imp{Coordinates of each document} along these factors, where proximity can be interpreted as similar profile in term of words.
-			\item \imp{Coordinates of each word} along the same factors, where proximity can be interpreted as similar profile in term of documents.
-			\item \imp{Affinities between a document and a term}, which is computed by the \imp{scalar product} between their vectors.
+			\item $\min(n, p) - 1$ \imp{factorial axes}, by decreasing order of importance, which can be interpreted as \imp{latent variables}.
+			\item \imp{Coordinates of each document} along these factors, where proximity can be interpreted as similarity in word distributions.
+			\item \imp{Coordinates of each word} along the same factors, where proximity can be interpreted as similarity in document distributions.
+			\item \imp{Affinities between documents and terms}, which are computed by the \imp{scalar product}.
 		\end{itemize}
@@
 	\begin{frame}{Relationship embeddings - centroids}
-		The same idea can be applied to \imp{relationships}, In fact, in our data table, we can extend our table to include \imp{interactions}.
+		The same idea can be applied to \imp{relationships}, In fact, in our dataset, we can extend our table to include \imp{interactions} (up to a certain order).
 		\begin{figure}
@@
 	\begin{frame}{Character/relationship embeddings - usages}
-		What can we do with these character/relationship embeddings ? As they are in the same space as textual units, we can: 
+		What can we do with these character/relationship embeddings ? \\
+		\vspace{0.3cm}
+		As they are in the same space as textual units, we can: 
 		\begin{itemize}
@@
 	\begin{frame}{Characters/relationships vs axes}
-		Sometimes, \imp{factorial axes can be interpreted with coordinates of the words}. \imp{Positions of characters/relationships on this axis} reflect their affinity with this particular scale:
+		Sometimes, \imp{factorial axes can be interpreted with coordinates of the words}. \imp{Positions of characters/relationships on this axis} reflect polarities on this scale:
 		\begin{figure}
@@
 	\begin{frame}{Characters/relationships vs words}
-		We can also get the \imp{similarities between characters/relationships vs words} with the help of the \imp{scalar product}:
+		We can also get the \imp{similarities between characters/relationships vs words} with the \imp{scalar product}:
 		\begin{figure}
@@
 	\begin{frame}{Words vs characters/relationships}
-		By transposing the previous table, particular words (or group of words, i.e. a query) can give a ranking of characters/relationships:
+		By transposing the previous table, particular words (or group of words, i.e. a query) can give a \imp{ranking of characters/relationships}:
 		\begin{figure}
@@
 
-	\section[Correspondence Analysis (CA) - regressions]{Correspondence Analysis (CA) - regressions}
+	\section[Correspondence Analysis - Regressions]{Correspondence Analysis - Regressions}
 
@@
 	\begin{frame}{Relationship embeddings - 1st idea problems}
-		In fact, building these character/relationship vectors as \imp{centroids} is like considering them as \imp{additional variables} in the CA.
+		In fact, building these character/relationship vectors as \imp{centroids} is like considering them as \imp{supplementary variables} in the CA.
 It leads to \imp{additive relationships}, i.e., for a character $c$
@@
 		$$
-		where $v_{cd}$ is the vector of relationship between $c$ and $d$, and $v_{cc}$ is defined as the centroid of units where $c$ is alone. This means
+		where $v_{cd}$ is the vector of relationship between $c$ and $d$, and $v_{cc}$ is defined as the centroid of units where $c$ is alone. It means that:
 		\begin{itemize}
@@
 		\end{itemize}
-		We can use a \imp{regression model with interaction}.
+		We can use a \imp{regression model}.
 	\end{frame}
@@
 	\begin{frame}{Relationship embeddings - 2nd idea}
-		Resulting coordinates of opposite characters point at \imp{different directions}:
+		Resulting coordinates point at \imp{different directions}:
 		\begin{figure}
@@
 			\item When $\lambda$ is \imp{low}, the solution focuses on \imp{very specific, small parts of the text} to define characters and relationships.
-			\item An \imp{average} $\lambda$ (but which one?) is able to \imp{highlight character/relationship specificities relatively to corpus size.}
+			\item An \imp{average} $\lambda$ (but which one?) is able to \imp{highlight character/relationship specificities} while using \imp{sufficient information}.
 		\end{itemize}
@@
 	\begin{frame}{Words vs characters/relationships - regression}
-		And relationships according to words are more coherent:
+		And characters/relationships according to words seems more adjusted:
 		\vspace{-0.2cm}
@@
 	\begin{frame}{Words vs characters/relationships - regression}
-		This method give also good results if regressors are constructed according to a \imp{narrative timeline} (here, the \emph{Tomes}):
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.49\textwidth]{img/aimer_g.png} \includegraphics[width=0.49\textwidth]{img/rue_g.png} \\
+			\includegraphics[width=0.49\textwidth]{img/justice_g.png}
+			\includegraphics[width=0.49\textwidth]{img/guerre_g.png}
+		\end{figure}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Words vs characters/relationships - regression}
+		This method give also good results if regressors are constructed according to a \imp{narrative time division} (here, \emph{tomes}):
 		\vspace{-0.2cm}
@@
 
-	\begin{frame}{CA quick summary}
-		To recap the CA method:
+	\begin{frame}{Quick summary}
+		To recap from here:
 		\begin{itemize}
@@
 			\end{itemize}
-			\item These characters/relationships vectors can be \imp{explored} regarding:
+			\item These character/relationship vectors can be \imp{explored} regarding:
 			\begin{itemize}
@@
 			\end{itemize}
-			\item Moreover, we can explore characters/relationships vectors according to a \imp{Timeline}.
+			\item Moreover, character/relationship vectors can be constructed according to a \imp{time division}.
 		\end{itemize}
@@
 
-	\section[Pre-trained Word Embeddings]{Pre-trained Word Embeddings}
+	\section[Other types of Embeddings]{Other types of Embeddings}
 
@@
 		\vspace{0.4cm}
-		An idea to overcome this problem is to embed units/characters/relationships in a \imp{absolute referential} such as a \imp{pre-trained word embedding space}.
+		To perform this idea, units/characters/relationships are embedded in a \imp{pre-trained word embedding space}.
 
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Pre-trained Word Embeddings}
+
+		\imp{Type-based embeddings} (no transformers) must be used, because we would like to have \imp{reference points}, such as the \imp{word vectors}, to explore results. \\
+		\vspace{0.3cm}
+		Some examples of type-based embedding methods:
+		\begin{itemize}
+			\item \imp{Word2Vec} \cite{mikolov_efficient_2013}
+			\item \imp{GloVe} \cite{pennington_glove_2014}
+			\item \imp{FastText} \cite{bojanowski_enriching_2017}
+		\end{itemize}
+		Here, we will use pre-trained word vectors constructed with \imp{FastText} {\color{blue} \url{https://fasttext.cc/docs/en/crawl-vectors.html}}.
+
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Pre-trained Word Embeddings}
+
+		There also exists various ways to construct \imp{sentences, paragraphs, or documents embeddings} (in our case units) into the \imp{same space as words}. \\
+		\vspace{0.3cm}
+		The method proposed by \cite{arora2017simple} seems to perform very well in various tasks. Quickly explained:
+
+		\begin{itemize}
+			\item Units are embedded by making the average of their words, \imp{weighted by $\frac{\theta}{\theta + f_w}$}, where $f_w$ is the word frequency and $\theta$ a "smoothing parameter".
+			\item We \imp{substract} from all vectors, contained in the columns of $\mathbf{X}$, their projection alongside the first (left) singular vector of $\mathbf{X}$.  
+		\end{itemize}
+
+		The first operation gives more importance to \imp{rare words}, the second helps to remove \imp{syntactic information}.
+
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Pre-trained Word Embeddings}
+
+		Embedding of characters/relationships is obtained again with centroids and regressions. The \imp{cosine similarity} is used to measure characters/relationships affinities with words:
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.8\textwidth]{img/reg_vs_word_wv.png}
+		\end{figure}
+
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Pre-trained Word Embeddings}
+
+		Still a work in progress. However, we can see that:
+		\begin{itemize}
+			\item The found words are \imp{less specific to the text} (easier to make a general interpretation).
+			\item Some characters/relationships are mainly defined by \imp{verbs}, others by \imp{nouns}, and others by \imp{adjectives}.
+			\item The \imp{negative words} actually give information.
+		\end{itemize}
+		More importantly, the characters/relationships are in an \imp{absolute space}, \imp{comparison between works should be made}.
+
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Non-negative matrix factorization}
+
+		The last idea is \imp{Non-negative Matrix Factorization}, which is a \imp{Topic Modeling} method. \\
+		\vspace{0.3cm}
+		Its usage permits to get associations between \imp{characters/relationships} and \imp{automatically found topics} (not only words).\\
+		\vspace{0.3cm}
+		As the method gives \imp{probabilities of using each topic}, for all units, character/relationship embeddings have to be adapted:
+		\begin{itemize}
+			\item Centroid $\rightarrow$ \imp{Probability Chain Rule}.
+			\item Regression $\rightarrow$ \imp{Multinomial Logistic Regression}. 
+		\end{itemize} 
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Non-negative matrix factorization}
+		This method seems promising, but, for the moment, not as accurate as the other two:
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{img/nmf.png}
+		\end{figure}		
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\section[Conclusion]{Conclusion}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{Conclusion}
+		The proposed framework to analyse characters and relationships seems promising:
+		\begin{itemize}
+			\item Works on \imp{various corpus size}.
+			\item Works with \imp{various type of textual units} (e.g., lines in plays).
+			\item Works with \imp{oriented relationships}.
+			\item \imp{Two types of character/relationship} construction.
+			\item \imp{Multiple ways to explore} the results.
+		\end{itemize}
+		However, some remarks:
+		\begin{itemize}
+			\item \imp{Choices in pre-processing} (stop words, lemmatization, thresholds on word frequencies, thresholds on character occurrences) can strongly affect results.
+			\item \imp{Hyperparameters} can be hard to tune.
+			\item Results can be \imp{hard to interpret}.
+			\item \imp{How can we know for sure that results are accurate?}
+		\end{itemize}
+	\end{frame}
+
+	%------------------------------------------------------------------
+
+	\begin{frame}{}
+		\begin{center}
+			\huge Thank you for your attention ! \\
+			\imp{Questions ?}
+		\end{center}
 	\end{frame}

### 2022-06-08 2.0_CA_lesMiserables_withNetwork.py

@@ -155,7 +155,7 @@ A_regression = words_vs_regressions[present_object_names]
 #  Network
 # -------------------------------
 
-studied_word = "guerre"
+studied_word = "justice"
 polarity = regression_vs_words[studied_word]
 min_occ = 20
 
@@ -183,7 +183,7 @@ with open("corpora/LesMiserables_fr/node_pos.pkl", "rb") as pkl_file:
     node_pos = pickle.load(pkl_file)
 
 display_char_network(interact_list, interaction_polarity, edge_weights, edge_min_width=0.1, edge_max_width=10,
-                     node_pos=node_pos, node_min_width=10, node_max_width=200, font_size=10, arrowsize=10)
+                     node_pos=node_pos, node_min_width=10, node_max_width=200, font_size=15, plt_title=studied_word)
 
 # with open("corpora/LesMiserables_fr/node_pos.pkl", "wb") as pkl_file:
 #     pickle.dump(node_pos, pkl_file)

### 2022-06-08 3.0_WV_lesMiserables.py

@@ -22,7 +22,7 @@ min_occurrences = 3
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter
-regularization_parameter = 1
+regularization_parameter = 0.01
 
 # -------------------------------
 #  Loading
@@ -121,7 +121,7 @@ corpus.remove_occurrences_with_frequency(1e-10)
 #unit_coord = build_occurrences_vectors(dt_matrix.T, word_coord)
 
 # choice 2
-weighting_param = 0.001
+weighting_param = 0.01
 word_weights = corpus.units_words.to_numpy().sum(axis=0)
 word_weights = word_weights / sum(word_weights)
 smoothed_word_weights = weighting_param / (weighting_param + word_weights)
@@ -182,17 +182,16 @@ A_regression = words_vs_regressions[present_object_names]
 occurrences_vs_words = words_vs_occurrences.transpose()
 regression_vs_words = words_vs_regressions.transpose()
 
-to_explore_words = ["aimer", "rue", "justice", "guerre"]
-word_vs_occ = pd.DataFrame(index=range(10))
-for to_explore_word in to_explore_words:
-    object_largest = occurrences_vs_words[to_explore_word].nlargest()
-    object_smallest = occurrences_vs_words[to_explore_word].nsmallest()
+reg_v_word = pd.DataFrame(index=range(10))
+for object_name in present_object_names:
+    object_largest = A_regression[object_name].nlargest()
+    object_smallest = A_regression[object_name].nsmallest()
     object_col = []
     for i in range(object_largest.shape[0]):
         object_col.append(f"{object_largest.index[i]} ({np.round(object_largest.iloc[i], 2)})")
     for i in range(object_smallest.shape[0]):
         object_col.append(f"{object_smallest.index[i]} ({np.round(object_smallest.iloc[i], 2)})")
-    object_df = pd.DataFrame({to_explore_word: object_col})
-    word_vs_occ = pd.concat([word_vs_occ, object_df], axis=1)
-word_vs_occ.to_csv("word_vs_occ_wv_LM.csv")
+    object_df = pd.DataFrame({object_name: object_col})
+    reg_v_word = pd.concat([reg_v_word, object_df], axis=1)
+reg_v_word.to_csv("reg_v_word.csv")
 

### 2022-06-08 4.0_NMF_lesMiserables.py

@@ -15,7 +15,7 @@ aggregation_level = "chapitre"
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 5
+min_occurrences = 3
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 
@@ -49,7 +49,7 @@ character_names = [process_text(character_name)
 corpus.aggregate_on(aggregation_level)
 
 # Construct the unit-term matrix and remove rare words
-corpus.build_units_words(TfidfVectorizer(max_df=0.95, min_df=2, max_features=1000, stop_words=used_stop_words))
+corpus.build_units_words(TfidfVectorizer(max_df=0.95, min_df=2, max_features=2000, stop_words=used_stop_words))
 
 # Remove characters from words
 corpus.remove_words(character_names)
@@ -78,9 +78,9 @@ tfidf_sums = corpus.units_words.sum(axis=1).to_numpy()
 # -------------------------------
 
 # --- Make the NMF model
-n_groups = 20
+n_groups = 10
 
-nmf_model = NMF(n_components=n_groups, init="nndsvd", max_iter=2000)
+nmf_model = NMF(n_components=n_groups, init="nndsvd", max_iter=1000)
 #nmf_model = LatentDirichletAllocation(n_components=n_groups)
 nmf_model.fit(corpus.units_words.to_numpy())
 
@@ -97,8 +97,7 @@ char_vs_theme = build_occurrences_vectors(corpus.occurrences, unit_prob)
 
 # Make the regression vectors
 unit_sizes = corpus.units_words.sum(axis=1).to_numpy()
-reg_vs_theme = build_logistic_regression_vectors(corpus.occurrences, unit_prob, tfidf_sums)
-reg_vs_theme = build_occurrences_vectors(corpus.occurrences, unit_prob)
+reg_vs_theme = build_logistic_regression_vectors(corpus.occurrences, unit_prob, tfidf_sums*100, reg_type="auto")
 reg_vs_theme = pd.DataFrame(reg_vs_theme, list(corpus.occurrences.columns))
 theme_vs_reg = reg_vs_theme.transpose()
 theme_vs_reg = theme_vs_reg.reindex(sorted(theme_vs_reg.columns), axis=1)
@@ -119,3 +118,4 @@ for obj in object_names:
         present_object_names.append(obj)
 
 A_regression = theme_vs_reg[present_object_names]
+A_regression.to_csv("char_topics.csv")

### 2022-06-08 local_functions.py

@@ -747,7 +747,7 @@ def display_char_o_network(interact_list, edge_polarity_list, edge_weight_list, 
 def display_char_network(interact_list, edge_polarity_list, edge_weight_list, color="polarity", width="weight",
                            width_rank=False, node_min_width=50, node_max_width=1000, edge_min_width=0.2, edge_max_width=5,
                            string_strength="weight", min_alpha=0.5, max_alpha=1, cmap=plt.cm.coolwarm,
-                           node_pos=None, font_size=10, arrowsize=10):
+                           node_pos=None, font_size=10, plt_title=None):
     """
     A function to diplay a graph between character interactions
     """
@@ -833,6 +833,10 @@ def display_char_network(interact_list, edge_polarity_list, edge_weight_list, co
 
     # Starting the graph
     plt.figure()
+
+    # Title
+    if plt_title is not None:
+        plt.title(plt_title, fontsize=20)
 
     # Create the nodes
     nx.draw_networkx_nodes(graph,

### 2022-08-23 0.1_book_char_detection.py
0.2_preprocess_booknlp_results.py complete

@@ -1,22 +1,22 @@
 from booknlp.booknlp import BookNLP
 import torch
 
+# Empty cache for memory
 torch.cuda.empty_cache()
 
-model_params={
-		"pipeline":"entity", 
-		"model":"big"
-	}
-	
-booknlp=BookNLP("en", model_params)
+# The model pipeline
+model_params = {"pipeline": "entity", "model": "big"}
+
+# The model
+booknlp = BookNLP("en", model_params)
 
 # Input file to process
-input_file="corpora/relationship_corpora/candide.txt"
+input_file = "corpora/relationship_corpora/candide.txt"
 
 # Output directory to store resulting files in
-output_directory="corpora/relationship_corpora_characters"
+output_directory = "corpora/relationship_corpora_characters"
 
 # File within this directory will be named ${book_id}.entities, ${book_id}.tokens, etc.
-book_id="candide"
+book_id = "candide"
 
 booknlp.process(input_file, output_directory, book_id)

### 2022-08-23 0.2_preprocess_booknlp_results.py

@@ -1,0 +1,56 @@
+import pandas as pd
+import re
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+min_occurrences_threshold = 2
+
+# -------------------------------
+#   Code
+# -------------------------------
+
+# Load entities and token list
+entities_df = pd.read_csv("corpora/relationship_corpora_characters/candide.entities", sep="\t")
+token_df = pd.read_csv("corpora/relationship_corpora_characters/candide.tokens", sep="\t")
+
+# Remove -1 entities and keep characters
+entities_df = entities_df.loc[(entities_df.COREF > 0) & (entities_df.cat == "PER")]
+
+# Build a dictionary for unique entities
+id_to_name = {}
+for entity_id in set(entities_df.COREF):
+    entity_df = entities_df.loc[entities_df.COREF == entity_id]
+    if len(entity_df) >= min_occurrences_threshold:
+        id_shortest_name = entity_df.text.str.len().idxmin()
+        entity_short_name = entity_df.text.loc[id_shortest_name]
+        id_to_name[entity_id] = entity_short_name.lower().strip()
+
+# Characters list
+characters = list(set(id_to_name.values()))
+
+# To create a dataframe
+output_data = []
+# Loop on sentence id
+for sentence_id in token_df.sentence_ID.unique():
+    # Select the sentence id
+    sentence_df = token_df[token_df.sentence_ID == sentence_id]
+    # Get paragraph id
+    paragraph_id = sentence_df.paragraph_ID.min()
+    # Get sentence
+    text = " ".join([re.sub("['_]", " ", word) for word in sentence_df.word if word != "\ufeff"])
+    # Get characters ids
+    char_ids = [int(char_id) for char_id
+                in list(entities_df.join(sentence_df, on="start_token", how="right").COREF.dropna())]
+
+    # Build row and append to dataframe
+    row_dict = {char: 0 for char in characters}
+    for char_id in char_ids:
+        if char_id in id_to_name:
+            row_dict[id_to_name[char_id]] += 1
+    row_dict["paragraph_id"] = paragraph_id
+    row_dict["text"] = text
+    output_data.append(row_dict)
+
+results_df = pd.DataFrame(output_data, columns=["paragraph_id", "text"] + characters)

### 2022-08-23 0.2_process_booknlp_results.py

@@ -1,11 +1,0 @@
-import pandas as pd
-
-entities_df = pd.read_csv("corpora/relationship_corpora_characters/candide.entities", sep="\t")
-token_df = pd.read_csv("corpora/relationship_corpora_characters/candide.tokens", sep="\t")
-
-entities_df = entities_df[entities_df.COREF > 0]
-
-with open("corpora/relationship_corpora/candide.txt") as corpus_file:
-    corpus_txt = corpus_file.read()
-
-corpus_txt[47110:47113]

### 2022-08-23 0.1_book_char_detection.py
add character_relation_annotations.txt

@@ -11,10 +11,10 @@ model_params = {"pipeline": "entity", "model": "big"}
 booknlp = BookNLP("en", model_params)
 
 # Input file to process
-input_file = "corpora/relationship_corpora/candide.txt"
+input_file = "corpora/booknlp_corpora/candide.txt"
 
 # Output directory to store resulting files in
-output_directory = "corpora/relationship_corpora_characters"
+output_directory = "corpora/booknlp_corpora_characters"
 
 # File within this directory will be named ${book_id}.entities, ${book_id}.tokens, etc.
 book_id = "candide"

### 2022-08-23 0.2_preprocess_booknlp_results.py

@@ -6,14 +6,15 @@ import re
 # -------------------------------
 
 min_occurrences_threshold = 2
+book_name = "candide"
 
 # -------------------------------
 #   Code
 # -------------------------------
 
 # Load entities and token list
-entities_df = pd.read_csv("corpora/relationship_corpora_characters/candide.entities", sep="\t")
-token_df = pd.read_csv("corpora/relationship_corpora_characters/candide.tokens", sep="\t")
+entities_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.entities", sep="\t")
+token_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.tokens", sep="\t")
 
 # Remove -1 entities and keep characters
 entities_df = entities_df.loc[(entities_df.COREF > 0) & (entities_df.cat == "PER")]
@@ -53,4 +54,6 @@ for sentence_id in token_df.sentence_ID.unique():
     row_dict["text"] = text
     output_data.append(row_dict)
 
+# Build dataframe and save it
 results_df = pd.DataFrame(output_data, columns=["paragraph_id", "text"] + characters)
+results_df.to_csv(f"corpora/relationship_preprocessed/{book_name}.tsv", sep="\t")

### 2022-08-23 1.4_preprocess_text.py

@@ -8,11 +8,11 @@ from tqdm import tqdm
 # -------------------------------
 
 # Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables.tsv"
+corpus_tsv_path = "corpora/booknlp_preprocessed/candide.tsv"
 # Outfile
-output_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+output_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
 # Language ("fr" or "en")
-language = "fr"
+language = "en"
 
 # -------------------------------
 #  Code

### 2022-08-23 2.2_CA_Hamlet.py

@@ -1,5 +1,5 @@
-from nltk.corpus import stopwords
 from local_functions import *
+from nltk.corpus import stopwords
 
 # -------------------------------
 #  Parameters

### 2022-08-23 3.2_WV_booknlp.py

@@ -1,0 +1,158 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+from nltk.corpus import stopwords
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "paragraph_id"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+used_stop_words = stopwords.words('english')
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns)]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
+# Make occurrences binary
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+
+# Make the occurrences across a meta
+corpus.update_occurrences_across_meta(meta_for_occurrences)
+
+# Make sure no units are empty
+corpus.remove_units_without_words()
+corpus.remove_units_without_occurrences()
[…]

### 2022-08-23 3.2_WV_booknlp.py
test the results for Candide

@@ -17,11 +17,11 @@ min_word_frequency = 5
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 2
+min_occurrences = 5
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter
-regularization_parameter = 0.01
+regularization_parameter = 1
 
 # -------------------------------
 #  Loading
@@ -155,4 +155,14 @@ words_vs_regressions = words_vs_regressions.reindex(sorted(words_vs_regressions.
 
 # ---- Explore the list of words
 
-word_to_check = ["friend", "enemy", "acquaintance", "lovers", "rivals", "employer", "employee"]
+# List of word to check
+word_to_check = ["familial", "social", "professional"]
+
+# Making vectors for these words
+word_to_check_coord = np.zeros((len(word_to_check), wv_dim))
+for i, word in enumerate(word_to_check):
+    word_to_check_coord[i, :] = wv_model.get_vector(word)
+
+# Compute the cosine sim between occurrences_coord and word_coord
+words_vs_check = pd.DataFrame(compute_cosine(word_to_check_coord, regression_coord), index=word_to_check,
+                              columns=corpus.occurrences.columns)

### 2022-08-24 article/paper1.tex
add article draft

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
%% auto break lines
\lstset{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2022}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{COMHUM 2022: Workshop on Computational Methods in the Humanities,
  June 9--10, 2022, Lausanne, Switzerland}

%%
%% The "title" command^
\title{Refining character relationships using embeddings of textual units}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Guillaume Guex}[%s
orcid=0000-0003-1001-9525,
email=guillaume.guex@unil.ch]
\address[1]{Departement of Language and Information Sciences, University of Lausanne, Switzerland}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX{} document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as well as many
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  LaTeX class \sep
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

Distant reading tools allow researchers, from various fields, to quickly gain knowledge on textual corpora without actually reading them. Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summary large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus. Methods in this case rely heavily on Big Data and make an extensive use of Machine Learning algorithms. In the second case, researchers use these methods to underline hidden structures in a particular text, helping them to refine their understanding of it and reinforce stated hypotheses. Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpus are smaller, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results. \\
Automatic extraction and analysis of \emph{character networks} from literacy works typically belong in the latter group. These methods aim at representing various interactions occurring between fictional characters found in a textual narrative with a graph, thus showing explicitly the hidden structure of character relationships constructed by the author. This structure might allow to find hidden pattern within book, which can highlight a particular genre or author style and help to understand a part of the "flavor" given by the author to the text.

\section{Methods}

When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ textual units $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and counting characters co-occurrences in these units. Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters. However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters. In this paper, we propose a data organization, leading to various type of analyses, which permits the use of the text contained in the unit in order to characterize relationship

\subsection{Data organization}

A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ can be represented in a $n \times (p+1)$ table $N$, where $p$ is the number of characters found in the narrative. Each line represent a textual unit, the first column is the text composing this unit, and the remaining $p$ columns contains the number of character

\section{Results}

\section{Conclusion}

%%
%% Define the bibliography file to be used
\bibliography{charnet}

\end{document}

%%
%% End of file

### 2022-08-26 article/paper1.tex
article

@@
 These methods aim at representing various interactions occurring between fictional characters found in a textual narrative with a graph, thus showing explicitly the hidden structure of character relationships constructed by the author.
-This structure might allow to find hidden pattern within book, which can highlight a particular genre or author style and help to understand a part of the "flavor" given by the author to the text.
+This structure might allow to find hidden patterns within a book, which can highlight a particular genre or style.
 
-\section{Methods}
+\section{Methodology}
 
@@
 However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
-In this paper, we propose a data organization, leading to various type of analyses, which permits the use of the text contained in the unit in order to characterize relationship
+In this paper, we propose a data organization leading to various methods which takes into consideration the text contained in the unit, helping to refine understanding of characters and their relationships.
 
@@
 
-A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ can be represented in a $n \times (p+1)$ table $N$, where $p$ is the number of characters found in the narrative.
-Each line represent a textual unit, the first column is the text composing this unit, and the remaining $p$ columns contains the number of character
+A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ can be represented in a $n \times (1 + p + p^2)$ table, as shown in Table \ref{raw_table}, where $p$ is the number of characters found in the narrative.
+Each line represent a textual unit, the first column is the text composing this unit, and the next $p$ columns contains variables $O_1, \ldots, O_p$ counting occurrences of each character in the unit.
+The $p \times p$ remaining columns contains variables $C_{ij}$, which count characters co-occurrences and can be defined with $C_{ij} = \min(O_i, O_j)$.
+Note that higher order co-occurrences could also be considered (e.g.
+variables denoting the co-occurrences of three characters), but it remains outside the scope of this article.
+
+\begin{table}[h]
+	\tiny
+	\begin{tabular}{|l|c|c|c|c|c|c|}
+		\hline
+		 text & Azelma & Babet & Brujon & ... & Babet-Brujon & ... \\
+		 \hline
+		 \hline 
+		 Il arriva [...] & 1 & 0 & 0 & ... & 0 & ... \\
+		 \hline
+		 Quand Éponine [...] & 0 & 1 & 1 & ... & 1 & ... \\
+		 \hline
+		 Éponine alla [...] & 0 & 1 & 0 & ... & 0 & ... \\
+		 \hline
+		 Si bien qu'en [...] & 0 & 2 & 2 & ... & 2 & ... \\
+		 \hline
+	\end{tabular}
+	\label{raw_table}
+	\caption{A snippet of the data table extracted from \emph{les Misérables}.
+Rows are paragraphs, the first column contains the text of these paragraphs, the next $p$ columns counts character occurrences, and the last $p \times p$ columns character co-occurrences.}
+\end{table}
+
+This data organization can seem trivial, but it already gives an orientation to the subsequent analyses and should be kept in mind of the practitioner.
+As a matter of fact, textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns.
+Of course, the whole information is contained in the text column, but, for the moment, this column is raw and improper to any kind of statistical analysis.
+Its treatment will come later in sections (REF) and (REF).
+The current digression aims at showing that this dataset is oriented in way to see how the last $p + p^2$ variables, i.e.
+character occurrences and co-occurrences, have an influence over the text contained in the first variable.
+While the author uses its characters and character interactions in order to build its narrative, we, to a certain extent, work backward: we are searching how character appearances in the textual unit influence her or his choice of words.
+The choice to include character co-occurrences along with character occurrences is motivated by the fact that the interaction between two (or more) characters should be considered as an object of its own: this interaction is not necessarily the sum of its parts and gives a particular flavor to the unit.
+As stated before, for the moment, the column containing the text of the unit is improper for statistical analysis.
+Different approaches could be made in order to extract workable information from this column, such as sentiment analysis (REF), textometry (REF), or even Deep Learning methods.
+Here, we will restrain ourselves to methods using a \emph{Bag-of-Path} approach.
+
+\subsection{The Bag-of-Path approach}
+
+detecting how character interactions gives
 

### 2022-09-01 article/paper1.tex
write article

--- 2022-08-24 article/paper1.tex
@@
 
-A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ can be represented in a $n \times (p+1)$ table $N$, where $p$ is the number of characters found in the narrative.
-Each line represent a textual unit, the first column is the text composing this unit, and the remaining $p$ columns contains the number of character
+A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ is represented in this article by two tables.
+The first one is well known in the field of textual analysis, and consists in the $n \times v$ contingency table $\mathbf{N}$, as represented by Table \ref{cont_table}, where $v$ is the vocabulary size.
+In this table, each row is an unit, and each columns contain a variable $V_i$, which counts the number of times the word $i$ appears in the unit.
+Using this table typically denotes a \emph{Bag-of-Words} approach to our analyses.
+\\
+The second table is a $n \times (p + p^2)$ table $\mathbf{C}$, as shown in Table \ref{char_table}, where $p$ is the number of characters found in the narrative.
+Each row represents a textual unit, the first column is the text composing this unit, and the next $p$ columns contains variables $O_1, \ldots, O_p$ counting occurrences of each character in the unit.
+The $p \times p$ remaining columns contains variables $C_{ij}$, which count characters co-occurrences and can be defined with $C_{ij} = \min(O_i, O_j)$.
+Note that higher order co-occurrences could also be considered (e.g.
+variables denoting the co-occurrences of three characters), but it remains outside the scope of this article.
+\\
+
+\begin{table}[h]
+	\scriptsize
+	\begin{tabular}{|c||c|c|c|c|c|c|}
+		\hline
+		& a & alarme & alerte & ... & est & ... \\
+		\hline
+		\hline 
+		$u_{4756}$ & 1 & 0 & 0 & ... & 0 & ... \\
+		\hline
+		$u_{4757}$ & 0 & 1 & 1 & ... & 1 & ... \\
+		\hline
+		$u_{4758}$ & 0 & 1 & 0 & ... & 0 & ... \\
+		\hline
+		$u_{4759}$ & 0 & 2 & 2 & ... & 2 & ... \\
+		\hline
+	\end{tabular}
+	\label{cont_table}
+	\caption{A snippet of the contingency table $\mathbf{N}$ extracted from \emph{les Misérables}.
+Rows are paragraphs, columns are words in the vocabulary, and cells count the number of time each word appear in the unit.}
+\end{table}
+
+\begin{table}[h]
+	\scriptsize
+	\begin{tabular}{|c||c|c|c|c|c|c|}
+		\hline
+		  & Azelma & Babet & Brujon & ... & Babet-Brujon & ... \\
+		 \hline
+		 \hline 
+		 $u_{4756}$ & 1 & 0 & 0 & ... & 0 & ... \\
+		 \hline
+		 $u_{4757}$ & 0 & 1 & 1 & ... & 1 & ... \\
+		 \hline
+		 $u_{4758}$ & 0 & 1 & 0 & ... & 0 & ... \\
+		 \hline
+		 $u_{4759}$ & 0 & 2 & 2 & ... & 2 & ... \\
+		 \hline
+	\end{tabular}
+	\label{char_table}
+	\caption{A snippet of the character table $\mathbf{C}$ extracted from \emph{les Misérables}.
+Rows are paragraphs, the first $p$ columns counts character occurrences, and the last $p \times p$ columns character co-occurrences.}
+\end{table}
+
+This data organization can seem trivial, but it already gives an orientation to the subsequent analyses and should be kept in mind of the practitioner.
+Textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns of both tables.
+Moreover, subsequent analyses are oriented in searching how the character table $\mathbf{C}$ have an influence over the contingency table $\mathbf{N}$, i.e.
+searching which words are over-represented or under-represented knowing the characters composition in the unit.
+While authors use characters in order to build the narrative, we, to a certain extent, work backward: we are searching how character appearances in the textual unit influence her or his choice of words.
+The choice to include character co-occurrences along with occurrences is motivated by the fact that the interaction between two (or more) characters should be considered as an object of its own: this interaction is not necessarily the sum of its parts and gives a particular flavor to the unit.
+\\
+The use of a contingency table to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
+Using this is approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, an well studied mathematical object which permits the use of various kind of statistical methods.
+\\
+This data organization also highlight the importance of chose a proper size for the units.
+These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally capture a particular kind of state of characters in the narrative, or a particular interaction between them.
+Unfortunately, it is impossible to define an ideal size for all kind of textual resource, and this size should be balanced regarding knowledge of the studied work.
+
+\subsection{Methods}
+
+Various methods can be performed using the previously stated data organization, such as Sentiment Analysis (REF), Textometry (REF), or even Deep Learning methods.
+Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding}.
+Following the guideline stated in the previous section, the approach here is to use the contingency table $N$ in order to embedded the textual units, which will help to see how resulting vectors depends on character occurrences and co-occurrences.
+Various kind embeddings can be performed, and we will focus here on two methods.
+Section (REF) describes \emph{Correspondence Analysis (CA)}, and section (REF) focuses on \emph{Pre-trained, static, word vectors (WV)}.
+In section (REF), we show two different way to use the table $\mathcal{C}$ in order to further embed characters and character pairs into the same spaces.
+
+\subsubsection{Correspondence Analysis}
+
+Using Correspondence Analysis in order to analyse textual resources has a long tradition (REF).
+It has the advantage to provide an embedding space, the factorial map, where units are placed alongside words, allowing to analyse or represent the different units in terms of word specificities.
+Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance and profiles, which is desirable when interpreting results.
+\\
+By performing the Correspondence Analysis, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) of table $\mathbf{N}$ and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
+Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
+(MORE EXPLANATION ON CA ?
+SEE MQ IV).
+\\
+Note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$  obtained from CA reflect textual unit profile (in terms of words)  regarding the mean profile.
+This mean that this analysis is in fact \emph{contrastive}: we highlight unit variations among the studied text.
+This could therefore becomes problematic if we would like to build our dataset on multiple work: units belonging to the same text have a great chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
+
+\subsubsection{Pre-trained word vector}
+
+Pre-trained word vectors, based on Word2Vec (REF), Glove (REF), or Fasttext (REF), have recently received great attention from various fields (REFS).
+The generally originate from a training of very large corpora, such as Wikipedia (REF) or Common Crawl (REF) and results in a embedding containing a large quantities of word vectors.
+
+\subsubsection{Character and character pairs embeddings}
 

### 2022-09-01 local_functions.py

@@ -616,6 +616,36 @@ def compute_cosine(vectors_1, vectors_2):
     # Return the matrix of cosine
     return norm_vectors_1 @ norm_vectors_2.T
 
+def get_largest_smallest_indices(df, column_list=None, n=5, option="both"):
+    """
+    A function to get the n largest and smallest index from a dataframe
+    :param column_list: The list of columns to get (None correspond to all)
+    :param n: the number of indices to get (in each direction)
+    :param option: either "both", "largest", or "smallest", defines the direction.
+    """
+
+    # Get the df columns
+    if column_list is not None:
+        df = df[column_list]
+
+    # Loop on the columns
+    result_df = pd.DataFrame(index=range(10))
+    for column_name in df.columns:
+        object_largest = df[column_name].nlargest()
+        object_smallest = df[column_name].nsmallest()
+        indices_col = []
+
+        for i in range(object_largest.shape[0]):
+            indices_col.append(f"{object_largest.index[i]} ({np.round(object_largest.iloc[i], 2)})")
+        for i in range(object_smallest.shape[0]):
+            indices_col.append(f"{object_smallest.index[i]} ({np.round(object_smallest.iloc[i], 2)})")
+        object_df = pd.DataFrame({column_name: indices_col})
+        result_df = pd.concat([result_df, object_df], axis=1)
+
+    # Return resulting dataframe
+    return result_df
+
+
 
 def display_char_o_network(interact_list, edge_polarity_list, edge_weight_list, color="polarity", width="weight",
                            width_rank=False, node_min_width=50, node_max_width=1000, edge_min_width=0.2, edge_max_width=5,

### 2022-09-01 article/paper1.tex
write article

--- 2022-08-24 article/paper1.tex
@@
 These methods aim at representing various interactions occurring between fictional characters found in a textual narrative with a graph, thus showing explicitly the hidden structure of character relationships constructed by the author.
-This structure might allow to find hidden pattern within book, which can highlight a particular genre or author style and help to understand a part of the "flavor" given by the author to the text.
+This structure might allow to find hidden patterns within a book, which can highlight a particular genre or style.
 
-\section{Methods}
+\section{Methodology}
 
-When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ textual units $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and counting characters co-occurrences in these units.
+When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ textual units $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting characters co-occurrences in these units.
 Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters.
 However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
-In this paper, we propose a data organization, leading to various type of analyses, which permits the use of the text contained in the unit in order to characterize relationship
+In this paper, we propose a data organization leading to various methods which takes into consideration the text contained in the unit, helping to refine understanding of characters and their relationships.
 
@@
 
-A textual narrative divided in $n$ textual units $u_1, \ldots, u_n$ can be represented in a $n \times (p+1)$ table $N$, where $p$ is the number of characters found in the narrative.
-Each line represent a textual unit, the first column is the text composing this unit, and the remaining $p$ columns contains the number of character
+In this article, the data representation for a textual narrative, divided in $n$ textual units $u_1, \ldots, u_n$, is made through two tables.
+The first one is well known in the field of textual analysis, and consists in the $n \times v$ contingency table $\mathbf{N}$, as represented by Table \ref{cont_table}, where $v$ is the vocabulary size.
+In this table, each row represents an unit, each column a word, and cells $n_{ij}$ counts the number of times the word $i$ appears in the unit.
+Using this table typically denotes a \emph{Bag-of-Words} approach in our analyses.
+\\
+\begin{table}[h]
+	\scriptsize
+	\begin{tabular}{|c||c|c|c|c|c|c|}
+		\hline
+		& aller & allumer & apercevoir & bas & bon & ... \\
+		\hline
+		\hline 
+		$u_{100}$ & 23 & 2 & 6 & 11 & 6 & ... \\
+		\hline
+		$u_{7795}$ & 12 & 1 & 0 & 3 & 9 & ... \\
+		\hline
+		$u_{7796}$ & 10 & 0 & 5 & 1 & 5 & ... \\
+		\hline
+		$u_{7797}$ & 0 & 0 & 1 & 0 & 0 & ... \\
+		\hline
+	\end{tabular}
+	\label{cont_table}
+	\caption{A snippet of the contingency table $\mathbf{N}$ extracted from \emph{les Misérables}.
+Rows are chapters, columns are words in the vocabulary, and cell $n_{ij}$ counts the number of time word $j$ appear in chapter $i$.}
+\end{table}
+The second table, denoted by $\mathbf{O}$, has a size of $n \times p$ where $p$ is the number of \emph{character-based objects} found in the narrative and cells $o_{ij}$ counts occurrences of object $j$ in unit $i$.
+A character-based object can be loosely defined in order to be flexible for various types of narrative or analyses, but can be roughly seen as a countable recurring narrative entity, containing one or more characters.
+For example, it can be a character occurrence, a character co-occurrence, an oriented character interaction (e.g.
+a dialog), or even a particular recurring event containing multiple characters (e.g.
+a lecture).
+In this article, we mostly consider character occurrences and pair of characters co-occurrences, as shown in Table \ref{occ_table}.
+
+\begin{table}[h]
+	\scriptsize
+	\begin{tabular}{|c||c|c|c|c|}
+		\hline
+		& Cosette & Thénardier & Valjean & ... \\
+		\hline
+		\hline 
+		$u_{101}$ & 66 & 78 & 0 & ... \\
+		\hline
+		$u_{102}$ & 21 & 26 & 0 & ... \\
+		\hline
+		$u_{103}$ & 12 & 25 & 0 & ... \\
+		\hline
+		$u_{104}$ & 12 & 0 & 5 & ... \\
+		\hline
+	\end{tabular}
+	\begin{tabular}{|c||c|c|c|c|}
+		\hline
+		& ... & Cosette-Thénardier & Cosette-Valjean & ... \\
+		\hline
+		\hline 
+		$u_{101}$  	& ... & 66 & 0 &  ... \\
+		\hline
+		$u_{102}$ 	& ... & 21 & 0 & ... \\
+		\hline
+		$u_{103}$  	& ... & 12 & 0 & ... \\
+		\hline
+		$u_{104}$ 	& ... & 0 & 5 & ... \\
+		\hline
+	\end{tabular}
+	\label{occ_table}
+	\caption{A snippet of the character-based objects table $\mathbf{O}$ extracted from \emph{les Misérables}.
+Rows are chapters, columns are character occurrences (top) and character co-occurrences (bottom), and cell $o_{ij}$ counts the number of times object $j$ appear in chapter $i$.
+Character co-occurrences are computed here as $o_{ij} = \min(o_{ik}, o_{il})$, where $\{k, l\}$ are characters constituting $j$.}
+\end{table}
+
+This data organization already gives an orientation to the subsequent analyses and should be kept in mind of the practitioner.
+Textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns of both tables.
+Moreover, subsequent analyses are oriented in searching how the object table $\mathbf{O}$ has an influence over the contingency table $\mathbf{N}$, i.e.
+searching which words are over-represented or under-represented knowing the character-based objects in the unit.
+While authors use characters in order to build the narrative, we, to a certain extent, work backward: we are searching how character appearances and interactions in the textual unit act on her/his choice of words.
+If extraction methods permit it, a practitioner should include all character-based objects which she/he desire to study.
+Here, for example, the choice to include character co-occurrences along with occurrences is motivated by the fact that we are interested in studying character relationships.
+A character co-occurrence can roughly be seen as an interaction between two characters, and an interaction between two characters (or more, but higher order interactions are outside the scope of this article) should be considered as an object of its own: this interaction is not necessarily the sum of its parts and gives a particular flavor to the unit.
+\\
+This data organization also highlight the importance of choosing a proper size for the units.
+These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally capture particularities about one of the character-based objects.
+Unfortunately, it is impossible to define an ideal size for all types of analysis, and this size should be balanced regarding the level of analysis, text size, selected character-based objects, and previous knowledge of the studied work.
+\\
+The use of a contingency table to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
+Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which permits the use of various kind of statistical methods.
+The next section shows two methods of analysis based on this table.
+\\
+
+\subsection{Embedding of textual units}
+
+Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Sentiment Analysis (REF), Textometry (REF), or even Deep Learning methods.
+Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
+In section (REF) These embeddings will help to see how resulting vectors depends on character occurrences and co-occurrences.
+Various kind embeddings can be performed, and we will focus here on two methods.
+Section (REF) describes \emph{Correspondence Analysis (CA)} and section (REF) focuses on \emph{Pre-trained, static, word vectors (WV)}.
+
+\subsubsection{Correspondence Analysis}
+
+Using Correspondence Analysis in order to analyse textual resources has a long tradition (REF).
+It has the advantage to provide an embedding space, the factorial map, where units are placed alongside words, allowing to analyse or represent the different units in terms of word specificities.
+Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance and profiles, which is desirable when interpreting results.
+\\
+By performing the Correspondence Analysis, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) of table $\mathbf{N}$ and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
+Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
+(MORE EXPLANATION ON CA ?
+SEE MQ IV).
+\\
+Note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$  obtained from CA reflect textual unit profile (in terms of words)  regarding the mean profile.
+This mean that this analysis is in fact \emph{contrastive}: we highlight unit variations among the studied text.
+This could therefore becomes problematic if we would like to build our dataset on multiple work: units belonging to the same text have a great chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
+
+\subsubsection{Pre-trained word vector}
+
+Pre-trained word vectors, based on Word2Vec (REF), Glove (REF), or Fasttext (REF), have recently received great attention from various fields (REFS).
+The generally originate from a training of very large corpora, such as Wikipedia (REF) or Common Crawl (REF) and results in a embedding containing a large quantities of word vectors.
+
+\subsubsection{Character and character pairs embeddings}
 

### 2022-09-01 2.0_CA_lesMiserables.py

@@ -17,7 +17,7 @@ max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
 min_occurrences = 1
 # Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = "tome"
+meta_for_occurrences = None
 # Regularization parameter (0.1)
 regularization_parameter = 1
 
@@ -64,7 +64,7 @@ interaction_occurrences = build_interactions(corpus.occurrences, max_interaction
 corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
 
 # Make occurrences binary
-corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+#corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
 
 # Make the occurrences across a meta
 corpus.update_occurrences_across_meta(meta_for_occurrences)

### 2022-09-02 article/paper1.tex
write article

@@
 \usepackage{listings}
+\usepackage{bm}
 %% auto break lines
@@
 Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpus are smaller, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results.
-\\
+
 Automatic extraction and analysis of \emph{character networks} from literacy works typically belong in the latter group.
@@
 In this article, the data representation for a textual narrative, divided in $n$ textual units $u_1, \ldots, u_n$, is made through two tables.
-The first one is well known in the field of textual analysis, and consists in the $n \times v$ contingency table $\mathbf{N}$, as represented by Table \ref{cont_table}, where $v$ is the vocabulary size.
+The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ contingency table $\mathbf{N}$, as represented by Table \ref{cont_table}, where $v$ is the vocabulary size.
 In this table, each row represents an unit, each column a word, and cells $n_{ij}$ counts the number of times the word $i$ appears in the unit.
 Using this table typically denotes a \emph{Bag-of-Words} approach in our analyses.
-\\
+
 \begin{table}[h]
@@
 \end{table}
-The second table, denoted by $\mathbf{O}$, has a size of $n \times p$ where $p$ is the number of \emph{character-based objects} found in the narrative and cells $o_{ij}$ counts occurrences of object $j$ in unit $i$.
+
+The second table, denoted by $\mathbf{O}$, has a size of $(n \times p)$ where $p$ is the number of \emph{character-based objects} found in the narrative and cells $o_{ij}$ counts occurrences of object $j$ in unit $i$.
 A character-based object can be loosely defined in order to be flexible for various types of narrative or analyses, but can be roughly seen as a countable recurring narrative entity, containing one or more characters.
@@
 A character co-occurrence can roughly be seen as an interaction between two characters, and an interaction between two characters (or more, but higher order interactions are outside the scope of this article) should be considered as an object of its own: this interaction is not necessarily the sum of its parts and gives a particular flavor to the unit.
-\\
+
 This data organization also highlight the importance of choosing a proper size for the units.
-These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally capture particularities about one of the character-based objects.
-Unfortunately, it is impossible to define an ideal size for all types of analysis, and this size should be balanced regarding the level of analysis, text size, selected character-based objects, and previous knowledge of the studied work.
-\\
+These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally captures particularities about one of the character-based objects.
+Unfortunately, it is impossible to define an ideal size for all types of analysis and this size should be balanced regarding the level of analysis, text size, selected character-based objects, and previous knowledge of the studied work.
+
 The use of a contingency table to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
@@
 The next section shows two methods of analysis based on this table.
-\\
 
@@
 Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
-In section (REF) These embeddings will help to see how resulting vectors depends on character occurrences and co-occurrences.
-Various kind embeddings can be performed, and we will focus here on two methods.
-Section (REF) describes \emph{Correspondence Analysis (CA)} and section (REF) focuses on \emph{Pre-trained, static, word vectors (WV)}.
+\\
+In section (REF), these vectors of textual units are used as anchor points in order to also embed character-based objects in the same space.
+Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible, in order to properly extract  information about the localization of character-based objects vectors (the relative position of these vectors is insufficient).
+For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of character-based objects relatively to word vectors, these objects can be characterized.
 
-\subsubsection{Correspondence Analysis}
+We propose here two embeddings verifying this condition: Section (REF) describes \emph{Correspondence Analysis (CA)} and section (REF) focuses on \emph{Pre-trained word vectors (WV)}.
 
-Using Correspondence Analysis in order to analyse textual resources has a long tradition (REF).
-It has the advantage to provide an embedding space, the factorial map, where units are placed alongside words, allowing to analyse or represent the different units in terms of word specificities.
-Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance and profiles, which is desirable when interpreting results.
-\\
-By performing the Correspondence Analysis, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) of table $\mathbf{N}$ and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
+\subsubsection{Correspondence Analysis (CA)}
+
+Using Correspondence Analysis in order to analyze textual resources has a long tradition in literature (REF).
+It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, allowing to analyze or represent the different units in terms of word specificities.
+Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance between profiles, which is desirable when interpreting results.
+
+By performing a Correspondence Analysis on table $\mathbf{N}$, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
 Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
-(MORE EXPLANATION ON CA ?
-SEE MQ IV).
-\\
+For detailed computations of quantities given by the CA, see Appendix \ref{ca_details}.
+The position of a unit vector $\mathbf{x}_i$ can be interpreted by two different methods.
+
+The first methods is to look at its position on a particular axis $\alpha$, i.e.
+looking at the component $x_{i\alpha}$.
+This component gives the position of the unit on a particular found "contrast" between units, depending on the chosen $\alpha$, and this contrast will be strong if $p_\alpha$, i.e.
+\emph{the proportion of inertia expressed in $\alpha$}, is high.
+It can further be interpreted by observing the \emph{contribution of each word $j$} composing the axis $\alpha$, i.e.
+$c^w_{j\alpha}$ and looking at the sign of $w_{j\alpha}$.
+Hopefully, by extracting and interpreting the most positive and negative contributing words, the chosen axis can express a particular duality which operates inside the studied text (e.g.
+love-hatred, action-description, lightness-darkness).
+The second method is to directly look at the \emph{similarities} $s_{ij}$ between an unit $i$ and a word $j$, as defined by the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$.
+A positive (resp.
+negative) similarity denotes a over-representation (resp.
+under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
+Observe that in this article, both methods are rather applied to character-based object vectors defined in section (REF), as they lay in the same space as unit vectors.
+
 Note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
 This mean that this analysis is in fact \emph{contrastive}: we highlight unit variations among the studied text.
-This could therefore becomes problematic if we would like to build our dataset on multiple work: units belonging to the same text have a great chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
+This could therefore becomes problematic if we would like to build our dataset on multiple works: units belonging to the same text have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
+Moreover, the words helping the interpretation of units (and character-based objects) are contained in the studied text, which might limit its range of application.
 
@@
 
+\appendix
+
+\section{Appendix}
+
+\subsection{Correspondence Analysis}
+\label{ca_details}
+
+Starting from the $(n \times v)$ contingency table $\mathbf{N} = (n_{ij})$, we define the vector of unit weights as $\mathbf{f} = (f_i) := (n_{i\bullet}/n_{\bullet \bullet})$ and the vector of word weights as $\mathbf{g} = (g_j) := (n_{\bullet j}/n_{\bullet \bullet})$, where $\bullet$ denotes the summation on the replaced index.
+It is then possible to compute the \emph{weighted scalar product matrix between units} $\mathbf{K} = (k_{ij})$ with
+
+\begin{equation}
+k_{ij} := \sqrt{f_i f_j} \sum_{k=1}^{v} g_k(q_{ik} - 1)(q_{jk} - 1), 
+\end{equation}
+
+where $q_{ik} = \frac{n_{ik} n_{\bullet \bullet}}{n_{j \bullet} n_{\bullet k}}$ is the \emph{quotient of independence} of the cell $i, k$.
+The vector of textual unit $i$, $\mathbf{x}_i = (x_{i\alpha})$, is obtained by the eigendecomposition of the matrix $\mathbf{K} = \mathbf{U}\bm{\Lambda}\mathbf{U}^\top$ and with
+
+\begin{equation}
+x_{i\alpha} := \frac{\sqrt{\lambda_\alpha}}{\sqrt{f_i}} u_{i \alpha},
+\end{equation}
+
+where $\lambda_\alpha$ are the eigenvalues contained in the diagonal of $\bm{\Lambda}$ and $u_{i \alpha}$ the eigenvectors components found in $\mathbf{U}$. \\
+We can also find the vector of word $j$, $\mathbf{w}_j = (w_{j\alpha})$, with
+
+\begin{equation}
+w_{j\alpha} := \frac{1}{\sqrt{\lambda_\alpha}} \sum_{i=1}^v f_i q_{ij} x_{i \alpha}.
+\end{equation}
+
+Note that various other quantities of interest can also be computed in CA, such as 
+\begin{align*}
+p_\alpha &:= \frac{\lambda_\alpha}{\lambda_\bullet} :\text{\small the proportion of inertia expressed in $\alpha$,} \\
+c^u_{i \alpha} &:= \frac{f_i x_{i\alpha}^2}{\lambda_\alpha} : \text{\small the contribution of unit $i$ to axis $\alpha$,} \\
+c^w_{j \alpha} &:= \frac{g_j w_{j\alpha}^2}{\lambda_\alpha} : \text{\small the contribution of word $j$ to axis $\alpha$,} \\
+h^u_{i \alpha} &:= \frac{x_{i\alpha}^2}{\sum_{\alpha} x_{i\alpha}^2} : \text{\small the contribution of  axis $\alpha$ to unit $i$,} \\
+h^w_{j \alpha} &:= \frac{w_{j\alpha}^2}{\sum_{\alpha} w_{j\alpha}^2} : \text{\small the contribution of  axis $\alpha$ to word $j$,}
+\end{align*}
+For a detailed interpretation of these different quantities, see (REF).
+
 %%

### 2022-09-06 article/paper1.tex
write article

@@
 \usepackage{bm}
+\usepackage{url}
+
 %% auto break lines
@@
 a dialog), or even a particular recurring event containing multiple characters (e.g.
-a lecture).
+a meeting).
 In this article, we mostly consider character occurrences and pair of characters co-occurrences, as shown in Table \ref{occ_table}.
@@
 While authors use characters in order to build the narrative, we, to a certain extent, work backward: we are searching how character appearances and interactions in the textual unit act on her/his choice of words.
-If extraction methods permit it, a practitioner should include all character-based objects which she/he desire to study.
+If the extraction method permits it, a practitioner should include all character-based objects which she/he desire to study.
 Here, for example, the choice to include character co-occurrences along with occurrences is motivated by the fact that we are interested in studying character relationships.
-A character co-occurrence can roughly be seen as an interaction between two characters, and an interaction between two characters (or more, but higher order interactions are outside the scope of this article) should be considered as an object of its own: this interaction is not necessarily the sum of its parts and gives a particular flavor to the unit.
+A character co-occurrence can roughly be seen as an interaction between two characters, and an interaction between two characters (or more, but higher order interactions are outside the scope of this article) should be considered as an object of its own: this interaction is not necessarily the sum of its parts and can give a particular flavor to the unit.
 
@@
 In section (REF), these vectors of textual units are used as anchor points in order to also embed character-based objects in the same space.
-Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible, in order to properly extract  information about the localization of character-based objects vectors (the relative position of these vectors is insufficient).
+Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible in order to properly extract information about the localization of character-based objects vectors (the relative position of these vectors is insufficient).
 For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of character-based objects relatively to word vectors, these objects can be characterized.
@@
 Using Correspondence Analysis in order to analyze textual resources has a long tradition in literature (REF).
-It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, allowing to analyze or represent the different units in terms of word specificities.
+It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, allowing to analyze or represent the different units in terms of word frequency profiles.
 Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance between profiles, which is desirable when interpreting results.
@@
 For detailed computations of quantities given by the CA, see Appendix \ref{ca_details}.
-The position of a unit vector $\mathbf{x}_i$ can be interpreted by two different methods.
+The position of a unit vector $\mathbf{x}_i$ can be interpreted by mutliple approaches, but we mainly use two here.
 
-The first methods is to look at its position on a particular axis $\alpha$, i.e.
+The first way to interpret it is to look at the unit-vector position on a particular axis $\alpha$, i.e.
 looking at the component $x_{i\alpha}$.
@@
 
-Note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
-This mean that this analysis is in fact \emph{contrastive}: we highlight unit variations among the studied text.
-This could therefore becomes problematic if we would like to build our dataset on multiple works: units belonging to the same text have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
-Moreover, the words helping the interpretation of units (and character-based objects) are contained in the studied text, which might limit its range of application.
+Using CA to embedded units however comes with some limitations.
+First, note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
+This analysis is therefore \emph{contrastive}: it highlights unit variations among the studied text.
+This could becomes problematic in order to study a dataset containing multiple texts: units belonging to the same text will have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
+Another limitation with this approach is that the words helping the interpretation of units (and character-based objects) are contained in the studied text.
+Approaches requiring to study the position of units and objects relatively to a predefined list of words (e.g., friends, enemies, family) might therefore be impossible.
 
-\subsubsection{Pre-trained word vector}
+\subsubsection{Pre-trained word vector (WV)}
 
-Pre-trained word vectors, based on Word2Vec (REF), Glove (REF), or Fasttext (REF), have recently received great attention from various fields (REFS).
-The generally originate from a training of very large corpora, such as Wikipedia (REF) or Common Crawl (REF) and results in a embedding containing a large quantities of word vectors.
+Pre-trained word vectors, based on Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
+They are generally obtained through a training on a very large corpora, such as Wikipedia (REF) or Common Crawl (REF), and the resulting embedding contains a large quantity of word vectors.
+As shown by multiple studies (REF), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in mutliple applications (REF).
 
-\subsubsection{Character and character pairs embeddings}
+There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF), which are often used to apply a classification or clustering algorithm on the newly embedded objects (REF).
+Here, we use a recent methodology proposed in (REF), in order to obtain textual unit vectors laying in the same space as words.
+
+More precisely, we use a pre-trained word vectors $w_1, \ldots, w_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is
+
+\subsection{Character-based object embeddings}
 
@@
 
-where $\lambda_\alpha$ are the eigenvalues contained in the diagonal of $\bm{\Lambda}$ and $u_{i \alpha}$ the eigenvectors components found in $\mathbf{U}$. \\
-We can also find the vector of word $j$, $\mathbf{w}_j = (w_{j\alpha})$, with
+where $\lambda_\alpha$ are the eigenvalues contained in the diagonal matrix $\bm{\Lambda}$ and $u_{i \alpha}$ the eigenvectors components found in $\mathbf{U}$.
+We find the vector of word $j$, $\mathbf{w}_j = (w_{j\alpha})$, with
 

### 2022-09-06 article/paper1.tex
write article

@@
 
-There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF), which are often used to apply a classification or clustering algorithm on the newly embedded objects (REF).
-Here, we use a recent methodology proposed in (REF), in order to obtain textual unit vectors laying in the same space as words.
+There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF).
+These vectors are often used to apply a classification or clustering algorithm on the newly embedded objects (REF), or to query information (REF).
+These methods often use the frequencies of words found in the objects, i.e.
+a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and align vectors.
+In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit size and gives state-of-the-art results in multiple tasks.
 
-More precisely, we use a pre-trained word vectors $w_1, \ldots, w_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is
+More precisely, we use a pre-trained word vectors $\mathbf{w}_1, \ldots, \mathbf{w}_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is 2 millions and the dimension of vectors are $300$.
+Textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.
 
@@
 
+\subsection{Unit embedding based of pre-trained word vectors}
+\label{wv_details}
+
+This methods is justified and detailed in (REF).
+Let $\mathbf{w}_1, \ldots, \mathbf{w}_v$ be pre-trained word vectors which appear in the studied corpus, and the $(n \times v)$ table $\mathbf{N}$ counting the frequency of these words in the $n$ textual units.
+We first construct the \emph{uncentered vectors} $\widetilde{\mathbf{x}}_i$ of each unit $i$ with
+\begin{equation}
+\widetilde{\mathbf{x}}_i = \sum_{j = 1}^v \frac{n_{ij}}{n_{i \bullet}} \frac{a}{a + \frac{n_{\bullet j}}{n_{\bullet \bullet}}} \mathbf{w}_j,
+\end{equation}
+where $a > 0$ is an hyperparameter which gives less importance to frequent words as $a \to 0$.
+Let $\widetilde{\mathbf{X}}$ be the matrix whose columns are vectors $\widetilde{\mathbf{x}}_i$, and $\mathbf{u}$ be its first singular vector.
+We find \emph{vectors} $\mathbf{x}_i$ of each units $i$ with
+\begin{equation}
+\mathbf{x}_i = \widetilde{\mathbf{x}}_i - \mathbf{u}\mathbf{u}^\top \widetilde{\mathbf{x}}_i.
+\end{equation}
+This last equation act like a \emph{centration} of unit vectors.
 %%

### 2022-09-06 article/paper1.tex
write article

@@
 		\hline 
-		$u_{100}$ & 23 & 2 & 6 & 11 & 6 & ... \\
+		$u_{101}$ & 23 & 2 & 6 & 11 & 6 & ... \\
 		\hline
-		$u_{7795}$ & 12 & 1 & 0 & 3 & 9 & ... \\
+		$u_{102}$ & 12 & 1 & 0 & 3 & 9 & ... \\
 		\hline
-		$u_{7796}$ & 10 & 0 & 5 & 1 & 5 & ... \\
+		$u_{103}$ & 10 & 0 & 5 & 1 & 5 & ... \\
 		\hline
-		$u_{7797}$ & 0 & 0 & 1 & 0 & 0 & ... \\
+		$u_{104}$ & 0 & 0 & 1 & 0 & 0 & ... \\
 		\hline
@@
 \subsection{Embedding of textual units}
+\label{unit_embeddings}
 
@@
 
-We propose here two embeddings verifying this condition: Section (REF) describes \emph{Correspondence Analysis (CA)} and section (REF) focuses on \emph{Pre-trained word vectors (WV)}.
+We propose here two embeddings verifying this condition: Section \ref{ca_method} describes \emph{Correspondence Analysis (CA)} and section \ref{wv_method} focuses on \emph{Pre-trained Word Vectors (WV)}.
 
 \subsubsection{Correspondence Analysis (CA)}
+\label{ca_method}
 
@@
 
-By performing a Correspondence Analysis on table $\mathbf{N}$, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
+By performing a Correspondence Analysis on table $\mathbf{N}$, we directly get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
 Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
@@
 under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
-Observe that in this article, both methods are rather applied to character-based object vectors defined in section (REF), as they lay in the same space as unit vectors.
+Observe that in this article, both methods are rather applied to character-based object vectors defined in section (REF), as they lie in the same space as unit vectors.
 
@@
 
-\subsubsection{Pre-trained word vector (WV)}
+\subsubsection{Pre-trained Word Vectors (WV)}
+\label{wv_method}
 
@@
 These methods often use the frequencies of words found in the objects, i.e.
-a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and align vectors.
+a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to align vectors.
 In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit size and gives state-of-the-art results in multiple tasks.
@@
 Textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.
+The main way to interpret units with this method is to use the cosine similarity between its corresponding vector $\mathbf{x}_i$ and every word-vectors $\mathbf{w}_j$, as defined by $s_{ij} := \frac{\mathbf{x}_i^\top \mathbf{w}_j}{\sqrt{\mathbf{x}_i^\top \mathbf{x}_i \mathbf{w}_j^\top \mathbf{w}_j}}$.
+The cosine similarity also permits to compare units between themselves.
+
+With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and character-based objects vectors in section REF) lie in an \emph{absolute space} defined by the used word vectors.
+Comparison between different texts are therefore more pertinent in this space and comparison with words absent from the corpus can be made.
+However, it is possible that all units from a given text, if the author style is particularly marked, are located in the same region of the space.
+In this case, the list of most associated word-vectors might be similar for every unit, and the analysis might not give usable results.
+This effect is fortunately limited by the centration of unit-vectors which occurs in the method describe in Appendix \ref{wv_details}.
 
 \subsection{Character-based object embeddings}
+
+The main goal of this article is not to analyze units, but rather the character-based objects, i.e.
+the $p$ columns of table $\mathbf{O}$.
+While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{O}$ in order to build the character-based vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ which lie in the same space as units.
+
+Two propositions of method are made: the \emph{centroids} method (CENT) is describe in section \ref{centroid} and the \emph{regressions} method (REG) is explained in section \ref{regression}.
+Both methods work with the proposed embeddings of units.
+
+\subsubsection{Centroids (CENT)}
+\label{centroid}
+
+This method is the most trivial and is based on the following intuition: a character-based object is characterized by the different units in which it appears.
+In other words, we can define the vector $\mathbf{y}_k$ for character-object object $k$ as
+\begin{equation}
+\mathbf{y}_k = \sum_{i=1}^n \frac{o_{ik}}{o_{\bullet k}} \mathbf{x}_i
+\end{equation}
+i.e.
+the center of mass, or \emph{centroid}, of the units containing the character-based object, weighted by the relative weight of its occurrences $\frac{o_{ik}}{o_{\bullet k}}$.
+This way of building character-based vectors is very closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
+However, by contrast to supplementary variables, no dilatation is made after computing centroids, which means that character-objects in fact lie in the same space as units (row).
+\\
+An important remark about the centroid method, is that character-objects vectors positions are \emph{additive}, which means that we have
+\begin{equation}
+o_{ic} = \sum_{g \in \mathcal{G}} o_{ig}, \forall i \implies \mathbf{y}_c = \sum_{g \in \mathcal{G}} \frac{o_{ig}}{o_{ic}} \mathbf{y}_g
+\end{equation}
+
+\subsubsection{Regressions (REG)}
+\label{regression}
 
@@
 Let $\widetilde{\mathbf{X}}$ be the matrix whose columns are vectors $\widetilde{\mathbf{x}}_i$, and $\mathbf{u}$ be its first singular vector.
-We find \emph{vectors} $\mathbf{x}_i$ of each units $i$ with
+We compute \emph{vectors} $\mathbf{x}_i$ of each units $i$ with
 \begin{equation}
@@
 \end{equation}
-This last equation act like a \emph{centration} of unit vectors.
-%%
+This last equation act like a \emph{centration} of unit vectors in the direction of the first singular vector $\mathbf{u}$.
+
 %% Define the bibliography file to be used

### 2022-09-07 article/paper1.tex
write article

@@
 The second table, denoted by $\mathbf{O}$, has a size of $(n \times p)$ where $p$ is the number of \emph{character-based objects} found in the narrative and cells $o_{ij}$ counts occurrences of object $j$ in unit $i$.
-A character-based object can be loosely defined in order to be flexible for various types of narrative or analyses, but can be roughly seen as a countable recurring narrative entity, containing one or more characters.
+A character-based object can be loosely defined in order to be flexible for various types of narrative or analyses, but can roughly be seen as a countable recurring narrative entity, containing one or more characters.
 For example, it can be a character occurrence, a character co-occurrence, an oriented character interaction (e.g.
@@
 These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally captures particularities about one of the character-based objects.
-Unfortunately, it is impossible to define an ideal size for all types of analysis and this size should be balanced regarding the level of analysis, text size, selected character-based objects, and previous knowledge of the studied work.
+Unfortunately, it is impossible to define an ideal size for all types of analysis and this size should be balanced regarding the level of analysis, the text size, the selected character-based objects, and previous knowledge of the studied work.
 
-The use of a contingency table to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
-Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which permits the use of various kind of statistical methods.
+The use of a contingency table $\mathbf{N}$ to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
+Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which allows the use of various kind of statistical methods.
 The next section shows two methods of analysis based on this table.
@@
 
-Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Sentiment Analysis (REF), Textometry (REF), or even Deep Learning methods.
+Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Sentiment Analysis (REF), Textometry (REF), or even Deep Learning methods (REF?).
 Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
 \\
-In section (REF), these vectors of textual units are used as anchor points in order to also embed character-based objects in the same space.
+In section (REF), these vectors of textual units are used as anchor points in order to also embed character-based objects into the same space.
 Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible in order to properly extract information about the localization of character-based objects vectors (the relative position of these vectors is insufficient).
@@
 Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
-For detailed computations of quantities given by the CA, see Appendix \ref{ca_details}.
+For a detailed computation of quantities in CA, see Appendix \ref{ca_details}.
 The position of a unit vector $\mathbf{x}_i$ can be interpreted by mutliple approaches, but we mainly use two here.
@@
 
-This method is the most trivial and is based on the following intuition: a character-based object is characterized by the different units in which it appears.
+This method is the most trivial and is based on the following intuition: a character-based object is characterized by all units in which it appears.
 In other words, we can define the vector $\mathbf{y}_k$ for character-object object $k$ as
@@
 the center of mass, or \emph{centroid}, of the units containing the character-based object, weighted by the relative weight of its occurrences $\frac{o_{ik}}{o_{\bullet k}}$.
-This way of building character-based vectors is very closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
-However, by contrast to supplementary variables, no dilatation is made after computing centroids, which means that character-objects in fact lie in the same space as units (row).
+This way of building character-based vectors is closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
+However, by contrast, character-based vectors are not dilated after computing centroids, which means that they lie in the same space as units (row).
 \\
@@
 \begin{equation}
-o_{ic} = \sum_{g \in \mathcal{G}} o_{ig}, \forall i \implies \mathbf{y}_c = \sum_{g \in \mathcal{G}} \frac{o_{ig}}{o_{ic}} \mathbf{y}_g
+o_{ik} = \sum_{g \in \mathcal{G}} o_{ig}, \forall i \implies \mathbf{y}_k = \sum_{g \in \mathcal{G}} \frac{o_{\bullet g}}{o_{\bullet k}} \mathbf{y}_g,
 \end{equation}
+where $\mathcal{G}$ is a subset of character-based objects.
+This property can be interpreted as followed: if the occurrences of a character $k$ can be divided among different situations $g$ (the character alone, the character in interaction with another character, etc.), the character vector $\mathbf{y}_k$ is in fact the centroid of all vectors $\mathbf{y}_g$ of these situations.
+This is not necessary an undesirable property, but this implies that the specificities of the character might be hidden if he is often registered in an interaction.
+For example, if the character is frequently with a friend, the character vector will be close to the vector of the couple (if both the character and the couple are counted in the table $\mathbf{O}$).
+By contrast, if we consider that an interaction between two characters is an \emph{emerging situation}, unrelated to prior behaviors of characters, the regressions method described in the next section seems more appropriate to capture every specificities.
 
@@
 where $a > 0$ is an hyperparameter which gives less importance to frequent words as $a \to 0$.
+In this article, we set $a$ to the recommended value of $0.01$.
 Let $\widetilde{\mathbf{X}}$ be the matrix whose columns are vectors $\widetilde{\mathbf{x}}_i$, and $\mathbf{u}$ be its first singular vector.

### 2022-09-07 article/paper1.tex
write article

@@
 
-\section{Results}
+When building a regression model with multiple explanatory variables, it is possible to include every variables and their \emph{interactions}.
+By doing so, we suppose that the effect of raising both variables is not the same as raising each variable independently.
+Regression models seem therefore appropriate to capture specificities of having a particular character-based object in a textual unit: the presence of a character $a$ has a effect on the vocabulary of an unit, the presence of another character $b$ has an other effect, and the presence of the pair $\{a, b\}$ yet a different effect.
+Now, the dependent variable still need to be defined.
+In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the chosen unit embeddings, and each regressions is constructed to predict the $\alpha$-th coordinate of each units by using variables in the $\mathbf{O}$.
+In a matrix notation, all models can be written as
+\begin{align}
+\mathbf{X} = \widetilde{\mathbf{O}} \mathbf{B} + \mathbf{E}, \label{cent_sol}
+\end{align}
+where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{O}}$ the $(n \times (p+1))$ matrix representing $\mathbf{O}$ with an additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{E}$ the $(n \times \alpha)$ error matrix.
+
+Estimates $\widehat{\mathbf{B}} = (\widehat{\beta}_{k\alpha})$ for the intercept and coefficient regressions are in fact the researched embeddings for character-based objects as well as for the intercept representing the general tone of the studied text.
+We therefore denote these estimates with $\mathbf{Y} = (y_{k\alpha})$ in the following, with the convention $y_{0\alpha}$ for intercept coefficients.
+
+As the number of character-objects might be very large, it is a good idea to add a $L^2$ regularization term in the objective function.
+Moreover, the quadratic error rate should also be weighted by the number of tokens in each unit.
+Including all this, we find the solution for our character-based vectors $\mathbf{y}_0, \mathbf{y}_1, \ldots, \mathbf{y}_p$ contained in rows of $\mathbf{Y}$ with
+\begin{equation}
+\mathbf{Y} = (\widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \widetilde{\mathbf{O}} + \lambda \mathbf{I}_{(p+1)})^{-1} \widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}, \label{reg_sol}
+\end{equation}
+where $\textbf{Diag}(\mathbf{f})$ is the diagonal matrix containing weights of units $\mathbf{f} = \left( \frac{n_{i \bullet}}{n_{\bullet \bullet}} \right)$, $\lambda > 1$ is the regularization coefficient, and $\mathbf{I}_{(p+1)}$ is the identity matrix of size $((p+1) \times (p+1))$.
+
+An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) (with a contraction and a different weighting scheme).
+In fact, the regressions method with a regularized term interpolate between the hypothesis where we suppose that every character-object should be considered independently (with $\lambda \to 0$), to the hypothesis of additive mixture between character-objects (with $\lambda \to \infty$), as discussed in section \ref{centroid}.
+Choosing an appropriate $\lambda$ according to the study (how is another, difficult question) might lead to a situation revealing pertinent information about all character-objects.
+
+\section{Case studies}
+\label{case_studies}
+
+\subsection{Datasets}
 

### 2022-09-07 2.2_CA_Hamlet.py
some tests on R&J and Hamlet CA

@@ -14,7 +14,7 @@ min_word_frequency = 5
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 1e-10
+min_occurrences = 2
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter
@@ -116,8 +116,8 @@ axes_vs_occurrences = axes_vs_occurrences.reindex(sorted(axes_vs_occurrences.col
 # ---- Explore the desired relationships
 
 # Objects to explore
-object_names = ["Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean", "Marius-Valjean", "Javert",
-                "Javert-Valjean", "Myriel", "Myriel-Valjean"]
+object_names = ["hamlet-queen", "queen-hamlet", "hamlet-king", "king-hamlet", "hamlet-ophelia", "ophelia-hamlet",
+                "king-queen", "queen-king"]
 if meta_for_occurrences is not None:
     separation_name = list(set(corpus.meta_variables[meta_for_occurrences]))
     for i in range(len(separation_name)):

### 2022-09-07 2.4_CA_Romeo&Juliet.py

@@ -14,7 +14,7 @@ min_word_frequency = 5
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 1e-10
+min_occurrences = 3
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter

### 2022-09-30 1.5_preprocess_Hamlet_old.py
make preprocessing old Hamlet

@@ -1,0 +1,51 @@
+import numpy as np
+import pandas as pd
+import spacy
+from local_functions import process_text
+from tqdm import tqdm
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/Hamlet/Hamlet_old.tsv"
+# Outfile
+output_tsv_path = "corpora/Hamlet/Hamlet_old_tokens.tsv"
+# Language ("fr" or "en")
+language = "en"
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+# Load the dataframe
+corpus_df = pd.read_csv(corpus_tsv_path, sep="\t", index_col=0)
+
+# Get the texts
+texts = corpus_df["text"]
+
+# Load the spacy model depending on language
+if language == "fr":
+    nlp = spacy.load("fr_core_news_lg")
+else:
+    nlp = spacy.load("en_core_web_lg")
+
+# Process the text
+processed_texts = []
+for text in tqdm(texts):
+    text_pp = nlp(text)
+    lemmas_pp = " ".join([word.lemma_ for word in text_pp if word.lemma_.strip() != ""])
+    processed_texts.append(process_text(lemmas_pp))
+
+# Change the text to the processed text
+corpus_df["text"] = processed_texts
+
+# Make the list of characters
+corpus_df = pd.get_dummies(corpus_df, columns=["char_to"], prefix="", prefix_sep="")
+
+# Remove empty lines
+corpus_df = corpus_df[corpus_df["text"] != ""]
+
+# Save the new corpus
+corpus_df.to_csv(output_tsv_path, sep="\t")

### 2022-09-30 2.2_CA_Hamlet_old.py

@@ -1,0 +1,133 @@
+from local_functions import *
+from nltk.corpus import stopwords
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/Hamlet/Hamlet_old.tsv"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+used_stop_words = stopwords.words('english')
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns)]
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Build interactions and add them to data
+interaction_occurrences = build_directed_interactions(list(corpus.texts), corpus.occurrences,
+                                                      max_interaction_degree)
+corpus.occurrences = interaction_occurrences
+
+# Make occurrences binary
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+
+# Make the occurrences across a meta
+corpus.update_occurrences_across_meta(meta_for_occurrences)
+
+# Make sure no units are empty
+corpus.remove_units_without_words()
+#corpus.remove_units_without_occurrences()
+corpus.remove_occurrences_with_frequency(1e-10)
+corpus.remove_words_with_frequency(1e-10)
+
+# Get units weights
+f_row = corpus.n_tokens / corpus.n_tokens.sum()
+
+# -------------------------------
+#  Analyses
+# -------------------------------
+
+# --- CA
+
+# Perform the CA
[…]

### 2022-09-30 1.5_preprocess_Hamlet_old.py
make all lowercase in hamlet old

@@ -47,5 +47,9 @@ corpus_df = pd.get_dummies(corpus_df, columns=["char_to"], prefix="", prefix_sep
 # Remove empty lines
 corpus_df = corpus_df[corpus_df["text"] != ""]
 
+# Lower columns
+corpus_df["char_from"] = corpus_df["char_from"].str.lower()
+corpus_df.columns = corpus_df.columns.str.lower()
+
 # Save the new corpus
 corpus_df.to_csv(output_tsv_path, sep="\t")

### 2022-09-30 2.4_CA_Hamlet_old.py

@@ -6,7 +6,7 @@ from nltk.corpus import stopwords
 # -------------------------------
 
 # Corpus tsv path
-corpus_tsv_path = "corpora/Hamlet/Hamlet_old.tsv"
+corpus_tsv_path = "corpora/Hamlet/Hamlet_old_tokens.tsv"
 # Word vectors to use
 word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
 # Minimum occurrences for words
@@ -45,7 +45,9 @@ corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
 corpus.remove_words_with_frequency(min_word_frequency)
 
 # Build interactions and add them to data
-interaction_occurrences = build_directed_interactions(list(corpus.texts), corpus.occurrences,
+char_from_low = list(corpus.meta_variables.char_from)
+char_from_low = [char_from.lower() for char_from in char_from_low]
+interaction_occurrences = build_directed_interactions(char_from_low, corpus.occurrences,
                                                       max_interaction_degree)
 corpus.occurrences = interaction_occurrences
 

### 2022-09-30 1.5_preprocess_Hamlet_old.py
remove the test on old

@@ -1,55 +1,0 @@
-import numpy as np
-import pandas as pd
-import spacy
-from local_functions import process_text
-from tqdm import tqdm
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/Hamlet/Hamlet_old.tsv"
-# Outfile
-output_tsv_path = "corpora/Hamlet/Hamlet_old_tokens.tsv"
-# Language ("fr" or "en")
-language = "en"
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-# Load the dataframe
-corpus_df = pd.read_csv(corpus_tsv_path, sep="\t", index_col=0)
-
-# Get the texts
-texts = corpus_df["text"]
-
-# Load the spacy model depending on language
-if language == "fr":
-    nlp = spacy.load("fr_core_news_lg")
-else:
-    nlp = spacy.load("en_core_web_lg")
-
-# Process the text
-processed_texts = []
-for text in tqdm(texts):
-    text_pp = nlp(text)
-    lemmas_pp = " ".join([word.lemma_ for word in text_pp if word.lemma_.strip() != ""])
-    processed_texts.append(process_text(lemmas_pp))
-
-# Change the text to the processed text
-corpus_df["text"] = processed_texts
-
-# Make the list of characters
-corpus_df = pd.get_dummies(corpus_df, columns=["char_to"], prefix="", prefix_sep="")
-
-# Remove empty lines
-corpus_df = corpus_df[corpus_df["text"] != ""]
-
-# Lower columns
-corpus_df["char_from"] = corpus_df["char_from"].str.lower()
-corpus_df.columns = corpus_df.columns.str.lower()
-
-# Save the new corpus
-corpus_df.to_csv(output_tsv_path, sep="\t")

### 2022-09-30 2.4_CA_Hamlet_old.py

@@ -1,135 +1,0 @@
-from local_functions import *
-from nltk.corpus import stopwords
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/Hamlet/Hamlet_old_tokens.tsv"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 2
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-used_stop_words = stopwords.words('english')
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns)]
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Build interactions and add them to data
-char_from_low = list(corpus.meta_variables.char_from)
-char_from_low = [char_from.lower() for char_from in char_from_low]
-interaction_occurrences = build_directed_interactions(char_from_low, corpus.occurrences,
-                                                      max_interaction_degree)
-corpus.occurrences = interaction_occurrences
-
-# Make occurrences binary
-corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
-
-# Make the occurrences across a meta
-corpus.update_occurrences_across_meta(meta_for_occurrences)
-
-# Make sure no units are empty
-corpus.remove_units_without_words()
-#corpus.remove_units_without_occurrences()
-corpus.remove_occurrences_with_frequency(1e-10)
-corpus.remove_words_with_frequency(1e-10)
-
-# Get units weights
[…]

### 2022-09-30 article/paper1.tex
format the results

@@
 %% The "title" command^
-\title{Refining character relationships using embeddings of textual units}
+\title{Refining character relationships using embeddings of textual units : a case study on Les Misérables}
 
@@
 For a detailed computation of quantities in CA, see Appendix \ref{ca_details}.
-The position of a unit vector $\mathbf{x}_i$ can be interpreted by mutliple approaches, but we mainly use two here.
 
-The first way to interpret it is to look at the unit-vector position on a particular axis $\alpha$, i.e.
-looking at the component $x_{i\alpha}$.
-This component gives the position of the unit on a particular found "contrast" between units, depending on the chosen $\alpha$, and this contrast will be strong if $p_\alpha$, i.e.
-\emph{the proportion of inertia expressed in $\alpha$}, is high.
-It can further be interpreted by observing the \emph{contribution of each word $j$} composing the axis $\alpha$, i.e.
-$c^w_{j\alpha}$ and looking at the sign of $w_{j\alpha}$.
-Hopefully, by extracting and interpreting the most positive and negative contributing words, the chosen axis can express a particular duality which operates inside the studied text (e.g.
-love-hatred, action-description, lightness-darkness).
-The second method is to directly look at the \emph{similarities} $s_{ij}$ between an unit $i$ and a word $j$, as defined by the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$.
+The relationship between a particular unit $i$ and a word $j$ is expressed through the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$.
 A positive (resp.
@@
 under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
-Observe that in this article, both methods are rather applied to character-based object vectors defined in section (REF), as they lie in the same space as unit vectors.
+Observe that in this article, this similarity is rather computed between word and character-based object vectors, as defined in section (REF), as they lie in the same space as unit vectors.
 
@@
 First, note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
-This analysis is therefore \emph{contrastive}: it highlights unit variations among the studied text.
+This analysis is thus \emph{contrastive}: it highlights unit variations among the studied text.
 This could becomes problematic in order to study a dataset containing multiple texts: units belonging to the same text will have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
@@
 
-\section{Case studies}
-\label{case_studies}
+\section{Case studie : \emph{Les Misérables}}
+\label{case_studie}
 
-\subsection{Datasets}
+For the moment, it is not possible to evaluate the presented methods by the use of some measurements, which would allow to test its validity on various corpora.
+In order to see if the methods give coherent results, we have to carefully scrutinized and compared them with previous knowledge of the studied work.
+For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present here only one case studies: \emph{Les Misérables} by Victor Hugo.
+The choice of this work is motivated by the fact that it is a large corpus, immensely studied, and containing various colorful characters and characters relationships.
+It is therefore a solid choice to clearly illustrate the potential of presented methods.
+
+\subsection{Preprocessing}
+
+The five volumes of \emph{Les Misérables}, in French, were extracted from \emph{Project Gutenberg}\footnote{\url{https://www.gutenberg.org/}}, while headers and footers of each files were manually removed.
+The whole text was lower cased, lemmatized, and stopwords\footnote{from a list made by Jacques Savoy \url{http://members.unine.ch/jacques.savoy/clef/frenchST.txt}} and punctuation were removed.
+Volumes, books, and chapters breaking points were kept for later uses.
+\\
+We chose to use chapter as textual units.
+The table $\mathbf{N}$ (Figure \ref{cont_table}) was build by considering words appearing at least $20$ times in the text and resulted in a table of size $365$ chapters $\times$ $1974$ words.
+\\
+Characters presences were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}} (REF) NER tools.
+In order to unify character and to further refine the detected characters list, we used hand-made lists of character and aliases from NER results.
+It resulted in the detection of 54 characters.
+The character-based objects considered in table $\mathbf{O}$ (Figure \ref{occ_table}) are single character occurrences (54 objects) and character pair co-occurrences (547 objects), resulting in a table of size $365 \times 601$.
+The character co-occurrences count is computed as $o_{ij} = \min(o_{ik}, o_{il})$, where $\{k, l\}$ are characters constituting the pair $j$.
+Note that we also tested experiments with objects consisting in character and character-pairs as found in each volumes (e.g.
+Cosette-Valjean in volume 1 and Cosette-Valjean in volume 2 are now different objects).
+This modified table, containing $1124$ character-based objects, permits to see the evolution in characters and relationships.
+
+\subsection{Methods}
+
+There are two types of methods for unit embeddings, \textbf{CA} (section \ref{ca_method}) and \textbf{WV} (section \ref{wv_method}), as well as two methods for character-based embedding, \textbf{CENT} (section \ref{centroid}) and \textbf{REG} (section \ref{regression}), making a total of 4 possibles ways for obtaining final embeddings.
+The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on French \emph{fastText}\footnote{\url{https://fasttext.cc/docs/en/crawl-vectors.html}} (REF) pre-trained embeddings, giving a $300$-dimensional space.
+The \textbf{CENT} do not have any hyperparameter and we fixed the hyperparameter of the \textbf{REG} methods to $\lambda = 1$ for all experiments.
+\\
+Note that, in addition to having 4 variations for the methods, results can be presented in various ways (e.g.
+most related/unrelated words regarding a character-based object, most related/unrelated character-based object regarding a word), without forgetting that the number of characters, relationships and words in the studied text is considerable.
+Thus, we chose to show here only some examples of formatted results, and leave the reader the choice to consult an exhaustive list of them on our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
+
+\subsection{Results}
+
+\subsubsection{CA unit embeddings}
+
+\begin{table*}[!bh]
+	\centering
+	\tiny
+	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
+		\hline
+		~ & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean & Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline \hline
+		0 & poupée (1.99) & noce (1.32) & fauteuil (0.88) & baron (1.24) & maire (0.52) & baron (1.4) & mouchard (1.79) & mouchard (1.81) & conventionnel (5.28) & chandelier (6.19) \\ \hline
+		1 & sabot (0.95) & baron (1.18) & baron (0.82) & assassin (0.79) & assassin (0.52) & assassin (1.18) & préfecture (1.52) & maire (1.71) & évêque (3.81) & couvert (5.07) \\ \hline
+		2 & voyageur (0.81) & mariage (1.05) & glace (0.8) & théodule (0.78) & forçat (0.51) & prisonnier (1.11) & maire (1.5) & préfecture (1.62) & hôpital (3.25) & gendarme (4.94) \\ \hline
+		3 & noce (0.69) & fauteuil (0.96) & plumet (0.67) & ursule (0.72) & preuve (0.47) & ursule (0.98) & agent (1.35) & preuve (1.26) & oratoire (2.71) & panier (4.36) \\ \hline
+		4 & crainte (0.64) & glace (0.96) & noce (0.64) & écriture (0.65) & gervai (0.47) & alouette (0.96) & police (1.11) & agent (1.18) & curé (2.56) & évêque (4.14) \\ \hline \hline
+		5 & infanterie (-0.59) & cuirassier (-0.59) & cuirassier (-0.58) & division (-0.48) & infanterie (-0.54) & cuirassier (-0.52) & infanterie (-0.57) & infanterie (-0.58) & cuirassier (-0.64) & blücher (-0.78) \\ \hline
+		6 & cuirassier (-0.59) & escadron (-0.58) & infanterie (-0.58) & wellington (-0.47) & cuirassier (-0.53) & wellington (-0.51) & cuirassier (-0.53) & cuirassier (-0.54) & infanterie (-0.61) & charte (-0.76) \\ \hline
+		7 & wellington (-0.57) & brigade (-0.58) & wellington (-0.56) & cuirassier (-0.47) & wellington (-0.52) & infanterie (-0.5) & brigade (-0.52) & brigade (-0.53) & assaillant (-0.57) & artillerie (-0.72) \\ \hline
+		8 & blücher (-0.55) & batterie (-0.56) & brigade (-0.53) & infanterie (-0.47) & blücher (-0.49) & hougomont (-0.49) & hougomont (-0.51) & hougomont (-0.52) & bayonnette (-0.55) & infanterie (-0.68) \\ \hline
+		9 & brigade (-0.54) & division (-0.56) & batterie (-0.53) & plateau (-0.46) & brigade (-0.48) & brigade (-0.49) & wellington (-0.51) & wellington (-0.52) & batterie (-0.54) & émeute (-0.67) \\ \hline
+	\end{tabular}
+\end{table*}
 

### 2022-09-30 2.0_CA_lesMiserables.py

@@ -64,7 +64,7 @@ interaction_occurrences = build_interactions(corpus.occurrences, max_interaction
 corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
 
 # Make occurrences binary
-#corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+corpus.occurrences = corpus.occurrences*(corpus.occurrences >= min_occurrences)
 
 # Make the occurrences across a meta
 corpus.update_occurrences_across_meta(meta_for_occurrences)

### 2022-09-30 CA_lesMiserables.py

@@ -1,0 +1,204 @@
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 1
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter (0.1)
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
+# Make occurrences binary
[…]

### 2022-09-30 CA_lesMiserables.py
format the results for article

@@ -189,10 +189,14 @@ for to_explore_word in word_names:
 words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects.csv")
 # Words vs Objects - centroids (limited char)
 form_lim_words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects_LIMITED.csv")
+form_lim_words_vs_occurrences.iloc[:, :5].to_csv("results/for_article/CA_CENT_words_vs_objects_LIMITED_1.csv")
+form_lim_words_vs_occurrences.iloc[:, 5:].to_csv("results/for_article/CA_CENT_words_vs_objects_LIMITED_2.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/CA_REG_words_vs_objects.csv")
 # Words vs Objects - regression (limited char)
 form_lim_words_vs_regressions.to_csv("results/CA_REG_words_vs_objects_LIMITED.csv")
+form_lim_words_vs_regressions.iloc[:, :5].to_csv("results/for_article/CA_REG_words_vs_objects_LIMITED_1.csv")
+form_lim_words_vs_regressions.iloc[:, 5:].to_csv("results/for_article/CA_REG_words_vs_objects_LIMITED_2.csv")
 
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words.csv")

### 2022-09-30 article/paper1.tex
format the results for article + article continued

@@
 The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on French \emph{fastText}\footnote{\url{https://fasttext.cc/docs/en/crawl-vectors.html}} (REF) pre-trained embeddings, giving a $300$-dimensional space.
-The \textbf{CENT} do not have any hyperparameter and we fixed the hyperparameter of the \textbf{REG} methods to $\lambda = 1$ for all experiments.
+The \textbf{CENT} do not have any hyperparameter and we fixed the hyperparameter of the \textbf{REG} methods to $\lambda = 0.01$ for all experiments.
 \\
@@
 
+The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$.
+We see that with only 5 words, characters and relationships are summarized accurately.
+As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g.
+Cosette, Cosette-Marius, and Cosette-Valjean).
+By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating.
+Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
+
 \begin{table*}[!bh]
 	\centering
-	\tiny
-	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
+	\begin{tabular}{|c|c|c|c|c|}
 		\hline
-		~ & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean & Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline \hline
-		0 & poupée (1.99) & noce (1.32) & fauteuil (0.88) & baron (1.24) & maire (0.52) & baron (1.4) & mouchard (1.79) & mouchard (1.81) & conventionnel (5.28) & chandelier (6.19) \\ \hline
-		1 & sabot (0.95) & baron (1.18) & baron (0.82) & assassin (0.79) & assassin (0.52) & assassin (1.18) & préfecture (1.52) & maire (1.71) & évêque (3.81) & couvert (5.07) \\ \hline
-		2 & voyageur (0.81) & mariage (1.05) & glace (0.8) & théodule (0.78) & forçat (0.51) & prisonnier (1.11) & maire (1.5) & préfecture (1.62) & hôpital (3.25) & gendarme (4.94) \\ \hline
-		3 & noce (0.69) & fauteuil (0.96) & plumet (0.67) & ursule (0.72) & preuve (0.47) & ursule (0.98) & agent (1.35) & preuve (1.26) & oratoire (2.71) & panier (4.36) \\ \hline
-		4 & crainte (0.64) & glace (0.96) & noce (0.64) & écriture (0.65) & gervai (0.47) & alouette (0.96) & police (1.11) & agent (1.18) & curé (2.56) & évêque (4.14) \\ \hline \hline
-		5 & infanterie (-0.59) & cuirassier (-0.59) & cuirassier (-0.58) & division (-0.48) & infanterie (-0.54) & cuirassier (-0.52) & infanterie (-0.57) & infanterie (-0.58) & cuirassier (-0.64) & blücher (-0.78) \\ \hline
-		6 & cuirassier (-0.59) & escadron (-0.58) & infanterie (-0.58) & wellington (-0.47) & cuirassier (-0.53) & wellington (-0.51) & cuirassier (-0.53) & cuirassier (-0.54) & infanterie (-0.61) & charte (-0.76) \\ \hline
-		7 & wellington (-0.57) & brigade (-0.58) & wellington (-0.56) & cuirassier (-0.47) & wellington (-0.52) & infanterie (-0.5) & brigade (-0.52) & brigade (-0.53) & assaillant (-0.57) & artillerie (-0.72) \\ \hline
-		8 & blücher (-0.55) & batterie (-0.56) & brigade (-0.53) & infanterie (-0.47) & blücher (-0.49) & hougomont (-0.49) & hougomont (-0.51) & hougomont (-0.52) & bayonnette (-0.55) & infanterie (-0.68) \\ \hline
-		9 & brigade (-0.54) & division (-0.56) & batterie (-0.53) & plateau (-0.46) & brigade (-0.48) & brigade (-0.49) & wellington (-0.51) & wellington (-0.52) & batterie (-0.54) & émeute (-0.67) \\ \hline
+		Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ \hline
+		poupée (0.7) & \textbf{noce} (1.72) & \textbf{noce} (1.0) & théodule (0.61) & \textbf{mestienne} (0.51) \\ \hline
+		\textbf{noce} (0.68) & \textbf{mariage} (1.31) & \textbf{mestienne} (0.97) & jondrette (0.59) & fossoyeur (0.46) \\ \hline
+		\textbf{mestienne} (0.58) & \textbf{marié} (1.21) & \textbf{mariage} (0.71) & \textbf{ursule} (0.56) & \textbf{accusé} (0.45) \\ \hline
+		\textbf{mariage} (0.48) & marier (1.11) & \textbf{marié} (0.68) & vernon (0.53) & maire (0.39) \\ \hline
+		\textbf{marié} (0.48) & baron (1.0) & corbillard (0.65) & tante (0.52) & jean (0.37) \\ 
+		\hline
 	\end{tabular}
+
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline
+		\textbf{noce} (1.2) & \textbf{accusé} (1.47) & \textbf{accusé} (1.85) & conventionnel (5.03) & chandelier (6.28) \\ \hline
+		\textbf{mariage} (0.85) & arras (1.04) & \textbf{avocat} (1.12) & évêque (3.54) & gendarme (5.06) \\ \hline
+		\textbf{ursule} (0.85) & mouchard (0.97) & \textbf{preuve} (1.1) & oratoire (3.39) & panier (4.72) \\ \hline
+		\textbf{marié} (0.8) & \textbf{avocat} (0.96) & président (1.08) & hôpital (2.57) & couvert (4.64) \\ \hline
+		tableau (0.74) & \textbf{preuve} (0.93) & forçat (1.01) & cathédrale (2.54) & deuil (4.52) \\ \hline
+	\end{tabular}
+
+	\label{CA_CENT_word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-CENT} method, for a selected set of characters and character pairs.
+Words appearing at least two times are in bold.}
+\end{table*}
+
+\begin{table*}[!bh]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ \hline
+		seau (1.23) & amant (0.83) & blessure (0.78) & jondrette (1.76) & matelas (1.02) \\ \hline
+		poupée (0.86) & mariage (0.73) & \textbf{noce} (0.76) & réchaud (1.26) & \textbf{chandelier} (0.87) \\ \hline
+		ravissant (0.7) & entraîner (0.7) & file (0.6) & galetas (1.11) & toulon (0.82) \\ \hline
+		source (0.65) & \textbf{noce} (0.67) & corbillard (0.58) & bouge (1.05) & fossoyeur (0.79) \\ \hline
+		rassurer (0.61) & volupté (0.63) & mestienne (0.58) & tableau (0.93) & pelle (0.76) \\ \hline
+	\end{tabular}
+
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline
+		égout (1.1) & arras (1.09) & accusé (1.04) & conventionnel (2.99) & deuil (1.14) \\ \hline
+		vase (1.08) & roue (0.89) & nier (0.79) & évêque (1.76) & \textbf{chandelier} (1.07) \\ \hline
+		issue (1.07) & bonjour (0.83) & quai (0.54) & cathédrale (1.14) & aveugle (1.01) \\ \hline
+		sable (1.0) & malle (0.8) & avocat (0.53) & prêtre (1.11) & panier (0.94) \\ \hline
+		couloir (0.98) & cabriolet (0.76) & fonction (0.5) & philosophie (1.06) & gendarme (0.89) \\ 
+		\hline
+	\end{tabular}
+
+	\label{CA_REG_word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-REG} method ($\lambda = 0.01$), for a selected set of characters and character pairs.
+Words appearing at least two times are in bold.}
 \end{table*}

### 2022-09-30 CA_lesMiserables.py

@@ -15,11 +15,11 @@ min_word_frequency = 20
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 1
+min_occurrences = 2
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
-# Regularization parameter (0.1)
-regularization_parameter = 1
+# Regularization parameter
+regularization_parameter = 0.01
 
 # -------------------------------
 #  Loading
@@ -64,7 +64,7 @@ interaction_occurrences = build_interactions(corpus.occurrences, max_interaction
 corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
 
 # Make occurrences binary
-corpus.occurrences = corpus.occurrences*(corpus.occurrences >= min_occurrences)
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
 
 # Make the occurrences across a meta
 corpus.update_occurrences_across_meta(meta_for_occurrences)
@@ -189,14 +189,10 @@ for to_explore_word in word_names:
 words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects.csv")
 # Words vs Objects - centroids (limited char)
 form_lim_words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects_LIMITED.csv")
-form_lim_words_vs_occurrences.iloc[:, :5].to_csv("results/for_article/CA_CENT_words_vs_objects_LIMITED_1.csv")
-form_lim_words_vs_occurrences.iloc[:, 5:].to_csv("results/for_article/CA_CENT_words_vs_objects_LIMITED_2.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/CA_REG_words_vs_objects.csv")
 # Words vs Objects - regression (limited char)
 form_lim_words_vs_regressions.to_csv("results/CA_REG_words_vs_objects_LIMITED.csv")
-form_lim_words_vs_regressions.iloc[:, :5].to_csv("results/for_article/CA_REG_words_vs_objects_LIMITED_1.csv")
-form_lim_words_vs_regressions.iloc[:, 5:].to_csv("results/for_article/CA_REG_words_vs_objects_LIMITED_2.csv")
 
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words.csv")
[…]

### 2022-10-01 article/paper1.tex
write article

@@
 
-The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$.
-We see that with only 5 words, characters and relationships are summarized accurately.
-As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g.
-Cosette, Cosette-Marius, and Cosette-Valjean).
-By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating.
-Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
-
 \begin{table*}[!bh]
@@
 	\label{CA_CENT_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-CENT} method, for a selected set of characters and character pairs.
+	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-CENT} method.
 Words appearing at least two times are in bold.}
@@
 	\label{CA_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to objects regarding the \textbf{CA-REG} method ($\lambda = 0.01$), for a selected set of characters and character pairs.
+	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
 Words appearing at least two times are in bold.}
+\end{table*}
+¨
+The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$.
+We see that with only 5 words, characters and relationships are summarized accurately.
+As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g.
+Cosette, Cosette-Marius, and Cosette-Valjean).
+By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating.
+Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
+
+\begin{table*}[!bh]
+	\centering
+	\scalebox{0.9}{	
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		aimer & rue & justice & guerre \\ \hline
+		Dahlia-Fameuil (1.12) & Courfeyrac-Fauchelevent (0.79) & Azelma-Babet (1.09) & Combeferre-Fauchelevent (1.35) \\ \hline
+		Dahlia-Listolier (1.12) & Courfeyrac-Toussaint (0.79) & Azelma-Brujon (1.09) & Feuilly-Valjean (1.27) \\ \hline
+		Fameuil-Zéphine (1.12) & Eponine-Fauchelevent (0.79) & Azelma-Claquesous (1.09) & Feuilly-Marius (1.22) \\ \hline
+		Listolier-Zéphine (1.12) & Eponine-Gavroche (0.79) & Azelma-Magnon (1.09) & Lesgle-Valjean (1.15) \\ \hline
+		Gillenormand-Toussaint (1.11) & Eponine-Pontmercy (0.79) & Azelma-Montparnasse (1.09) & Mabeuf-Valjean (1.15) \\ \hline
+	\end{tabular}
+	}
+	\label{CA_CENT_obj_words}
+	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-CENT} method.}
+\end{table*}
+
+\begin{table*}[!bh]
+	\centering
+	\scalebox{0.9}{	
+		\begin{tabular}{|c|c|c|c|}
+			\hline
+			aimer & rue & justice & guerre \\ \hline
+			Cosette-Marius (0.35) & Courfeyrac (0.37) & Javert-Valjean (0.37) & Grantaire-Pontmercy (0.94) \\ \hline
+			Myriel (0.31) & Grantaire-Prouvaire (0.29) & Champmathieu-Valjean (0.37) & Grantaire (0.56) \\ \hline
+			Basque-Fauchelevent (0.25) & Cosette-Javert (0.26) & Myriel (0.21) & Marius-Pontmercy (0.55) \\ \hline
+			Myriel-Valjean (0.22) & Marius-Prouvaire (0.22) & Grantaire (0.18) & Pontmercy (0.55) \\ \hline
+			Fauchelevent-Gillenormand (0.21) & Enjolras (0.22) & Grantaire-Javert (0.16) & Enjolras (0.49) \\ \hline
+		\end{tabular}
+	}
+	\label{CA_REG_obj_words}
+	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-REG} method ($\lambda = 0.01$).}
 \end{table*}

### 2022-10-01 2.1_CA_lesMiserables_withNetwork.py

@@ -187,3 +187,4 @@ display_char_network(interact_list, interaction_polarity, edge_weights, edge_min
 
 # with open("corpora/LesMiserables_fr/node_pos.pkl", "wb") as pkl_file:
 #     pickle.dump(node_pos, pkl_file)
+

### 2022-10-01 CA_lesMiserables.py

@@ -197,11 +197,11 @@ form_lim_words_vs_regressions.to_csv("results/CA_REG_words_vs_objects_LIMITED.cs
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words.csv")
 # Objects vs Words - centroids (limited words)
-form_lim_occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words_LIMITED.csv")
+form_lim_occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words_LIMITED.csv", index=False)
 # Objects vs Words - regression
 regressions_vs_words.to_csv("results/CA_REG_objects_vs_words.csv")
 # Objects vs Words - regression (limited words)
-form_lim_regressions_vs_words.to_csv("results/CA_REG_objects_vs_words_LIMITED.csv")
+form_lim_regressions_vs_words.to_csv("results/CA_REG_objects_vs_words_LIMITED.csv", index=False)
 
 # -- For article
 

### 2022-10-01 article/paper1.tex
write article

@@
 
+The next results can be found in Table 5 and Table 6.
+In fact, they are just the transposed results from previous table, with the top 5 characters based objects displayed for a set of words.
+This type of results can be seen as "queries" an user could make in order to find the most associated objects.
+We chose here to show the most associated objects to the words "aimer", "rue", "justice" and "guerre", as they represent some of the major topic of the book.
+Surprisingly, in this task, the \textbf{CA-CENT} method give quite poor results compared to the \textbf{CA-REG}.
+In the latter, the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
+Thus this seems like convincing results.
+
 \section{Conclusion}

### 2022-10-03 article/paper1.tex
create networks

@@
 This type of results can be seen as "queries" an user could make in order to find the most associated objects.
-We chose here to show the most associated objects to the words "aimer", "rue", "justice" and "guerre", as they represent some of the major topic of the book.
+We chose here to show the most associated objects to words "aimer", "rue", "justice" and "guerre", as they represent some of the major topics of the book.
 Surprisingly, in this task, the \textbf{CA-CENT} method give quite poor results compared to the \textbf{CA-REG}.
 In the latter, the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
-Thus this seems like convincing results.
+These type of results can also be represented through weighted signed networks, as found in Figure 1.
+The network structure represent the number of time characters are detected together, and remains unchanged regarding the word query, and the signed weights (edge color) display similarities between character-pairs (edges) and the studied word (the query).
+This representation gives a quick visual support in order to explore the studied work.
+
+\begin{figure*}[!bh]
+	\centering
+	\includegraphics[width=0.45\textwidth]{fig/aimer.png} \includegraphics[width=0.45\textwidth]{fig/rue.png}
+	\includegraphics[width=0.45\textwidth]{fig/justice.png}
+	\includegraphics[width=0.45\textwidth]{fig/guerre.png}
+	\label{networks}
+	\caption{Resulting weighted networks, between main characters, with examples of word queries ("aimer", "rue", "justice", and "guerre").
+These networks are computed with \textbf{CA-REG} method ($\lambda = 0.01$).
+Red indicate positive affinity, blue negative one, and edge width the number of detected interactions between characters.}
+\end{figure*}
 

### 2022-10-03 CA_lesMiserables_Networks.py

@@ -16,7 +16,7 @@ min_word_frequency = 20
 # Max interactions
 max_interaction_degree = 2
 # The minimum occurrences for an object to be considered
-min_occurrences = 2
+min_occurrences = 1
 # Use a meta variable to build occurrences (None for original)
 meta_for_occurrences = None
 # Regularization parameter (0.1)
@@ -77,7 +77,6 @@ corpus.update_occurrences_across_meta(meta_for_occurrences)
 
 # Make sure no units are empty
 corpus.remove_units_without_words()
-#corpus.remove_units_without_occurrences()
 corpus.remove_occurrences_with_frequency(1e-10)
 corpus.remove_words_with_frequency(1e-10)
 
@@ -122,40 +121,11 @@ words_vs_regressions = pd.DataFrame(col_coord @ regression_coord.T, index=corpus
 words_vs_regressions = words_vs_regressions.reindex(sorted(words_vs_regressions.columns), axis=1)
 regression_vs_words = words_vs_regressions.transpose()
 
-# ---- Examine relations with axes
-
-regressions_vs_axes = pd.DataFrame(regression_coord, index=["intercept"] + list(corpus.occurrences.columns))
-occurrences_vs_axes = pd.DataFrame(occurrence_coord, index=list(corpus.occurrences.columns))
-axes_vs_regressions = regressions_vs_axes.transpose()
-axes_vs_regressions = axes_vs_regressions.reindex(sorted(axes_vs_regressions.columns), axis=1)
-axes_vs_occurrences = occurrences_vs_axes.transpose()
-axes_vs_occurrences = axes_vs_occurrences.reindex(sorted(axes_vs_occurrences.columns), axis=1)
-
-# ---- Explore the desired relationships
-
-# Objects to explore
-object_names = ["T1", "T2", "T3", "T4", "T5", "Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean",
-                "Marius-Valjean", "Javert", "Javert-Valjean", "Myriel", "Myriel-Valjean"]
-if meta_for_occurrences is not None:
-    separation_name = list(set(corpus.meta_variables[meta_for_occurrences]))
-    for i in range(len(separation_name)):
-        separation_name.extend([f"{obj}_{i+1}" for obj in object_names])
-    object_names.extend(separation_name)
-
-# The subset of object
-present_object_names = []
-for obj in object_names:
-    if obj in words_vs_regressions.columns:
-        present_object_names.append(obj)
-
[…]

### 2022-10-03 article/paper1.tex
create timeline with CA

@@
 
+\begin{figure*}[!bh]
+	\centering
+	\includegraphics[width=0.45\textwidth]{fig/aimer.png} \includegraphics[width=0.45\textwidth]{fig/rue.png}
+	\includegraphics[width=0.45\textwidth]{fig/justice.png}
+	\includegraphics[width=0.45\textwidth]{fig/guerre.png}
+	\label{networks}
+	\caption{Resulting weighted networks, between main characters, with examples of word queries ("aimer", "rue", "justice", and "guerre").
+These networks are computed with \textbf{CA-REG} method ($\lambda = 0.01$).
+Red indicate positive affinity, blue negative one, and edge width the number of detected interactions between characters.}
+\end{figure*}
+
 The next results can be found in Table 5 and Table 6.
@@
 
-\begin{figure*}[!bh]
+\subsubsection{WV unit embeddings}
+
+% ----------------------------------------------
+
+\begin{table*}[!bh]
 	\centering
-	\includegraphics[width=0.45\textwidth]{fig/aimer.png} \includegraphics[width=0.45\textwidth]{fig/rue.png}
-	\includegraphics[width=0.45\textwidth]{fig/justice.png}
-	\includegraphics[width=0.45\textwidth]{fig/guerre.png}
-	\label{networks}
-	\caption{Resulting weighted networks, between main characters, with examples of word queries ("aimer", "rue", "justice", and "guerre").
-These networks are computed with \textbf{CA-REG} method ($\lambda = 0.01$).
-Red indicate positive affinity, blue negative one, and edge width the number of detected interactions between characters.}
-\end{figure*}
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		T1 & T2 & T3 & T4 & T5 \\ \hline
+		huissier (1.4) & cuirassier (3.38) & gamin (1.92) & émeute (1.48) & sable (3.04) \\ \hline
+		hôte (1.11) & infanterie (2.9) & mine (1.38) & révolte (0.86) & berge (2.32) \\ \hline
+		arras (0.92) & sacrement (2.69) & farce (0.81) & bourgeoisie (0.84) & égout (2.16) \\ \hline
+		lampe (0.91) & brigade (2.41) & ignorance (0.74) & populaire (0.82) & voûte (1.9) \\ \hline
+		montreuil (0.81) & division (2.4) & jondrette (0.7) & insurrection (0.81) & vase (1.89) \\ 
+		\hline
+	\end{tabular}
+
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Cosette-Valjean\_1 & Cosette-Valjean\_2 & Cosette-Valjean\_3 & Cosette-Valjean\_4 & Cosette-Valjean\_5 \\ \hline
+		maladie (0.49) & façade (0.68) & - & promenade (0.5) & noce (1.27) \\ \hline
+		médecin (0.48) & corbillard (0.66) & - &chaîne (0.47) & marié (0.93) \\ \hline
+		demain (0.33) & mestienne (0.6) & - & blessure (0.46) & mardi (0.89) \\ \hline
+		surprise (0.28) & bâtiment (0.56) & - &tuyau (0.45) & mariage (0.86) \\ \hline
+		auprès (0.28) & cul (0.55) & - &luxembourg (0.44) & file (0.65) \\ \hline
+	\end{tabular}
+
+	\label{CA_TIME_REG_word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) vs volumes objects (top) and Cosette-Valjean relationship as found in each tome, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
+Note that no co-occurrence between Cosette and Valjean were automatically found in volume 3.}
+\end{table*}
 

### 2022-10-03 CA_lesMiserables_Timeline.py

@@ -1,0 +1,224 @@
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = "tome"
+# Regularization parameter
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
[…]

### 2022-10-03 article/paper1.tex
next results

@@
 \usepackage{url}
+\usepackage{array,multirow,graphicx}
+\usepackage{float}
 
@@
 \\
-Note that, in addition to having 4 variations for the methods, results can be presented in various ways (e.g.
-most related/unrelated words regarding a character-based object, most related/unrelated character-based object regarding a word), without forgetting that the number of characters, relationships and words in the studied text is considerable.
-Thus, we chose to show here only some examples of formatted results, and leave the reader the choice to consult an exhaustive list of them on our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
+Note that, in addition to having 4 variations for the methods and 2 sets of character-based objects (characters and character-pairs for the whole book, or discretized by volumes), results can be presented in various ways (e.g.
+most related words regarding a character-based object, most related character-based object regarding a word), without forgetting that the number of characters, relationships and words in the studied text is considerable.
+Thus, we chose to show here only some examples of results, and leave the reader the choice to consult an exhaustive list of them on our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
 
@@
 
-\subsubsection{CA unit embeddings}
+\subsubsection{The most associated words for a subset of characters-based objects}
+
+%------------------------------
+
+\begin{table*}[!h]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{CA-CENT}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\cline{2-6}
+		& poupée (0.7) & \textbf{noce} (1.72) & \textbf{noce} (1.0) & théodule (0.61) & \textbf{mestienne} (0.51) \\
+		& \textbf{noce} (0.68) & \textbf{mariage} (1.31) & \textbf{mestienne} (0.97) & jondrette (0.59) & fossoyeur (0.46) \\
+		& \textbf{mestienne} (0.58) & \textbf{marié} (1.21) & \textbf{mariage} (0.71) & \textbf{ursule} (0.56) & \textbf{accusé} (0.45) \\
+		& \textbf{mariage} (0.48) & marier (1.11) & \textbf{marié} (0.68) & vernon (0.53) & maire (0.39) \\
+		& \textbf{marié} (0.48) & baron (1.0) & corbillard (0.65) & tante (0.52) & jean (0.37) \\ 
+		\cline{2-6}
+		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		\cline{2-6}
+		& \textbf{noce} (1.2) & \textbf{accusé} (1.47) & \textbf{accusé} (1.85) & conventionnel (5.03) & chandelier (6.28) \\
+		& \textbf{mariage} (0.85) & arras (1.04) & \textbf{avocat} (1.12) & évêque (3.54) & gendarme (5.06) \\
+		& \textbf{ursule} (0.85) & mouchard (0.97) & \textbf{preuve} (1.1) & oratoire (3.39) & panier (4.72) \\
+		& \textbf{marié} (0.8) & \textbf{avocat} (0.96) & président (1.08) & hôpital (2.57) & couvert (4.64) \\
+		& tableau (0.74) & \textbf{preuve} (0.93) & forçat (1.01) & cathédrale (2.54) & deuil (4.52) \\
+		\hline
+		\hline
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{CA-REG}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\cline{2-6}
+		& seau (1.23) & amant (0.83) & blessure (0.78) & jondrette (1.76) & matelas (1.02) \\
+		& poupée (0.86) & mariage (0.73) & \textbf{noce} (0.76) & réchaud (1.26) & \textbf{chandelier} (0.87) \\
+		& ravissant (0.7) & entraîner (0.7) & file (0.6) & galetas (1.11) & toulon (0.82) \\
+		& source (0.65) & \textbf{noce} (0.67) & corbillard (0.58) & bouge (1.05) & fossoyeur (0.79) \\
+		& rassurer (0.61) & volupté (0.63) & mestienne (0.58) & tableau (0.93) & pelle (0.76) \\ 
+		\cline{2-6}
+		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		\cline{2-6}
+		& égout (1.1) & arras (1.09) & accusé (1.04) & conventionnel (2.99) & deuil (1.14) \\ 
+		& vase (1.08) & roue (0.89) & nier (0.79) & évêque (1.76) & \textbf{chandelier} (1.07) \\ 
+		& issue (1.07) & bonjour (0.83) & quai (0.54) & cathédrale (1.14) & aveugle (1.01) \\ 
+		& sable (1.0) & malle (0.8) & avocat (0.53) & prêtre (1.11) & panier (0.94) \\
+		& couloir (0.98) & cabriolet (0.76) & fonction (0.5) & philosophie (1.06) & gendarme (0.89) \\ 
+		\hline
+		\hline
+		\hline
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{WV-CENT}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\cline{2-6}
+		& \textbf{jean} (0.34) & aimer (0.38) & \textbf{jean} (0.6) & embrasser (0.36) & \textbf{jean} (0.56) \\
+		& dormir (0.28) & rêver (0.34) & \textbf{jacques} (0.3) & \textbf{essayer} (0.36) & \textbf{habiller} (0.27) \\ 
+		& regarder (0.26) & \textbf{vouloir} (0.32) & \textbf{philippe} (0.26) & \textbf{avouer} (0.36) & \textbf{poser} (0.26) \\
+		& \textbf{habiller} (0.26) & douter (0.32) & \textbf{habiller} (0.26) & \textbf{vouloir} (0.35) & \textbf{jacques} (0.26) \\
+		& \textbf{voir} (0.25) & \textbf{avouer} (0.32) & \textbf{pantalon} (0.25) & \textbf{voir} (0.35) & \textbf{pantalon} (0.25) \\
+		\cline{2-6}
+		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		\cline{2-6}
+		& \textbf{jean} (0.35) & \textbf{saisir} (0.34) & \textbf{jean} (0.54) & \textbf{évêque} (0.59) & \textbf{évêque} (0.55) \\
+		& questionner (0.31) & \textbf{jean} (0.34) & denis (0.31) & \textbf{archevêque} (0.52) & \textbf{archevêque} (0.46) \\
+		& \textbf{essayer} (0.31) & placer (0.31) & \textbf{jacques} (0.3) & \textbf{prêtre} (0.45) & \textbf{prêtre} (0.42) \\
+		& oser (0.31) & retirer (0.29) & \textbf{saisir} (0.3) & \textbf{abbé} (0.39) & âme (0.42) \\
+		& \textbf{poser} (0.29) & dégager (0.29) & \textbf{philippe} (0.28) & souverain (0.38) & \textbf{abbé} (0.39) \\
+		\hline
+		\hline
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{WV-REG}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\cline{2-6}
+		& contempler (0.29) & éternel (0.35) & \textbf{rue} (0.44) & regarder (0.38) & \textbf{jean} (0.56) \\
+		& emplir (0.29) & \textbf{amour} (0.35) & \textbf{jean} (0.41) & voir (0.36) & pantalon (0.28) \\
+		& doucement (0.27) & humanité (0.34) & faubourg (0.41) & refermer (0.34) & jacques (0.26) \\
+		& envelopper (0.26) & \textbf{âme} (0.32) & \textbf{boulevard} (0.41) & \textbf{glisser} (0.34) & philippe (0.23) \\
+		& illuminer (0.26) & vérité (0.32) & quartier (0.34) & poser (0.31) & \textbf{glisser} (0.23) \\ 
+		\cline{2-6}
+		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		\cline{2-6}
+		& \textbf{rue} (0.35) & serrer (0.34) & \textbf{rue} (0.35) & \textbf{évêque} (0.43) & ange (0.37) \\
+		& \textbf{boulevard} (0.35) & \textbf{glisser} (0.34) & \textbf{boulevard} (0.34) & divin (0.4) & \textbf{évêque} (0.31) \\
+		& souterrain (0.35) & forcer (0.34) & autorité (0.33) & humble (0.39) & \textbf{âme} (0.31) \\
+		& bastille (0.35) & bouger (0.33) & civil (0.33) & bonté (0.38) & \textbf{amour} (0.29) \\
+		& carrefour (0.34) & aller (0.32) & loi (0.33) & archevêque (0.37) & aurore (0.28) \\
+		\hline
+	\end{tabular}
+
+	\label{word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.
+Words appearing at least two times within the same method are in bold.}
+\end{table*}
+
+%------------------------------
+
+The first results in this section is to examine the most associated words with a subset of character-based objects, as measured by the similarities defined in section \ref{unit_embeddings}.
+Results can be found in Table 3 for all methods.
+
+We can first observe that \textbf{CA} methods seems to summarize objects with a vocabulary closer to the work, while \textbf{WV} methods tend to use more general concepts, with notably more verbs.
+This behavior can be traced back to the nature of embeddings: in the \textbf{WV} embedding, word-vectors are fixed and do not consider the actual frequencies of words found in the studied corpora.
+A character could be highly similar to a word appearing only a few times in the corpus if this word is located near the vocabulary associated with this character.
+By contrast, \textbf{CA} will generally takes into account word frequencies, and balance them with specificities, in order to describe a character.
+
+Another remark can be made about the difference between \textbf{CENT} methods and \textbf{REG} methods.
+As expected, we see that the \textbf{CENT} methods reveal their additive construction between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g.
+Cosette, Cosette-Marius, and Cosette-Valjean).
+By constrast, the \textbf{REG} methods display more "perpendicular" descriptions of objects, with less words repeating.
+While
+
+Note that we did not show here the least associated words with each object, as they are frequently the same for all methods and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
+
+Overall, we find that the \textbf{CA-REG} method gives the most satisfying results, with pertinent words associated with each character-based object, and an high variety in the choice of words.
+
+\subsubsection{The most associated characters-based objects for a subset of words}
+
+%------------------------------
 
@@
 	\centering
+	\scalebox{0.82}{	
 	\begin{tabular}{|c|c|c|c|c|}
 		\hline
-		Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ \hline
-		poupée (0.7) & \textbf{noce} (1.72) & \textbf{noce} (1.0) & théodule (0.61) & \textbf{mestienne} (0.51) \\ \hline
-		\textbf{noce} (0.68) & \textbf{mariage} (1.31) & \textbf{mestienne} (0.97) & jondrette (0.59) & fossoyeur (0.46) \\ \hline
-		\textbf{mestienne} (0.58) & \textbf{marié} (1.21) & \textbf{mariage} (0.71) & \textbf{ursule} (0.56) & \textbf{accusé} (0.45) \\ \hline
-		\textbf{mariage} (0.48) & marier (1.11) & \textbf{marié} (0.68) & vernon (0.53) & maire (0.39) \\ \hline
-		\textbf{marié} (0.48) & baron (1.0) & corbillard (0.65) & tante (0.52) & jean (0.37) \\ 
+		& aimer & rue & justice & guerre \\ \hline
 		\hline
-	\end{tabular}
-
-	\begin{tabular}{|c|c|c|c|c|}
+		\parbox[t]{2mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{\textbf{CA-CENT}}}} & Dahlia-Fameuil (1.12) & Courfeyrac-Fauchelevent (0.79) & Azelma-Babet (1.09) & Combeferre-Fauchelevent (1.35) \\
+		& Dahlia-Listolier (1.12) & Courfeyrac-Toussaint (0.79) & Azelma-Brujon (1.09) & Feuilly-Valjean (1.27) \\
+		& Fameuil-Zéphine (1.12) & Eponine-Fauchelevent (0.79) & Azelma-Claquesous (1.09) & Feuilly-Marius (1.22) \\
+		& Listolier-Zéphine (1.12) & Eponine-Gavroche (0.79) & Azelma-Magnon (1.09) & Lesgle-Valjean (1.15) \\
+		& Gillenormand-Toussaint (1.11) & Eponine-Pontmercy (0.79) & Azelma-Montparnasse (1.09) & Mabeuf-Valjean (1.15) \\ 
 		\hline
-		Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline
-		\textbf{noce} (1.2) & \textbf{accusé} (1.47) & \textbf{accusé} (1.85) & conventionnel (5.03) & chandelier (6.28) \\ \hline
-		\textbf{mariage} (0.85) & arras (1.04) & \textbf{avocat} (1.12) & évêque (3.54) & gendarme (5.06) \\ \hline
-		\textbf{ursule} (0.85) & mouchard (0.97) & \textbf{preuve} (1.1) & oratoire (3.39) & panier (4.72) \\ \hline
-		\textbf{marié} (0.8) & \textbf{avocat} (0.96) & président (1.08) & hôpital (2.57) & couvert (4.64) \\ \hline
-		tableau (0.74) & \textbf{preuve} (0.93) & forçat (1.01) & cathédrale (2.54) & deuil (4.52) \\ \hline
-	\end{tabular}
-
-	\label{CA_CENT_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-CENT} method.
-Words appearing at least two times are in bold.}
-\end{table*}
-
-\begin{table*}[!bh]
-	\centering
-	\begin{tabular}{|c|c|c|c|c|}
 		\hline
-		Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ \hline
-		seau (1.23) & amant (0.83) & blessure (0.78) & jondrette (1.76) & matelas (1.02) \\ \hline
-		poupée (0.86) & mariage (0.73) & \textbf{noce} (0.76) & réchaud (1.26) & \textbf{chandelier} (0.87) \\ \hline
-		ravissant (0.7) & entraîner (0.7) & file (0.6) & galetas (1.11) & toulon (0.82) \\ \hline
-		source (0.65) & \textbf{noce} (0.67) & corbillard (0.58) & bouge (1.05) & fossoyeur (0.79) \\ \hline
-		rassurer (0.61) & volupté (0.63) & mestienne (0.58) & tableau (0.93) & pelle (0.76) \\ \hline
-	\end{tabular}
-
-	\begin{tabular}{|c|c|c|c|c|}
+		\parbox[t]{2mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{\textbf{CA-REG}}}} & Cosette-Marius (0.35) & Courfeyrac (0.37) & Javert-Valjean (0.37) & Grantaire-Pontmercy (0.94) \\
+		& Myriel (0.31) & Grantaire-Prouvaire (0.29) & Champmathieu-Valjean (0.37) & Grantaire (0.56) \\
+		& Basque-Fauchelevent (0.25) & Cosette-Javert (0.26) & Myriel (0.21) & Marius-Pontmercy (0.55) \\
+		& Myriel-Valjean (0.22) & Marius-Prouvaire (0.22) & Grantaire (0.18) & Pontmercy (0.55) \\
+		& Fauchelevent-Gillenormand (0.21) & Enjolras (0.22) & Grantaire-Javert (0.16) & Enjolras (0.49) \\ 
 		\hline
-		Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\ \hline
-		égout (1.1) & arras (1.09) & accusé (1.04) & conventionnel (2.99) & deuil (1.14) \\ \hline
-		vase (1.08) & roue (0.89) & nier (0.79) & évêque (1.76) & \textbf{chandelier} (1.07) \\ \hline
-		issue (1.07) & bonjour (0.83) & quai (0.54) & cathédrale (1.14) & aveugle (1.01) \\ \hline
-		sable (1.0) & malle (0.8) & avocat (0.53) & prêtre (1.11) & panier (0.94) \\ \hline
-		couloir (0.98) & cabriolet (0.76) & fonction (0.5) & philosophie (1.06) & gendarme (0.89) \\ 
 		\hline
-	\end{tabular}
-
-	\label{CA_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
-Words appearing at least two times are in bold.}
-\end{table*}
-¨
-The first results in this section is to examine the most associated words with a subset of character-based objects, which can be found in Table 3 for \textbf{CA-CENT} and Table 4 for \textbf{CA-REG} with $\lambda = 0.01$.
-We see that with only 5 words, characters and relationships are summarized accurately.
-As expected, we see that the \textbf{CA-CENT} reveals its additive nature between characters and relationships: words used to describe a relationship rob off on their characters descriptions (see e.g.
-Cosette, Cosette-Marius, and Cosette-Valjean).
-By constrast, the \textbf{CA-REG} method displays more "perpendicular" descriptions of objects, with less words repeating.
-Note that we did not show here the least associated words with each object, as they are frequently the same and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
-
-\begin{table*}[!bh]
-	\centering
-	\scalebox{0.9}{	
-	\begin{tabular}{|c|c|c|c|}
 		\hline
-		aimer & rue & justice & guerre \\ \hline
-		Dahlia-Fameuil (1.12) & Courfeyrac-Fauchelevent (0.79) & Azelma-Babet (1.09) & Combeferre-Fauchelevent (1.35) \\ \hline
-		Dahlia-Listolier (1.12) & Courfeyrac-Toussaint (0.79) & Azelma-Brujon (1.09) & Feuilly-Valjean (1.27) \\ \hline
-		Fameuil-Zéphine (1.12) & Eponine-Fauchelevent (0.79) & Azelma-Claquesous (1.09) & Feuilly-Marius (1.22) \\ \hline
-		Listolier-Zéphine (1.12) & Eponine-Gavroche (0.79) & Azelma-Magnon (1.09) & Lesgle-Valjean (1.15) \\ \hline
-		Gillenormand-Toussaint (1.11) & Eponine-Pontmercy (0.79) & Azelma-Montparnasse (1.09) & Mabeuf-Valjean (1.15) \\ \hline
+		\parbox[t]{2mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{\textbf{WV-CENT}}}} & Cosette-Marius (0.38) & Grantaire-Prouvaire (0.57) & Azelma-Babet (0.34) & Grantaire (0.32) \\
+		& Fantine-Marius (0.34) & Marius-Prouvaire (0.54) & Azelma-Brujon (0.34) & Combeferre-Lesgle (0.32) \\
+		& Fantine-Pontmercy (0.34) & Cosette-Javert (0.43) & Azelma-Claquesous (0.34) & Feuilly-Lesgle (0.25) \\
+		& Basque-Fauchelevent (0.34) & Magnon-Monsieur Thénardier (0.37) & Azelma-Magnon (0.34) & Combeferre-Marius (0.25) \\
+		& Prouvaire-Valjean (0.33) & Gavroche (0.36) & Azelma-Montparnasse (0.34) & Combeferre-Grantaire (0.25) \\ 
+		\hline
+		\hline
+		\parbox[t]{2mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{\textbf{WV-REG}}}} & Prouvaire-Valjean (0.34) & Grantaire-Prouvaire (0.8) & Champmathieu-Valjean (0.38) & Grantaire-Pontmercy (0.39) \\
+		& Champmathieu-Chenildieu (0.31) & Marius-Prouvaire (0.77) & Azelma-Brujon (0.35) & Enjolras-Marius (0.35) \\
+		& Brevet-Chenildieu (0.31) & Courfeyrac (0.66) & Azelma-Claquesous (0.35) & Grantaire (0.31) \\
+		& Brevet-Cochepaille (0.31) & Cosette-Javert (0.64) & Azelma-Magnon (0.35) & Combeferre-Lesgle (0.31) \\
+		& Champmathieu-Cochepaille (0.31) & Prouvaire (0.63) & Azelma-Montparnasse (0.35) & Cosette-Gavroche (0.27) \\ \hline
 	\end{tabular}
@@
 	\label{CA_CENT_obj_words}
-	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-CENT} method.}
+	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.}
 \end{table*}
 
-\begin{table*}[!bh]
-	\centering
-	\scalebox{0.9}{	
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			aimer & rue & justice & guerre \\ \hline
-			Cosette-Marius (0.35) & Courfeyrac (0.37) & Javert-Valjean (0.37) & Grantaire-Pontmercy (0.94) \\ \hline
-			Myriel (0.31) & Grantaire-Prouvaire (0.29) & Champmathieu-Valjean (0.37) & Grantaire (0.56) \\ \hline
-			Basque-Fauchelevent (0.25) & Cosette-Javert (0.26) & Myriel (0.21) & Marius-Pontmercy (0.55) \\ \hline
-			Myriel-Valjean (0.22) & Marius-Prouvaire (0.22) & Grantaire (0.18) & Pontmercy (0.55) \\ \hline
-			Fauchelevent-Gillenormand (0.21) & Enjolras (0.22) & Grantaire-Javert (0.16) & Enjolras (0.49) \\ \hline
-		\end{tabular}
-	}
-	\label{CA_REG_obj_words}
-	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words regarding the \textbf{CA-REG} method ($\lambda = 0.01$).}
-\end{table*}
+%------------------------------
+
+%------------------------------
 
@@
 
-The next results can be found in Table 5 and Table 6.
-In fact, they are just the transposed results from previous table, with the top 5 characters based objects displayed for a set of words.
-This type of results can be seen as "queries" an user could make in order to find the most associated objects.
+%------------------------------
+
+These results are extracted from the transposed table from the last, and display the most associated character-based objects to a selected set of words.
+They can be found in Table 4.
+This type of results can be seen as "queries", made from a single word, which output the highest objects in the work related to that query.
 We chose here to show the most associated objects to words "aimer", "rue", "justice" and "guerre", as they represent some of the major topics of the book.
-Surprisingly, in this task, the \textbf{CA-CENT} method give quite poor results compared to the \textbf{CA-REG}.
-In the latter, the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
-These type of results can also be represented through weighted signed networks, as found in Figure 1.
+In this task, the \textbf{CA-REG} again seems to display the most satifying results: the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
+
+Note that another way to represent these results is through weighted signed networks, as found in Figure 1 (for \textbf{CA-REG}).
 The network structure represent the number of time characters are detected together, and remains unchanged regarding the word query, and the signed weights (edge color) display similarities between character-pairs (edges) and the studied word (the query).
@@
 
-\subsubsection{WV unit embeddings}
+While somewhat inferior with the select set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
 

### 2022-10-03 WV_lesMiserables.py

@@ -1,0 +1,260 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
[…]

### 2022-10-10 article/paper1.tex
suppress limited results, create timeline for WV

@@
 Volumes, books, and chapters breaking points were kept for later uses.
-\\
+
 We chose to use chapter as textual units.
 The table $\mathbf{N}$ (Figure \ref{cont_table}) was build by considering words appearing at least $20$ times in the text and resulted in a table of size $365$ chapters $\times$ $1974$ words.
-\\
+
 Characters presences were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}} (REF) NER tools.
@@
 The character co-occurrences count is computed as $o_{ij} = \min(o_{ik}, o_{il})$, where $\{k, l\}$ are characters constituting the pair $j$.
-Note that we also tested experiments with objects consisting in character and character-pairs as found in each volumes (e.g.
-Cosette-Valjean in volume 1 and Cosette-Valjean in volume 2 are now different objects).
-This modified table, containing $1124$ character-based objects, permits to see the evolution in characters and relationships.
+
+Note that, in section \ref{diachronic}, we also tested experiments with objects consisting in character and character-pairs as found in each volumes (e.g.
+Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects) with the addition of volume constants ($V_i=1$ in volume $i$, $V_i=0$ in the other volumes) in order to isolate specific volume vocabulary.
+This new table $\mathbf{O}_\text{vol}$, containing $1124$ character-based objects, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
 
@@
 \\
-Note that, in addition to having 4 variations for the methods and 2 sets of character-based objects (characters and character-pairs for the whole book, or discretized by volumes), results can be presented in various ways (e.g.
-most related words regarding a character-based object, most related character-based object regarding a word), without forgetting that the number of characters, relationships and words in the studied text is considerable.
-Thus, we chose to show here only some examples of results, and leave the reader the choice to consult an exhaustive list of them on our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
+Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{O}$ and $\mathbf{O}_\text{vol}$, and a considerable number of characters and character relationships, results can also be presented in various ways (similarities between character-based objects, between words, between objects and words, etc.).
+Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding character-based objects (section \ref{words}), the 5 most related character-based object regarding a subset of words (section \ref{objects})), and a diachronic study of top associated words for a subset of character-based objects (section \ref{diachronic}).
+We invite curious readers to consult these results for all words and objects, which can be found in our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
 
@@
 \subsubsection{The most associated words for a subset of characters-based objects}
+\label{words}
 
@@
 By constrast, the \textbf{REG} methods display more "perpendicular" descriptions of objects, with less words repeating.
-While
 
@@
 \subsubsection{The most associated characters-based objects for a subset of words}
+\label{objects}
 
@@
 	\label{networks}
-	\caption{Resulting weighted networks, between main characters, with examples of word queries ("aimer", "rue", "justice", and "guerre").
+	\caption{Resulting weighted and signed networks between main characters, with examples of word queries ("aimer", "rue", "justice", and "guerre").
 These networks are computed with \textbf{CA-REG} method ($\lambda = 0.01$).
-Red indicate positive affinity, blue negative one, and edge width the number of detected interactions between characters.}
+Red indicate positive affinity, blue negative affinity, and edge width is proportional to the number of detected interactions between characters.}
 \end{figure*}
@@
 In this task, the \textbf{CA-REG} again seems to display the most satifying results: the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
+While somewhat inferior with the select set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
+It should also give interesting results when comparing different corpora, due to the fixed nature of word-vectors, but case studies concerning multiple corpora are outside the scope of this article.
 
 Note that another way to represent these results is through weighted signed networks, as found in Figure 1 (for \textbf{CA-REG}).
-The network structure represent the number of time characters are detected together, and remains unchanged regarding the word query, and the signed weights (edge color) display similarities between character-pairs (edges) and the studied word (the query).
-This representation gives a quick visual support in order to explore the studied work.
-
-While somewhat inferior with the select set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
+The network structure represent the number of time characters are detected together (which do not depend on the query), and the signed weights (edge color) display similarities between character relationship (edges) and the queried word.
+This representation gives a quick visual support in order to explore the studied work and could be implemented as a standalone program.
 
@@
 
+	\label{CA_TIME_REG_word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) vs volumes objects (top) and Cosette-Valjean relationship as found in each tome, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
+Note that no co-occurrence between Cosette and Valjean were automatically found in volume 3.}
+\end{table*}
+
+\subsubsection{A diachronic study of the most associated words for a subset of character-based objects}
+\label{diachronic}
+
+\begin{table*}[!h]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{CA-CENT}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\cline{2-6}
+		& poupée (0.7) & \textbf{noce} (1.72) & \textbf{noce} (1.0) & théodule (0.61) & \textbf{mestienne} (0.51) \\
+		& \textbf{noce} (0.68) & \textbf{mariage} (1.31) & \textbf{mestienne} (0.97) & jondrette (0.59) & fossoyeur (0.46) \\
+		& \textbf{mestienne} (0.58) & \textbf{marié} (1.21) & \textbf{mariage} (0.71) & \textbf{ursule} (0.56) & \textbf{accusé} (0.45) \\
+		& \textbf{mariage} (0.48) & marier (1.11) & \textbf{marié} (0.68) & vernon (0.53) & maire (0.39) \\
+		& \textbf{marié} (0.48) & baron (1.0) & corbillard (0.65) & tante (0.52) & jean (0.37) \\ 
+		\cline{2-6}
+		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		\cline{2-6}
+		& \textbf{noce} (1.2) & \textbf{accusé} (1.47) & \textbf{accusé} (1.85) & conventionnel (5.03) & chandelier (6.28) \\
+		& \textbf{mariage} (0.85) & arras (1.04) & \textbf{avocat} (1.12) & évêque (3.54) & gendarme (5.06) \\
+		& \textbf{ursule} (0.85) & mouchard (0.97) & \textbf{preuve} (1.1) & oratoire (3.39) & panier (4.72) \\
+		& \textbf{marié} (0.8) & \textbf{avocat} (0.96) & président (1.08) & hôpital (2.57) & couvert (4.64) \\
+		& tableau (0.74) & \textbf{preuve} (0.93) & forçat (1.01) & cathédrale (2.54) & deuil (4.52) \\
+		\hline
+	\end{tabular}
 	\label{CA_TIME_REG_word_vs_obj}

### 2022-10-10 2.1_CA_lesMiserables_withNetwork.py

@@ -1,190 +1,0 @@
-from local_functions import *
-import pickle
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
-# Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 20
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 2
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter (0.1)
-regularization_parameter = 0.01
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Get the main characters
-main_char_idx = np.where((corpus.occurrences >= min_occurrences).to_numpy().sum(axis=0) > 10)
-main_char_names = np.array(corpus.occurrences.columns)[main_char_idx]
[…]

### 2022-10-10 CA_lesMiserables.py

@@ -187,21 +187,12 @@ for to_explore_word in word_names:
 
 # Words vs Objects - centroids
 words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects.csv")
-# Words vs Objects - centroids (limited char)
-form_lim_words_vs_occurrences.to_csv("results/CA_CENT_words_vs_objects_LIMITED.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/CA_REG_words_vs_objects.csv")
-# Words vs Objects - regression (limited char)
-form_lim_words_vs_regressions.to_csv("results/CA_REG_words_vs_objects_LIMITED.csv")
-
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words.csv")
-# Objects vs Words - centroids (limited words)
-form_lim_occurrences_vs_words.to_csv("results/CA_CENT_objects_vs_words_LIMITED.csv", index=False)
 # Objects vs Words - regression
 regressions_vs_words.to_csv("results/CA_REG_objects_vs_words.csv")
-# Objects vs Words - regression (limited words)
-form_lim_regressions_vs_words.to_csv("results/CA_REG_objects_vs_words_LIMITED.csv", index=False)
 
 # -- For article
 

### 2022-10-10 CA_lesMiserables_Timeline.py

@@ -122,8 +122,7 @@ regressions_vs_words = words_vs_regressions.transpose()
 # ---- Limited char and words
 
 # Objects to explore
-object_names = ["T1", "T2", "T3", "T4", "T5", "Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean",
-                "Marius-Valjean", "Javert", "Javert-Valjean", "Myriel", "Myriel-Valjean"]
+object_names = ["T1", "T2", "T3", "T4", "T5", "Cosette", "Cosette-Marius", "Cosette-Valjean", "Marius", "Valjean"]
 if meta_for_occurrences is not None:
     separation_name = list(set(corpus.meta_variables[meta_for_occurrences]))
     for i in range(len(separation_name)):
@@ -192,33 +191,34 @@ for to_explore_word in word_names:
 
 # Words vs Objects - centroids
 words_vs_occurrences.to_csv("results/CA_TIME_CENT_words_vs_objects.csv")
-# Words vs Objects - centroids (limited char)
-form_lim_words_vs_occurrences.to_csv("results/CA_TIME_CENT_words_vs_objects_LIMITED.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/CA_TIME_REG_words_vs_objects.csv")
-# Words vs Objects - regression (limited char)
-form_lim_words_vs_regressions.to_csv("results/CA_TIME_REG_words_vs_objects_LIMITED.csv")
-
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/CA_TIME_CENT_objects_vs_words.csv")
-# Objects vs Words - centroids (limited words)
-form_lim_occurrences_vs_words.to_csv("results/CA_TIME_CENT_objects_vs_words_LIMITED.csv", index=False)
 # Objects vs Words - regression
 regressions_vs_words.to_csv("results/CA_TIME_REG_objects_vs_words.csv")
-# Objects vs Words - regression (limited words)
-form_lim_regressions_vs_words.to_csv("results/CA_TIME_REG_objects_vs_words_LIMITED.csv", index=False)
 
 # -- For article
 
 # extra_limited
 part_1 = ["T1", "T2", "T3", "T4", "T5"]
-part_2 = ["Cosette-Valjean_1", "Cosette-Valjean_2", "Cosette-Valjean_4", "Cosette-Valjean_5"]
[…]

### 2022-10-10 WV_lesMiserables.py

@@ -232,21 +232,12 @@ for to_explore_word in word_names:
 
 # Words vs Objects - centroids
 words_vs_occurrences.to_csv("results/WV_CENT_words_vs_objects.csv")
-# Words vs Objects - centroids (limited char)
-form_lim_words_vs_occurrences.to_csv("results/WV_CENT_words_vs_objects_LIMITED.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/WV_REG_words_vs_objects.csv")
-# Words vs Objects - regression (limited char)
-form_lim_words_vs_regressions.to_csv("results/WV_REG_words_vs_objects_LIMITED.csv")
-
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/WV_CENT_objects_vs_words.csv")
-# Objects vs Words - centroids (limited words)
-form_lim_occurrences_vs_words.to_csv("results/WV_CENT_objects_vs_words_LIMITED.csv", index=False)
 # Objects vs Words - regression
 regressions_vs_words.to_csv("results/WV_REG_objects_vs_words.csv")
-# Objects vs Words - regression (limited words)
-form_lim_regressions_vs_words.to_csv("results/WV_REG_objects_vs_words_LIMITED.csv", index=False)
 
 # -- For article
 

### 2022-10-10 WV_lesMiserables_Timeline.py

@@ -1,0 +1,269 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = "tome"
+# Regularization parameter
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
[…]

### 2022-10-11 article/paper1.tex
write paper

@@
 In this article, the data representation for a textual narrative, divided in $n$ textual units $u_1, \ldots, u_n$, is made through two tables.
-The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ contingency table $\mathbf{N}$, as represented by Table \ref{cont_table}, where $v$ is the vocabulary size.
+The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ contingency table $\mathbf{N}$, as represented by Table 1, where $v$ is the vocabulary size.
 In this table, each row represents an unit, each column a word, and cells $n_{ij}$ counts the number of times the word $i$ appears in the unit.
@@
 
-The second table, denoted by $\mathbf{O}$, has a size of $(n \times p)$ where $p$ is the number of \emph{character-based objects} found in the narrative and cells $o_{ij}$ counts occurrences of object $j$ in unit $i$.
-A character-based object can be loosely defined in order to be flexible for various types of narrative or analyses, but can roughly be seen as a countable recurring narrative entity, containing one or more characters.
-For example, it can be a character occurrence, a character co-occurrence, an oriented character interaction (e.g.
+The second table, denoted by $\mathbf{O}$, has a size of $(n \times p)$ where $p$ is the number of \emph{entities} found in the narrative and cells $o_{ij}$ indicates the presence, or the count for a weighted version, of entity $j$ in unit $i$.
+An entity, in the context of this article, can be loosely defined in order to be flexible for various types of narrative or analyses, but can roughly be seen as a recurring narrative object, which can contain one or more characters.
+For example, it can be a character, pair of characters (or even triplet, quadruplet, etc.), an oriented character interaction (e.g.
 a dialog), or even a particular recurring event containing multiple characters (e.g.
 a meeting).
-In this article, we mostly consider character occurrences and pair of characters co-occurrences, as shown in Table \ref{occ_table}.
+In this article, we mostly consider character and pair of characters as entities, as shown in Table 2.
+Note that we consider that a character or a pair of characters are present in the unit if character names (or aliases) are detected above a fixed threshold.
+A weighted version of this table, where $o_{ij}$ contain the number of occurrences of the entity $j$ in the unit $i$, is also possible and the theory will be written accordingly.
 
@@
 		\hline 
-		$u_{101}$ & 66 & 78 & 0 & ... \\
+		$u_{101}$ & 1 & 1 & 0 & ... \\
 		\hline
-		$u_{102}$ & 21 & 26 & 0 & ... \\
+		$u_{102}$ & 1 & 1 & 0 & ... \\
 		\hline
-		$u_{103}$ & 12 & 25 & 0 & ... \\
+		$u_{103}$ & 1 & 1 & 0 & ... \\
 		\hline
-		$u_{104}$ & 12 & 0 & 5 & ... \\
+		$u_{104}$ & 1 & 0 & 1 & ... \\
 		\hline
@@
 		\hline 
-		$u_{101}$  	& ... & 66 & 0 &  ... \\
+		$u_{101}$  	& ... & 1 & 0 &  ... \\
 		\hline
-		$u_{102}$ 	& ... & 21 & 0 & ... \\
+		$u_{102}$ 	& ... & 1 & 0 & ... \\
 		\hline
-		$u_{103}$  	& ... & 12 & 0 & ... \\
+		$u_{103}$  	& ... & 1 & 0 & ... \\
 		\hline
-		$u_{104}$ 	& ... & 0 & 5 & ... \\
+		$u_{104}$ 	& ... & 0 & 1 & ... \\
 		\hline
@@
 	\label{occ_table}
-	\caption{A snippet of the character-based objects table $\mathbf{O}$ extracted from \emph{les Misérables}.
-Rows are chapters, columns are character occurrences (top) and character co-occurrences (bottom), and cell $o_{ij}$ counts the number of times object $j$ appear in chapter $i$.
-Character co-occurrences are computed here as $o_{ij} = \min(o_{ik}, o_{il})$, where $\{k, l\}$ are characters constituting $j$.}
+	\caption{A snippet of the entities table $\mathbf{O}$ extracted from \emph{les Misérables}.
+Rows are chapters, columns are characters (top) and character-pairs (bottom), and cell $o_{ij}$ denotes if $j$ appear in chapter $i$.}
 \end{table}
@@
 Textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns of both tables.
-Moreover, subsequent analyses are oriented in searching how the object table $\mathbf{O}$ has an influence over the contingency table $\mathbf{N}$, i.e.
-searching which words are over-represented or under-represented knowing the character-based objects in the unit.
+Moreover, subsequent analyses are oriented in searching how the entity table $\mathbf{O}$ has an influence over the contingency table $\mathbf{N}$, i.e.
+searching which words are over-represented or under-represented knowing entities in the unit.
 While authors use characters in order to build the narrative, we, to a certain extent, work backward: we are searching how character appearances and interactions in the textual unit act on her/his choice of words.
-If the extraction method permits it, a practitioner should include all character-based objects which she/he desire to study.
-Here, for example, the choice to include character co-occurrences along with occurrences is motivated by the fact that we are interested in studying character relationships.
-A character co-occurrence can roughly be seen as an interaction between two characters, and an interaction between two characters (or more, but higher order interactions are outside the scope of this article) should be considered as an object of its own: this interaction is not necessarily the sum of its parts and can give a particular flavor to the unit.
+If the extraction method permits it, a practitioner should include all entities which she/he desire to study.
+Here, for example, the choice to include character-pairs along with characters is motivated by the fact that we are interested in studying character relationships.
+A character-pair can roughly be seen as an interaction between two characters, and this interaction should be considered as an object of its own: the presence of this interaction in a unit do not result in having a mixture of words used for each character, and rather give a particular flavor to the unit.
 
 This data organization also highlight the importance of choosing a proper size for the units.
-These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally captures particularities about one of the character-based objects.
-Unfortunately, it is impossible to define an ideal size for all types of analysis and this size should be balanced regarding the level of analysis, the text size, the selected character-based objects, and previous knowledge of the studied work.
+These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally captures particularities about one of the entity.
+Unfortunately, it is impossible to define an ideal size for all types of analysis and this size should be balanced regarding the level of analysis, the text size, the selected entities, and previous knowledge of the studied work.
 
@@
 \\
-In section (REF), these vectors of textual units are used as anchor points in order to also embed character-based objects into the same space.
-Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible in order to properly extract information about the localization of character-based objects vectors (the relative position of these vectors is insufficient).
-For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of character-based objects relatively to word vectors, these objects can be characterized.
+In section \ref{entity_embeddings}, these vectors of textual units are used as anchor points in order to also embed entities into the same space.
+Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible in order to properly extract information about the localization of entity vectors (the relative position of these entity vectors among themselves is insufficient).
+For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, these entities can be characterized.
 
@@
 
-The relationship between a particular unit $i$ and a word $j$ is expressed through the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$.
+The association between a particular unit $i$ and a word $j$ is expressed through the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$, which act as a similarity measure.
 A positive (resp.
@@
 under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
-Observe that in this article, this similarity is rather computed between word and character-based object vectors, as defined in section (REF), as they lie in the same space as unit vectors.
+Observe that in this article, this similarity is rather computed between word and entity vectors, as defined in section \ref{entity_embeddings}, as they lie in the same space as unit vectors.
 
-Using CA to embedded units however comes with some limitations.
+Using CA to embedded units however comes with limitations.
 First, note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
 This analysis is thus \emph{contrastive}: it highlights unit variations among the studied text.
-This could becomes problematic in order to study a dataset containing multiple texts: units belonging to the same text will have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between text.
-Another limitation with this approach is that the words helping the interpretation of units (and character-based objects) are contained in the studied text.
-Approaches requiring to study the position of units and objects relatively to a predefined list of words (e.g., friends, enemies, family) might therefore be impossible.
+This could becomes problematic in order to study a dataset containing multiple corpora: units belonging to the same text will have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between the different works.
+Another limitation with this approach is that the words helping the interpretation of units (and entities) are contained in the studied text.
+Approaches requiring to study the position of units and entities relatively to a predefined list of words (e.g., friends, enemies, family) might therefore be impossible if these words do not appear in the text.
 
@@
 
-Pre-trained word vectors, based on Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
+Pre-trained word vectors, based on methods such as Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
 They are generally obtained through a training on a very large corpora, such as Wikipedia (REF) or Common Crawl (REF), and the resulting embedding contains a large quantity of word vectors.
@@
 a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to align vectors.
-In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit size and gives state-of-the-art results in multiple tasks.
+In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit sizes and gives state-of-the-art results in various tasks.
 
-More precisely, we use a pre-trained word vectors $\mathbf{w}_1, \ldots, \mathbf{w}_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is 2 millions and the dimension of vectors are $300$.
 Textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.
@@
 
-With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and character-based objects vectors in section REF) lie in an \emph{absolute space} defined by the used word vectors.
+With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and entity vectors in section \ref{entity_embeddings}) lie in an \emph{absolute space} defined by the used word vectors.
 Comparison between different texts are therefore more pertinent in this space and comparison with words absent from the corpus can be made.
@@
 
-\subsection{Character-based object embeddings}
+\subsection{Entity embeddings}
+\label{entity_embeddings}
 
-The main goal of this article is not to analyze units, but rather the character-based objects, i.e.
+The main goal of this article is not to analyze units, but rather the entities, i.e.
 the $p$ columns of table $\mathbf{O}$.
-While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{O}$ in order to build the character-based vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ which lie in the same space as units.
+While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{O}$ in order to build the entity vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ which lie in the same space as units.
 
 Two propositions of method are made: the \emph{centroids} method (CENT) is describe in section \ref{centroid} and the \emph{regressions} method (REG) is explained in section \ref{regression}.
-Both methods work with the proposed embeddings of units.
+Both methods work with the aforementioned embeddings of units.
 
@@
 
-This method is the most trivial and is based on the following intuition: a character-based object is characterized by all units in which it appears.
+This method is the most trivial and is based on the following intuition: an entity is characterized by all units in which it appears.
 In other words, we can define the vector $\mathbf{y}_k$ for character-object object $k$ as
@@
 i.e.
-the center of mass, or \emph{centroid}, of the units containing the character-based object, weighted by the relative weight of its occurrences $\frac{o_{ik}}{o_{\bullet k}}$.
-This way of building character-based vectors is closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
-However, by contrast, character-based vectors are not dilated after computing centroids, which means that they lie in the same space as units (row).
+the center of mass, or \emph{centroid}, of the units containing the entity, weighted by the relative weight $\frac{o_{ik}}{o_{\bullet k}}$.
+This way of building entity vectors is closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
+However, by contrast, entity vectors are not dilated after computing centroids, which means that they lie in the same space as units (row).
 \\
-An important remark about the centroid method, is that character-objects vectors positions are \emph{additive}, which means that we have
+An important remark about the centroid method, is that entity vectors positions are \emph{additive}, which means that we have
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{G}$ is a subset of character-based objects.
-This property can be interpreted as followed: if the occurrences of a character $k$ can be divided among different situations $g$ (the character alone, the character in interaction with another character, etc.), the character vector $\mathbf{y}_k$ is in fact the centroid of all vectors $\mathbf{y}_g$ of these situations.
-This is not necessary an undesirable property, but this implies that the specificities of the character might be hidden if he is often registered in an interaction.
-For example, if the character is frequently with a friend, the character vector will be close to the vector of the couple (if both the character and the couple are counted in the table $\mathbf{O}$).
-By contrast, if we consider that an interaction between two characters is an \emph{emerging situation}, unrelated to prior behaviors of characters, the regressions method described in the next section seems more appropriate to capture every specificities.
+where $\mathcal{G}$ is a subset of entities.
+This property can be interpreted as followed: if a character $k$ can be divided among different situations $g$ (the character alone, the character in interaction with another character, etc.), the character vector $\mathbf{y}_k$ is in fact the centroid of all vectors $\mathbf{y}_g$ of these situations.
+This is not necessary an undesirable property, but it implies that the specificities of the lone character might be hidden if he is often registered in an interaction.
+By contrast, if we consider that an interaction between two characters is an \emph{emerging situation}, unrelated to prior behaviors of characters, the regressions method described in the next section seems more appropriate.
 
@@
 By doing so, we suppose that the effect of raising both variables is not the same as raising each variable independently.
-Regression models seem therefore appropriate to capture specificities of having a particular character-based object in a textual unit: the presence of a character $a$ has a effect on the vocabulary of an unit, the presence of another character $b$ has an other effect, and the presence of the pair $\{a, b\}$ yet a different effect.
+Regression models seem therefore appropriate to capture specificities of having a particular entity in a textual unit: the presence of a character $a$ has a effect on the vocabulary of an unit, the presence of another character $b$ has an other effect, and the presence of the pair $\{a, b\}$ yet a different effect.
 Now, the dependent variable still need to be defined.
-In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the chosen unit embeddings, and each regressions is constructed to predict the $\alpha$-th coordinate of each units by using variables in the $\mathbf{O}$.
+In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the chosen unit embeddings, and each regressions is constructed to predict the $\alpha$-th coordinate of each units by using variables in the table $\mathbf{O}$.
 In a matrix notation, all models can be written as
@@
 \end{align}
-where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{O}}$ the $(n \times (p+1))$ matrix representing $\mathbf{O}$ with an additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{E}$ the $(n \times \alpha)$ error matrix.
+where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{O}}$ is the matrix $\mathbf{O}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{E}$ the $(n \times \alpha)$ matrix containing normal errors.
 
-Estimates $\widehat{\mathbf{B}} = (\widehat{\beta}_{k\alpha})$ for the intercept and coefficient regressions are in fact the researched embeddings for character-based objects as well as for the intercept representing the general tone of the studied text.
+Estimates $\widehat{\mathbf{B}} = (\widehat{\beta}_{k\alpha})$ for the intercept and coefficient regressions are in fact the researched embeddings for entities as well as for the intercept representing the general tone of the studied text.
 We therefore denote these estimates with $\mathbf{Y} = (y_{k\alpha})$ in the following, with the convention $y_{0\alpha}$ for intercept coefficients.
 
-As the number of character-objects might be very large, it is a good idea to add a $L^2$ regularization term in the objective function.
+As the number of entities (i.e.
+predictors) might be very large, it is a good idea to add a $L^2$ regularization term in the objective function.
 Moreover, the quadratic error rate should also be weighted by the number of tokens in each unit.
@@
 An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) (with a contraction and a different weighting scheme).
-In fact, the regressions method with a regularized term interpolate between the hypothesis where we suppose that every character-object should be considered independently (with $\lambda \to 0$), to the hypothesis of additive mixture between character-objects (with $\lambda \to \infty$), as discussed in section \ref{centroid}.
-Choosing an appropriate $\lambda$ according to the study (how is another, difficult question) might lead to a situation revealing pertinent information about all character-objects.
+In fact, the regressions method with a regularized term interpolate between the hypothesis where we suppose that every entity should be considered independently (with $\lambda \to 0$), to the hypothesis of additive mixture between entities (with $\lambda \to \infty$), as discussed in section \ref{centroid}.
+Choosing an appropriate $\lambda$ according to the study (how is another, difficult question) might lead to a situation revealing desirable information about entities.
 
@@
 For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present here only one case studies: \emph{Les Misérables} by Victor Hugo.
-The choice of this work is motivated by the fact that it is a large corpus, immensely studied, and containing various colorful characters and characters relationships.
+The choice of this work is motivated by the fact that it is a large corpus, well-known, immensely studied, and containing various colorful characters and characters relationships.
 It is therefore a solid choice to clearly illustrate the potential of presented methods.
@@
 
-Characters presences were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}} (REF) NER tools.
+Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}} (REF) NER tools.
 In order to unify character and to further refine the detected characters list, we used hand-made lists of character and aliases from NER results.
 It resulted in the detection of 54 characters.
-The character-based objects considered in table $\mathbf{O}$ (Figure \ref{occ_table}) are single character occurrences (54 objects) and character pair co-occurrences (547 objects), resulting in a table of size $365 \times 601$.
-The character co-occurrences count is computed as $o_{ij} = \min(o_{ik}, o_{il})$, where $\{k, l\}$ are characters constituting the pair $j$.
+The entities considered in table $\mathbf{O}$ (Figure \ref{occ_table}) are single character (54 entities) and character pairs (547 entities), resulting in a table of size $365 \times 601$.
+A character or a character-pairs presence is considered present iff characters are detected at least 2 times in the chapter.
 
-Note that, in section \ref{diachronic}, we also tested experiments with objects consisting in character and character-pairs as found in each volumes (e.g.
-Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects) with the addition of volume constants ($V_i=1$ in volume $i$, $V_i=0$ in the other volumes) in order to isolate specific volume vocabulary.
-This new table $\mathbf{O}_\text{vol}$, containing $1124$ character-based objects, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
+Note that, in section \ref{diachronic}, we also tested experiments with entities consisting in character and character-pairs as found in each volumes (e.g.
+Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate specific volume vocabulary.
+This new table $\mathbf{O}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
 
@@
 
-There are two types of methods for unit embeddings, \textbf{CA} (section \ref{ca_method}) and \textbf{WV} (section \ref{wv_method}), as well as two methods for character-based embedding, \textbf{CENT} (section \ref{centroid}) and \textbf{REG} (section \ref{regression}), making a total of 4 possibles ways for obtaining final embeddings.
-The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on French \emph{fastText}\footnote{\url{https://fasttext.cc/docs/en/crawl-vectors.html}} (REF) pre-trained embeddings, giving a $300$-dimensional space.
-The \textbf{CENT} do not have any hyperparameter and we fixed the hyperparameter of the \textbf{REG} methods to $\lambda = 0.01$ for all experiments.
-\\
-Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{O}$ and $\mathbf{O}_\text{vol}$, and a considerable number of characters and character relationships, results can also be presented in various ways (similarities between character-based objects, between words, between objects and words, etc.).
-Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding character-based objects (section \ref{words}), the 5 most related character-based object regarding a subset of words (section \ref{objects})), and a diachronic study of top associated words for a subset of character-based objects (section \ref{diachronic}).
-We invite curious readers to consult these results for all words and objects, which can be found in our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
+There are two types of methods for unit embeddings, \textbf{CA} (section \ref{ca_method}) and \textbf{WV} (section \ref{wv_method}), as well as two methods for entity embeddings, \textbf{CENT} (section \ref{centroid}) and \textbf{REG} (section \ref{regression}), making a total of 4 possibles ways for obtaining final embeddings.
+
+The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} (REF) trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is 2 millions and the dimension of vectors are $300$.
+
+Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{O}$ and $\mathbf{O}_\text{vol}$, and a considerable number of entities, results can also be presented in various ways (similarities between entities, between entities and words, etc.).
+Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of top associated words for a subset of entities (section \ref{diachronic}).
+We invite curious readers to consult results for all words and entities, which can be found in our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
 
@@
 
-\subsubsection{The most associated words for a subset of characters-based objects}
+\subsubsection{The most associated words for a subset of entities}
 \label{words}
@@
 	\label{word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to a selected set of characters and character pairs, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.
+	\caption{The 5 most associated words (similarity in parentheses) to a selected set of entities, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.
 Words appearing at least two times within the same method are in bold.}
@@
 
-The first results in this section is to examine the most associated words with a subset of character-based objects, as measured by the similarities defined in section \ref{unit_embeddings}.
+The first results in this section is to examine the most associated words with a subset of entities, as measured by the similarities defined in section \ref{unit_embeddings}.
 Results can be found in Table 3 for all methods.
 
-We can first observe that \textbf{CA} methods seems to summarize objects with a vocabulary closer to the work, while \textbf{WV} methods tend to use more general concepts, with notably more verbs.
-This behavior can be traced back to the nature of embeddings: in the \textbf{WV} embedding, word-vectors are fixed and do not consider the actual frequencies of words found in the studied corpora.
-A character could be highly similar to a word appearing only a few times in the corpus if this word is located near the vocabulary associated with this character.
-By contrast, \textbf{CA} will generally takes into account word frequencies, and balance them with specificities, in order to describe a character.
+We can first observe that \textbf{CA} methods seems to summarize entities with a vocabulary closer to the work, while \textbf{WV} methods tend to frequently use words with a wider scope, with notably more verbs.
+It results in having the \textbf{WV} giving a general feeling for the tone used for describing characters and relationships, while the \textbf{CA} method can depict very specific objects, location or event associated with these entities.
+This behavior can understood by the nature of unit embeddings: in the \textbf{WV} embedding, word-vectors are fixed and do not consider the actual frequencies of words found in the studied corpora.
+A character can be close to a word appearing only a few times (or none) in the corpus if this word is located near the vocabulary associated with this character, as semantically similar words are located in the same region of space.
+By contrast, \textbf{CA} will generally takes into account word frequencies along with specificities in order to describe an entity, and very specific words can define particular regions of space.
 
@@
 Cosette, Cosette-Marius, and Cosette-Valjean).
-By constrast, the \textbf{REG} methods display more "perpendicular" descriptions of objects, with less words repeating.
+By constrast, the \textbf{REG} methods display more "perpendicular" descriptions of entities, with less words repeating.
 
-Note that we did not show here the least associated words with each object, as they are frequently the same for all methods and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
+Note that we did not show here the least associated words with each entities, as they are frequently the same for all methods and all related to the long description of the Battle of Waterloo in volume 2 ("infanterie", "wellington", "cuirassier", "bridage"), containing no protagonist of the story.
 
-Overall, we find that the \textbf{CA-REG} method gives the most satisfying results, with pertinent words associated with each character-based object, and an high variety in the choice of words.
+Overall, we find that the \textbf{CA-REG} method gives the most satisfying results, with pertinent words associated with each entity, and an high variety in the choice of words.
 
@@
 	\label{CA_CENT_obj_words}
-	\caption{The 5 most associated character-based objects (similarity in parentheses) to a selected set of words, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.}
+	\caption{The 5 most associated entities (similarity in parentheses) to a selected set of words, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.}
 \end{table*}
@@
 
-These results are extracted from the transposed table from the last, and display the most associated character-based objects to a selected set of words.
+These results are extracted from the transposed table from the last, and display the most associated entities to a selected set of words.
 They can be found in Table 4.
-This type of results can be seen as "queries", made from a single word, which output the highest objects in the work related to that query.
-We chose here to show the most associated objects to words "aimer", "rue", "justice" and "guerre", as they represent some of the major topics of the book.
-In this task, the \textbf{CA-REG} again seems to display the most satifying results: the main love relationship (Cosette-Marius) of the book is the most associated object for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top object for "justice", and officers or aggressive characters appear massively associated with "guerre".
-While somewhat inferior with the select set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
+This type of results can be seen as queries, made from a single word, which output the most associated entities in the work related to that query.
+We chose here to show top entities related to words "aimer", "rue", "justice" and "guerre", as they represent some of the main topics of the book.
+In this task again, from our point of view, the \textbf{CA-REG} displays the most accurate results: the main love relationship (Cosette-Marius) of the book is the most associated entity for "aimer", several "amis de l'ABC" (a revolutionary group) are most associated with "rue", the cop-suspect relationship (Javert-Valjean) is the top entity for "justice", and military officers or bellicose characters are associated with "guerre".
+While somewhat inferior with the selected set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
 It should also give interesting results when comparing different corpora, due to the fixed nature of word-vectors, but case studies concerning multiple corpora are outside the scope of this article.
@@
 This representation gives a quick visual support in order to explore the studied work and could be implemented as a standalone program.
-
-% ----------------------------------------------
-
-\begin{table*}[!bh]
-	\centering
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline
-		T1 & T2 & T3 & T4 & T5 \\ \hline
-		huissier (1.4) & cuirassier (3.38) & gamin (1.92) & émeute (1.48) & sable (3.04) \\ \hline
-		hôte (1.11) & infanterie (2.9) & mine (1.38) & révolte (0.86) & berge (2.32) \\ \hline
-		arras (0.92) & sacrement (2.69) & farce (0.81) & bourgeoisie (0.84) & égout (2.16) \\ \hline
-		lampe (0.91) & brigade (2.41) & ignorance (0.74) & populaire (0.82) & voûte (1.9) \\ \hline
-		montreuil (0.81) & division (2.4) & jondrette (0.7) & insurrection (0.81) & vase (1.89) \\ 
-		\hline
-	\end{tabular}
-
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline
-		Cosette-Valjean\_1 & Cosette-Valjean\_2 & Cosette-Valjean\_3 & Cosette-Valjean\_4 & Cosette-Valjean\_5 \\ \hline
-		maladie (0.49) & façade (0.68) & - & promenade (0.5) & noce (1.27) \\ \hline
-		médecin (0.48) & corbillard (0.66) & - &chaîne (0.47) & marié (0.93) \\ \hline
-		demain (0.33) & mestienne (0.6) & - & blessure (0.46) & mardi (0.89) \\ \hline
-		surprise (0.28) & bâtiment (0.56) & - &tuyau (0.45) & mariage (0.86) \\ \hline
-		auprès (0.28) & cul (0.55) & - &luxembourg (0.44) & file (0.65) \\ \hline
-	\end{tabular}
-
-	\label{CA_TIME_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) vs volumes objects (top) and Cosette-Valjean relationship as found in each tome, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
-Note that no co-occurrence between Cosette and Valjean were automatically found in volume 3.}
-\end{table*}
 
@@
 		\hline
-		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\textbf{CA-CENT}}}} & Cosette & Cosette-Marius & Cosette-Valjean & Marius & Valjean \\ 
+		\parbox[t]{2mm}{\multirow{24}{*}{\rotatebox[origin=c]{90}{\textbf{CA-REG}}}} 
+		& $V_1$ & $V_2$ & $V_3$ & $V_4$ & $V_5$ \\ 
 		\cline{2-6}
-		& poupée (0.7) & \textbf{noce} (1.72) & \textbf{noce} (1.0) & théodule (0.61) & \textbf{mestienne} (0.51) \\
-		& \textbf{noce} (0.68) & \textbf{mariage} (1.31) & \textbf{mestienne} (0.97) & jondrette (0.59) & fossoyeur (0.46) \\
-		& \textbf{mestienne} (0.58) & \textbf{marié} (1.21) & \textbf{mariage} (0.71) & \textbf{ursule} (0.56) & \textbf{accusé} (0.45) \\
-		& \textbf{mariage} (0.48) & marier (1.11) & \textbf{marié} (0.68) & vernon (0.53) & maire (0.39) \\
-		& \textbf{marié} (0.48) & baron (1.0) & corbillard (0.65) & tante (0.52) & jean (0.37) \\ 
+		& huissier (1.4) & cuirassier (3.38) & gamin (1.92) & émeute (1.48) & sable (3.04) \\
+		& hôte (1.11) & infanterie (2.9) & mine (1.38) & révolte (0.86) & berge (2.32) \\
+		& arras (0.92) & sacrement (2.69) & farce (0.81) & bourgeoisie (0.84) & égout (2.16) \\
+		& lampe (0.91) & brigade (2.41) & ignorance (0.74) & populaire (0.82) & voûte (1.9) \\
+		& montreuil (0.81) & division (2.4) & jondrette (0.7) & insurrection (0.81) & vase (1.89) \\ 
 		\cline{2-6}
-		& Marius-Valjean & Javert & Javert-Valjean & Myriel & Myriel-Valjean \\
+		& Valjean 1 & Valjean 2 & Valjean 3 & Valjean 4 & Valjean 5 \\ 
 		\cline{2-6}
-		& \textbf{noce} (1.2) & \textbf{accusé} (1.47) & \textbf{accusé} (1.85) & conventionnel (5.03) & chandelier (6.28) \\
-		& \textbf{mariage} (0.85) & arras (1.04) & \textbf{avocat} (1.12) & évêque (3.54) & gendarme (5.06) \\
-		& \textbf{ursule} (0.85) & mouchard (0.97) & \textbf{preuve} (1.1) & oratoire (3.39) & panier (4.72) \\
-		& \textbf{marié} (0.8) & \textbf{avocat} (0.96) & président (1.08) & hôpital (2.57) & couvert (4.64) \\
-		& tableau (0.74) & \textbf{preuve} (0.93) & forçat (1.01) & cathédrale (2.54) & deuil (4.52) \\
+		& chandelier (1.03) & pelle (2.6) & ursule (1.49) & réverbère (0.98) & matelas (2.54) \\ 
+		& toulon (0.8) & fossoyeur (2.35) & luxembourg (1.06) & hausser (0.45) & ronde (1.96) \\
+		& gervai (0.73) & pioche (1.51) & tableau (0.93) & promenade (0.37) & galerie (1.06) \\ 
+		& bagne (0.65) & carte (1.39) & banc (0.81) & lanterne (0.36) & lanterne (0.99) \\ 
+		& maire (0.57) & mestienne (1.35) & mouchoir (0.77) & tuyau (0.35) & rive (0.99) \\ 
+		\cline{2-6}
+		& Cosette 1 & Cosette 2 & Cosette 3 & Cosette 4 & Cosette 5 \\ 
+		\cline{2-6}
+		& gargote (0.59) & seau (1.48) & - & ravissant (1.11) & encre (0.76) \\ 
+		& balayer (0.57) & poupée (0.99) & - & céleste (0.76) & plume (0.59) \\
+		& alouette (0.56) & source (0.84) & - & volupté (0.67) & noce (0.49) \\
+		& servante (0.43) & gargote (0.71) & - & frémir (0.64) & chandelier (0.48) \\
+		& mois (0.34) & mestienne (0.64) & - & lancier (0.6) & antichambre (0.47) \\
+		\cline{2-6}
+		& Cosette-Valjean 1 & Cosette-Valjean 2 & Cosette-Valjean 3 & Cosette-Valjean 4 & Cosette-Valjean 5 \\
+		\cline{2-6}
+		& maladie (0.49) & façade (0.68) & - & promenade (0.5) & noce (1.27) \\ 
+		& médecin (0.48) & corbillard (0.66) & - & chaîne (0.47) & marié (0.93) \\
+		& demain (0.33) & mestienne (0.6) & - & blessure (0.46) & mardi (0.89) \\
+		& surprise (0.28) & bâtiment (0.56) & - & tuyau (0.45) & mariage (0.86) \\
+		& auprès (0.28) & cul (0.55) &- & luxembourg (0.44) & file (0.65) \\ 
+		\hline
+		\hline
+		\parbox[t]{2mm}{\multirow{24}{*}{\rotatebox[origin=c]{90}{\textbf{WV-REG}}}} 
+		& $V_1$ & $V_2$ & $V_3$ & $V_4$ & $V_5$ \\ 
+		\cline{2-6}
+		& demander (0.36) & saint (0.39) & gamin (0.45) & violence (0.44) & égout (0.52) \\ 
+		& décider (0.3) & mont (0.39) & garçon (0.42) & haine (0.42) & quai (0.45) \\ 
+		& aider (0.3) & régiment (0.38) & jeune (0.36) & révolte (0.42) & rue (0.44) \\ 
+		& expliquer (0.29) & chapelle (0.38) & enfant (0.35) & souffrance (0.4) & eau (0.42) \\
+		& plaindre (0.29) & infanterie (0.36) & père (0.34) & étincelle (0.39) & chaussée (0.42) \\
+		\cline{2-6}
+		& Valjean 1 & Valjean 2 & Valjean 3 & Valjean 4 & Valjean 5 \\ 
+		\cline{2-6}
+		& essayer (0.29) & jean (0.54) & admirer (0.32) & jean (0.71) & jean (0.72) \\ 
+		& réfléchir (0.27) & jacques (0.33) & passer (0.31) & jacques (0.41) & pantalon (0.42) \\ 
+		& expliquer (0.24) & pantalon (0.29) & observer (0.3) & pantalon (0.36) & jacques (0.39) \\ 
+		& agir (0.24) & mr (0.28) & guetter (0.3) & louis (0.34) & philippe (0.34) \\ 
+		& questionner (0.24) & denis (0.28) & croiser (0.3) & philippe (0.33) & denis (0.33) \\ 
+		\cline{2-6}
+		& Cosette 1 & Cosette 2 & Cosette 3 & Cosette 4 & Cosette 5 \\ 
+		\cline{2-6}
+		& an (0.41) & dormir (0.33) & - & rêver (0.32) & rêver (0.31) \\
+		& mois (0.39) & regarder (0.29) & - & regarder (0.31) & mentir (0.29) \\
+		& mère (0.36) & sentir (0.28) & - & contempler (0.28) & écrire (0.29) \\
+		& fille (0.35) & endormir (0.28) & - & pleurer (0.27) & demander (0.28) \\
+		& enfant (0.33) & respirer (0.28) & - & lire (0.27) & pleurer (0.28) \\
+		\cline{2-6}
+		& Cosette-Valjean 1 & Cosette-Valjean 2 & Cosette-Valjean 3 & Cosette-Valjean 4 & Cosette-Valjean 5 \\
+		\cline{2-6}
+		& voir (0.32) & rue (0.55) & - & jean (0.52) & mariage (0.42) \\ 
+		& entendre (0.31) & ruelle (0.48) & - & pantalon (0.35) & marié (0.4) \\ 
+		& frissonner (0.3) & boulevard (0.45) & - & gilet (0.28) & noce (0.4) \\ 
+		& grommeler (0.3) & mur (0.4) & - & gris (0.27) & gai (0.33) \\ 
+		& essayer (0.3) & faubourg (0.4) & - & manteau (0.26) & amour (0.3) \\ 
 		\hline
 	\end{tabular}
-	\label{CA_TIME_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) vs volumes objects (top) and Cosette-Valjean relationship as found in each tome, regarding the \textbf{CA-REG} method ($\lambda = 0.01$).
-Note that no co-occurrence between Cosette and Valjean were automatically found in volume 3.}
+	\label{TIME_REG_word_vs_obj}
+	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean entity, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).
+Note that Cosette was not found in volume 3 because she is not explicitly cited (she is often refereed as "the daugther of M.
+Leblanc").}
 \end{table*}
+
+These results are obtained from the table $\mathbf{O}_\text{vol}$ where entities are considered different based on the volume.
+By doing so, it permits to track, e.g., the evolution of associated words for entities along the book.
+Moreover, we also define a constant term $V_i$ for each volumes $i$, which absorbs the associated words for each volume.
+Results for constants and a subset of entities can be found in Table 5.
+Note that we did not show \textbf{CONT} results in this table, as they are similar to the one found in Table 3 : words are often repeated themselves among object.
+
+Here again, we see that associated words for the \textbf{WV} method are less specific and again give the general tone of the tome or entity.
 

### 2022-10-11 article/paper1.tex
write paper

@@
 %% The "title" command^
-\title{Refining character relationships using embeddings of textual units : a case study on Les Misérables}
+\title{Characterizing narrative entities with embeddings : a case study of character relationships in Les Misérables}
 
@@
 
-Distant reading tools allow researchers, from various fields, to quickly gain knowledge on textual corpora without actually reading them.
-Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summary large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus.
-Methods in this case rely heavily on Big Data and make an extensive use of Machine Learning algorithms.
-In the second case, researchers use these methods to underline hidden structures in a particular text, helping them to refine their understanding of it and reinforce stated hypotheses.
-Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpus are smaller, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results.
+In the field of \emph{Digital Humanities}, \emph{Distant Reading} tools (REF) allow researchers to quickly gain knowledge on textual corpora without actually reading them.
+Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summary large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus (REF).
+Methods in this case rely heavily on Big Data and make an extensive use of Machine Learning, often with the help of supervised methods.
+In the second case, researchers use computational methods to underline hidden structures in a small corpus or even a lone text, which helps them to refine their understanding of this corpora and reinforce stated hypotheses (REF).
+Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpora are small, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results.
+The use of exploratory tools and unsupervised methods is also preferred in this context, as it is less desirable to base methods on information coming from large external corpora.
+The proposed method typically belong to this second group of methods, as it is unsupervised and work on a single document.
 
-Automatic extraction and analysis of \emph{character networks} from literacy works typically belong in the latter group.
-These methods aim at representing various interactions occurring between fictional characters found in a textual narrative with a graph, thus showing explicitly the hidden structure of character relationships constructed by the author.
-This structure might allow to find hidden patterns within a book, which can highlight a particular genre or style.
+When a lone (or a few) textual narrative is analyzed, a particular effort is made into studying \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book.
+Researchers are often interested by characterizing them and see how they are articulated to one another in the story.
+Various computational tools can help them in this tasks, to name a few, Named Entity Recognition tools (REF), Automatic Character Networks Extraction (REF), Sentiment Analysis (REF), Topic Modeling (REF), Textometry (REF), and Word Embeddings (REF).
+All these methods have been used in order to explicitly show hidden structures constructed by the author in her/his work.
+It permits to find regularities and patterns, and can help to categorize particular narrative constructions, writing styles, or genres.
+These kind of methods can be great complement to classical analyses of literacy works as they allow to efficiently summarized information which is otherwise quite diffuse.
+
+In this article, we propose a general framework in order to automatically characterize various narrative entities in a literacy work.
+The entire framework is exposed starting from a very wide perspective, which is how to organize the textual data, and is narrowed down to a very specific use, the study of character relationships in \emph{Les Misérables}, by Victor Hugo.
+Along this presentation, various choices are made to highlight a particular usage of this framework, but theses choices should be viewed as suggestion rather than rules: the real strength of this framework is its flexibility and the direction taken in this article is oriented for a particular task.
+To be more specific, we are interested here in using \emph{embeddings} in order to locate \emph{character relationships} alongside the vocabulary.
+Similarity measures can then be constructed between these words and the relationships, which can help a practitioner to characterize them.
+Four variations of this method are proposed, and are tested on \emph{Les Misérables}.
+
+The idea behind this methodology comes from the field of automatic extraction and analysis of \emph{character networks} from literacy works (REF).
+When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ \emph{textual units} $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting characters co-occurrences in these units (REF).
+Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters.
+However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
+Various improvements where proposed in order to weight or sign (or both) the edges in the character networks, such as using Sentiment Analysis (REF) Topic Modeling (REF), or BLABLA (REF).
+A particular inspiration for the current work is the article by (REF), where authors also analyzed characters in \emph{Les Misérables} by building various signed and weighted networks, with the help of Sentiment Analysis and Topic Modeling.
+The current framework was build by expanding this idea of refining character relationships while keeping exploring directions as wide as possible.
+Embeddings appeared to us to be the proper tool for achieving this.
+As a matter of fact, with embeddings, the textual contents of units are transformed into workable mathematical objects (the vectors), usable for various tasks, while conserving a maximum of information.
+The framework has been further generalized in order to be applicable on various type of narrative entities, but the presented case remains the study of character relationships in \emph{Les Misérables}.
+
+The current article is structured as followed.
+Section \ref{methodology} define the methodology, with section \ref{data} defining the data organization, section  \ref{unit_embeddings} describing how to embed textual units, and section \ref{entity_embeddings} deriving entity vectors lying in the same space as units.
+In section \ref{case_studie}, we present the methods and results for the case study of character relationship embeddings in \emph{Les Misérables}, and section \ref{conclusion} draw conclusions and perspectives about this work.
+All (Python) scripts and datasets used in this article, as well as extended results, can be found in the dedicated GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors}.}
 
 \section{Methodology}
-
-When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ textual units $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting characters co-occurrences in these units.
-Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters.
-However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
-In this paper, we propose a data organization leading to various methods which takes into consideration the text contained in the unit, helping to refine understanding of characters and their relationships.
+\label{methodology}
 
 \subsection{Data organization}
+\label{data}
 
-In this article, the data representation for a textual narrative, divided in $n$ textual units $u_1, \ldots, u_n$, is made through two tables.
-The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ contingency table $\mathbf{N}$, as represented by Table 1, where $v$ is the vocabulary size.
+In this article, the textual narrative is divided in $n$ \emph{textual units} $u_1, \ldots, u_n$, and is represented through two tables.
+The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ \emph{unit-word contingency table} $\mathbf{N}$, as represented by Table 1, where $v$ is the vocabulary size.
 In this table, each row represents an unit, each column a word, and cells $n_{ij}$ counts the number of times the word $i$ appears in the unit.
@@
 
-The second table, denoted by $\mathbf{O}$, has a size of $(n \times p)$ where $p$ is the number of \emph{entities} found in the narrative and cells $o_{ij}$ indicates the presence, or the count for a weighted version, of entity $j$ in unit $i$.
-An entity, in the context of this article, can be loosely defined in order to be flexible for various types of narrative or analyses, but can roughly be seen as a recurring narrative object, which can contain one or more characters.
-For example, it can be a character, pair of characters (or even triplet, quadruplet, etc.), an oriented character interaction (e.g.
+The second table is the \emph{unit-entity table}, noted $\mathbf{E}$.
+It has a size of $(n \times p)$ where $p$ is the number of \emph{narrative entities} found in the text and cells $e_{ij}$ indicates the presence, or the count for a weighted version, of entity $j$ in unit $i$.
+An narrative entity, in the context of this article, can be loosely defined in order to be flexible for various types of works or analyses.
+It can roughly be seen as a recurring narrative object, which can contain one or more characters.
+For example, it can be a location, a character, a pair of characters (or even a triplet, a quadruplet, etc.), an oriented character interaction (e.g.
 a dialog), or even a particular recurring event containing multiple characters (e.g.
@@
 Note that we consider that a character or a pair of characters are present in the unit if character names (or aliases) are detected above a fixed threshold.
-A weighted version of this table, where $o_{ij}$ contain the number of occurrences of the entity $j$ in the unit $i$, is also possible and the theory will be written accordingly.
+A weighted version of this table, where $e_{ij}$ contain the number of occurrences of the entity $j$ in the unit $i$, is also possible and formulas are written accordingly.
 
@@
 	\label{occ_table}
-	\caption{A snippet of the entities table $\mathbf{O}$ extracted from \emph{les Misérables}.
-Rows are chapters, columns are characters (top) and character-pairs (bottom), and cell $o_{ij}$ denotes if $j$ appear in chapter $i$.}
+	\caption{A snippet of the entities table $\mathbf{E}$ extracted from \emph{les Misérables}.
+Rows are chapters, columns are characters (top) and character-pairs (bottom), and cell $e_{ij}$ denotes if $j$ appear in chapter $i$.}
 \end{table}
@@
 Textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns of both tables.
-Moreover, subsequent analyses are oriented in searching how the entity table $\mathbf{O}$ has an influence over the contingency table $\mathbf{N}$, i.e.
+Moreover, subsequent analyses are oriented in searching how the entity table $\mathbf{E}$ has an influence over the contingency table $\mathbf{N}$, i.e.
 searching which words are over-represented or under-represented knowing entities in the unit.
@@
 Here, for example, the choice to include character-pairs along with characters is motivated by the fact that we are interested in studying character relationships.
-A character-pair can roughly be seen as an interaction between two characters, and this interaction should be considered as an object of its own: the presence of this interaction in a unit do not result in having a mixture of words used for each character, and rather give a particular flavor to the unit.
+A character-pair can roughly be seen as an interaction between two characters, and this interaction should be considered as an object of its own: the presence of this interaction in a unit do not result in having a mixture of words used for each character, but rather gives a specific flavor to the unit.
 
-This data organization also highlight the importance of choosing a proper size for the units.
+This data organization also highlights the importance of choosing a proper size for the units.
 These units should be large enough to contain enough words in order the properly capture the textual specificity of each unit, but not too large, as each unit should ideally captures particularities about one of the entity.
@@
 Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which allows the use of various kind of statistical methods.
-The next section shows two methods of analysis based on this table.
+The next section shows a particular direction on how to use this table, with the help of \emph{embeddings}.
 
@@
 
-Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Sentiment Analysis (REF), Textometry (REF), or even Deep Learning methods (REF?).
+Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Topic Modeling (REF), Sentiment Analysis (REF), or Textometry (REF) methods.
 Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
@@
 In section \ref{entity_embeddings}, these vectors of textual units are used as anchor points in order to also embed entities into the same space.
-Therefore, it is crucial that an interpretation about the directions, or the regions, of this embedding is possible in order to properly extract information about the localization of entity vectors (the relative position of these entity vectors among themselves is insufficient).
-For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, these entities can be characterized.
-
-We propose here two embeddings verifying this condition: Section \ref{ca_method} describes \emph{Correspondence Analysis (CA)} and section \ref{wv_method} focuses on \emph{Pre-trained Word Vectors (WV)}.
+Therefore, it is crucial that an interpretation about the directions or the regions of this embedding is possible, in order to properly interpret the localization of entity vectors (the relative position of entity vectors among themselves is generally insufficient).
+For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, entities can be characterized.
+We propose two embeddings verifying this condition: Section \ref{ca_method} describes \emph{Correspondence Analysis (\textbf{CA})} and section \ref{wv_method} focuses on \emph{Pre-trained Word Vectors (\textbf{WV})}.
 
@@
 
-Using Correspondence Analysis in order to analyze textual resources has a long tradition in literature (REF).
-It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, allowing to analyze or represent the different units in terms of word frequency profiles.
-Moreover, units and words placement in the embedding space have a direct interpretation in terms of chi2 distance between profiles, which is desirable when interpreting results.
+Using \emph{Correspondence Analysis} (\textbf{CA}) in order to analyze textual resources has a long tradition (REF).
+It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, and allows the interpretation of the placement of units in terms of word frequency profiles.
+Units and words vectors in the embedding space have a direct interpretation in terms of chi2 distance between profiles.
 
-By performing a Correspondence Analysis on table $\mathbf{N}$, we directly get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
+By performing a Correspondence Analysis on table $\mathbf{N}$, we get $n$ vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ corresponding to units (rows) and $v$ vectors $\mathbf{w}_1, \ldots, \mathbf{w}_v$ corresponding to words (columns).
 Each of these vectors has a size of $\min(n, v) - 1$, which will generally be $n - 1$.
@@
 under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
-Observe that in this article, this similarity is rather computed between word and entity vectors, as defined in section \ref{entity_embeddings}, as they lie in the same space as unit vectors.
+Observe that in this article, this similarity is rather computed between a word vector and a entity vector, since the latter, as we will see in section \ref{entity_embeddings}, lies in the same space as unit vectors.
 
-Using CA to embedded units however comes with limitations.
-First, note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from CA reflect textual unit profile (in terms of words) regarding the mean profile.
+Note that vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ obtained from \textbf{CA} reflect textual unit profile (in terms of words) regarding the mean profile (the origin in the factorial map).
 This analysis is thus \emph{contrastive}: it highlights unit variations among the studied text.
@@
 
-Pre-trained word vectors, based on methods such as Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
+\emph{Pre-trained Word Vectors}$  $ (\textbf{WV}), based on methods such as Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
 They are generally obtained through a training on a very large corpora, such as Wikipedia (REF) or Common Crawl (REF), and the resulting embedding contains a large quantity of word vectors.
-As shown by multiple studies (REF), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in mutliple applications (REF).
+As shown by multiple studies (REF), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in various applications (REF).
 
-There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF).
-These vectors are often used to apply a classification or clustering algorithm on the newly embedded objects (REF), or to query information (REF).
-These methods often use the frequencies of words found in the objects, i.e.
-a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to align vectors.
-In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit sizes and gives state-of-the-art results in various tasks.
+There exists multiple methods in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF), based on pre-trained word vectors.
+These derived vectors are often used to apply a classification or clustering algorithm  (REF) on the newly embedded objects, or to query information (REF).
+In order to derive vectors for groups of words, the majority of methods use the frequencies of words in the objects, i.e.
+a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to standardize vectors.
+In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit sizes and gives state-of-the-art results in many tasks.
 
@@
 
-With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and entity vectors in section \ref{entity_embeddings}) lie in an \emph{absolute space} defined by the used word vectors.
+With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and entity vectors in section \ref{entity_embeddings}) lie in an \emph{absolute space} defined by the pre-trained word vectors.
 Comparison between different texts are therefore more pertinent in this space and comparison with words absent from the corpus can be made.
-However, it is possible that all units from a given text, if the author style is particularly marked, are located in the same region of the space.
-In this case, the list of most associated word-vectors might be similar for every unit, and the analysis might not give usable results.
+However, it is still possible that all units from a given text will be located in the same region of the space, if the style of the text is particular.
+In this case, the list of most associated word-vectors might be similar for every unit, and the analysis will not give satisfying results.
 This effect is fortunately limited by the centration of unit-vectors which occurs in the method describe in Appendix \ref{wv_details}.
@@
 The main goal of this article is not to analyze units, but rather the entities, i.e.
-the $p$ columns of table $\mathbf{O}$.
-While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{O}$ in order to build the entity vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ which lie in the same space as units.
+the $p$ columns of table $\mathbf{E}$.
+While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{E}$ in order to build the entity vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ relatively to unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$.
 
-Two propositions of method are made: the \emph{centroids} method (CENT) is describe in section \ref{centroid} and the \emph{regressions} method (REG) is explained in section \ref{regression}.
+Two propositions of method are made: the \emph{centroids method} (\textbf{CENT}) is describe in section \ref{centroid} and the \emph{regressions method} (\textbf{REG}) is explained in section \ref{regression}.
 Both methods work with the aforementioned embeddings of units.
@@
 \begin{equation}
-\mathbf{y}_k = \sum_{i=1}^n \frac{o_{ik}}{o_{\bullet k}} \mathbf{x}_i
+\mathbf{y}_k = \sum_{i=1}^n \frac{e_{ik}}{e_{\bullet k}} \mathbf{x}_i
 \end{equation}
 i.e.
-the center of mass, or \emph{centroid}, of the units containing the entity, weighted by the relative weight $\frac{o_{ik}}{o_{\bullet k}}$.
-This way of building entity vectors is closely related to the treatment of \emph{supplementary variables} found in CA (REF): these variables do not act in the choice of factorial axis, but can still be represented afterward.
+the center of mass, or \emph{centroid}, of the units containing the entity, weighted by the relative weight $\frac{e_{ik}}{e_{\bullet k}}$.
+This way of building entity vectors is closely related to the treatment of \emph{supplementary variables} found in \textbf{CA}: these variables do not act in the choice of factorial axis, but can still be represented afterward.
 However, by contrast, entity vectors are not dilated after computing centroids, which means that they lie in the same space as units (row).
@@
 \begin{equation}
-o_{ik} = \sum_{g \in \mathcal{G}} o_{ig}, \forall i \implies \mathbf{y}_k = \sum_{g \in \mathcal{G}} \frac{o_{\bullet g}}{o_{\bullet k}} \mathbf{y}_g,
+e_{ik} = \sum_{g \in \mathcal{G}} e_{ig}, \forall i \implies \mathbf{y}_k = \sum_{g \in \mathcal{G}} \frac{e_{\bullet g}}{e_{\bullet k}} \mathbf{y}_g,
 \end{equation}
@@
 By doing so, we suppose that the effect of raising both variables is not the same as raising each variable independently.
-Regression models seem therefore appropriate to capture specificities of having a particular entity in a textual unit: the presence of a character $a$ has a effect on the vocabulary of an unit, the presence of another character $b$ has an other effect, and the presence of the pair $\{a, b\}$ yet a different effect.
-Now, the dependent variable still need to be defined.
-In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the chosen unit embeddings, and each regressions is constructed to predict the $\alpha$-th coordinate of each units by using variables in the table $\mathbf{O}$.
+Regression models seem therefore appropriate to capture specificities of having a particular entity in a textual unit.
+For example, in the case of character pairs, the presence of a character $a$ will have a effect on the vocabulary of an unit, the presence of another character $b$ will have another effect, and the presence of the pair $\{a, b\}$ yet a different effect.
+Now, dependent variables in regression models still need to be defined.
+In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the embeddings, and each regression is constructed to predict the $\alpha$-th coordinate of each units by using variables in the table $\mathbf{E}$.
 In a matrix notation, all models can be written as
 \begin{align}
-\mathbf{X} = \widetilde{\mathbf{O}} \mathbf{B} + \mathbf{E}, \label{cent_sol}
+\mathbf{X} = \widetilde{\mathbf{E}} \mathbf{B} + \bm{\Sigma}, \label{cent_sol}
 \end{align}
-where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{O}}$ is the matrix $\mathbf{O}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{E}$ the $(n \times \alpha)$ matrix containing normal errors.
+where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{E}}$ is the matrix $\mathbf{E}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{\Sigma}$ the $(n \times \alpha)$ matrix containing normal errors.
 
@@
 \begin{equation}
-\mathbf{Y} = (\widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \widetilde{\mathbf{O}} + \lambda \mathbf{I}_{(p+1)})^{-1} \widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}, \label{reg_sol}
+\mathbf{Y} = (\widetilde{\mathbf{E}}^\top \textbf{Diag}(\mathbf{f}) \widetilde{\mathbf{E}} + \lambda \mathbf{I}_{(p+1)})^{-1} \widetilde{\mathbf{E}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}, \label{reg_sol}
 \end{equation}
@@
 
-An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{O}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) (with a contraction and a different weighting scheme).
+An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{E}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) (with a contraction and a different weighting scheme).
 In fact, the regressions method with a regularized term interpolate between the hypothesis where we suppose that every entity should be considered independently (with $\lambda \to 0$), to the hypothesis of additive mixture between entities (with $\lambda \to \infty$), as discussed in section \ref{centroid}.
@@
 The choice of this work is motivated by the fact that it is a large corpus, well-known, immensely studied, and containing various colorful characters and characters relationships.
-It is therefore a solid choice to clearly illustrate the potential of presented methods.
+It is therefore a solid choice to clearly illustrate the potential of the presented methodology.
 
@@
 It resulted in the detection of 54 characters.
-The entities considered in table $\mathbf{O}$ (Figure \ref{occ_table}) are single character (54 entities) and character pairs (547 entities), resulting in a table of size $365 \times 601$.
+The entities considered in table $\mathbf{E}$ (Figure \ref{occ_table}) are single character (54 entities) and character pairs (547 entities), resulting in a table of size $365 \times 601$.
 A character or a character-pairs presence is considered present iff characters are detected at least 2 times in the chapter.
@@
 Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate specific volume vocabulary.
-This new table $\mathbf{O}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
+This new table $\mathbf{E}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
 
@@
 
-Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{O}$ and $\mathbf{O}_\text{vol}$, and a considerable number of entities, results can also be presented in various ways (similarities between entities, between entities and words, etc.).
+Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{E}$ and $\mathbf{E}_\text{vol}$, and a considerable number of entities, results can also be presented in various ways (similarities between entities, between entities and words, etc.).
 Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of top associated words for a subset of entities (section \ref{diachronic}).
@@
 While somewhat inferior with the selected set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
-It should also give interesting results when comparing different corpora, due to the fixed nature of word-vectors, but case studies concerning multiple corpora are outside the scope of this article.
+It should also give interesting results when comparing different books, due to the fixed nature of word-vectors, but case studies concerning multiple works are outside the scope of this article.
 
@@
 	\label{TIME_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean entity, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).
-Note that Cosette was not found in volume 3 because she is not explicitly cited (she is often refereed as "the daugther of M.
-Leblanc").}
+	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean entity, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).}
 \end{table*}
@@
 These results are obtained from the table $\mathbf{O}_\text{vol}$ where entities are considered different based on the volume.
-By doing so, it permits to track, e.g., the evolution of associated words for entities along the book.
-Moreover, we also define a constant term $V_i$ for each volumes $i$, which absorbs the associated words for each volume.
-Results for constants and a subset of entities can be found in Table 5.
-Note that we did not show \textbf{CONT} results in this table, as they are similar to the one found in Table 3 : words are often repeated themselves among object.
+By doing so, it permits to track the evolution of similarities along the book.
+Additionally to entities, we can also define constant term $V_i$ for each volumes $i$, which absorbs the associated words with each volume.
+Results for constants and a subset of entities (Valjean, Cosette, Valjean-Cosette) can be found in Table 5.
+Note that we did not show \textbf{CONT} results in this table, as they are similar to the one found in Table 3 : words are often repeated themselves for different objects and are less convincing.
 
-Here again, we see that associated words for the \textbf{WV} method are less specific and again give the general tone of the tome or entity.
+Here again, we see that associated words for the \textbf{WV} give a general tone to tomes and entities, while \textbf{CA} results are more specific and related to particular events which occurred for characters.
+As expected, volume constants give a quick summary of each volumes, especially with the \textbf{CA-REG} method (e.g.
+$V_2$ for the Battle of Waterloo, $V_4$ for the barricade event).
+Associated words with entities also seems accurate in describing them.
+Note that Cosette was not detected in volume 3 because she is not explicitly cited (she is often refereed as "the daugther of M.
+Leblanc"), and this  also entails an absence of the Valjean-Cosette pair.
 
 \section{Conclusion}
+\label{conclusion}
 

### 2022-10-11 article/paper1.tex
write paper

@@
 This analysis is thus \emph{contrastive}: it highlights unit variations among the studied text.
-This could becomes problematic in order to study a dataset containing multiple corpora: units belonging to the same text will have a greater chance to be close from each other, and the displayed variance might be largely composed by differences of style between the different works.
+It means that the particular tone of the whole studied text might be hidden in this analysis and only the variation around this tone will be revealed.
+It might lead to the situation where the (absolute) feeling experienced by the reader will not appear in this analysis, e.g.
+a sad character in a sad book will appear joyful if he is less sad than the mean tone.
+This could becomes problematic when this method is used sequentially to study multiple works: particularities of each book will be hidden.
 Another limitation with this approach is that the words helping the interpretation of units (and entities) are contained in the studied text.
@@
 
-The five volumes of \emph{Les Misérables}, in French, were extracted from \emph{Project Gutenberg}\footnote{\url{https://www.gutenberg.org/}}, while headers and footers of each files were manually removed.
-The whole text was lower cased, lemmatized, and stopwords\footnote{from a list made by Jacques Savoy \url{http://members.unine.ch/jacques.savoy/clef/frenchST.txt}} and punctuation were removed.
+The five volumes of \emph{Les Misérables}, in French, were extracted from \emph{Project Gutenberg}\footnote{\url{https://www.gutenberg.org/}.}, while headers and footers of each files were manually removed.
+The whole text was lower cased, lemmatized, and stopwords\footnote{from a list made by Jacques Savoy \url{http://members.unine.ch/jacques.savoy/clef/frenchST.txt}.} and punctuation were removed.
 Volumes, books, and chapters breaking points were kept for later uses.
@@
 
-Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}} (REF) NER tools.
+Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}.} (REF) NER tools.
 In order to unify character and to further refine the detected characters list, we used hand-made lists of character and aliases from NER results.
@@
 
-The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} (REF) trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is 2 millions and the dimension of vectors are $300$.
+The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} (REF) trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word-vectors $m$ is 2 millions and the dimension of the vector space is $300$.
 
@@
 Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of top associated words for a subset of entities (section \ref{diachronic}).
-We invite curious readers to consult results for all words and entities, which can be found in our GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors/results}}
+We invite curious readers to consult results for all words and entities, which can be found in our GitHub repository.\footnote{the "results" folder in \url{https://github.com/gguex/char2char_vectors}.}
 
@@
 While somewhat inferior with the selected set of queries, \textbf{WV} methods have the advantage to be able to query words outside the scope of the book, as the pre-trained word embedding possess a very large vocabulary.
-It should also give interesting results when comparing different books, due to the fixed nature of word-vectors, but case studies concerning multiple works are outside the scope of this article.
 
@@
 	\label{TIME_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean entity, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).}
+	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).}
 \end{table*}
 
-These results are obtained from the table $\mathbf{O}_\text{vol}$ where entities are considered different based on the volume.
+These results are obtained from the table $\mathbf{E}_\text{vol}$ where entities are considered different based on the volume.
 By doing so, it permits to track the evolution of similarities along the book.
 Additionally to entities, we can also define constant term $V_i$ for each volumes $i$, which absorbs the associated words with each volume.
-Results for constants and a subset of entities (Valjean, Cosette, Valjean-Cosette) can be found in Table 5.
+Results for constants and a subset of entities (Valjean, Cosette, Cosette-Valjean) can be found in Table 5.
 Note that we did not show \textbf{CONT} results in this table, as they are similar to the one found in Table 3 : words are often repeated themselves for different objects and are less convincing.
@@
 Note that Cosette was not detected in volume 3 because she is not explicitly cited (she is often refereed as "the daugther of M.
-Leblanc"), and this  also entails an absence of the Valjean-Cosette pair.
+Leblanc"), and this also explains the absence of the Cosette-Valjean pair.
 
@@
 \label{conclusion}
+
+In this article, we introduced a general framework in order to automatically extract textual information about narrative entities from a small corpus or a single work.
+The framework is build on two tables, the unit-word table $\mathbf{N}$ and the unit-entity table $\mathbf{E}$.
+This data organization sets subsequent analyses into a classical statistical framework, where the goal is to see how variables in $\mathbf{E}$ (the entities) affects the variables in $\mathbf{N}$ (the vocabulary) for each textual units.
+A choice was taken to use embeddings for analyzing these effects: units and words are embedded using Correspondence Analysis or pre-trained Word Embedding on $\mathbf{N}$, and entities are embedded in the same space as units using the Centroids or the Regressions methods on $\mathbf{E}$.
+These embeddings are then used in order to see affinities between entities and words, enabling the characterization of the formers by the latters.
+A case study on \emph{Les Misérables} was performed to see if methods gave promising results.
+
+The first important choice in the analysis is how to define the size of units.
+Other corpora were also tested (e.g.
+Shakespeare plays) and it seems important to define units with at least a paragraph size (after preprocessing) in order to represent them accurately.
+Choosing small units might be able to successfully capture word specificities related to a small subset of entities, but their direction becomes almost orthogonal one to another if the size of units is too small.
+This situation results in taking into account the "noise" in subsequent analysis, typically denoting an overfitting regime with an high variance and low bias.
+By contrast, large units will result in an underfitting regime, with a low variance and high bias, failing to capture entities specificities, but more robust to particularities in word usages.
+Having enough units is also important in order to properly locate entities in the embedding space.
+In order to analyze characters and relationships, we advice the practitioner to use his prior knowledge of the work in order to split the studied narrative as close as possible to "scenes" (as found in theater), which describes a particular event between an almost constant set of characters.
+
+The second choice is to select which entities to study.
+This choice is of course driven by the studied problematic, but is also limited by the automatic extraction tools available.
+These entities can be quite various, but must appear frequently in the work in order to be placed correctly in the embedding space.
+However, it is unadvised to set an entity which is almost always there (e.g.
+a narrator), as it will already be represented by the origin in the $\mathbf{CENT}$ method or as the constant term in the $\mathbf{REG}$ method.
+As a rules of thumbs, the number of entities should ideally be lower than the number of textual units.
+However, even with an exceeding number of entities (like in our case study, where we had 547 entities for 365 units), if some entities appear rarely, analyses are still possible.
+Note that the version of the table $\mathbf{E}$ containing counts of entities rather than presence among each units was also tested in experiments, but gave similar results for the studied corpus.
+
+The choice of using embeddings, where units, entities and words are located, is motivated by the fact that the resulting space permits many types of exploration.
+As presented in this article, we can extract some of the most (or least) associated words with each entity or rank entities according to a word query.
+Nevertheless, other types of exploration could be made.
+Entities could be placed along a particular axis in the space, define with a set of positive and a set of negative words in order to highlight a particular contrast (good-bad, like in sentiment analysis, introvert-extrovert, friend-enemy, etc.).
+This approach could also be combined with a clustering of the words, or a Topic Modeling methods, thus permitting to define interpretable regions of the embedding space.
+Relative location of entities could also be used in order to cluster or classify them.
+All these leads could be explored by subsequent researches.
+
+The difference in the choice between \textbf{CA} and \textbf{WV} embeddings appears quite clearly in the results.
+\textbf{CA} highlights particular words associated with entities, very specific to the studied work and the narrative events found in it, while \textbf{WV} give a feel of the general tone in the text when these entities are present.
+This difference is explained by the fact that \textbf{CA} focuses on words appearing within the work, with possibly very different location to semantically similar words, while \textbf{WV} word-vectors are positioned regarding their semantic and syntactic similarities.
+A entity located in the \textbf{WV} space will then be in a semantic or syntactic region, and its characterizing words should all be related.
+Results show that \textbf{CA} methods generally perform better to quickly interpret entities among the narrative, but might bit limited for some applications.
+As a matter of fact, the advantage of \textbf{WV} embedding is that its space is absolute, permitting the comparison of results between sequentially studied texts, and also contains a larger vocabulary in its embedding.
+This last property could be used in order to use a fixed list of relationship attribute (e.g., friend, enemy, family, colleague), which do not necessarily appear in every text in the studied corpus, in order to categorized character relationships.
+
+The choice between the \textbf{CENT} method and the \textbf{REG} method is relatively easy: thanks to its hyperparameter $\lambda$, the \textbf{REG} method can give similar results to the \textbf{CENT} method when $\lambda$ is high (with only a contraction of entity vectors), but also give more "perpendicular" word affinities between entities when $\lambda$ is low.
+Thus, it is clearly a superior choice in order to give a variety of results.
+The choice for this hyperparameter $\lambda$ depends on what the practitioner want from his results.
+If her/his entities are defined that some of them are completely included into other, such as character and character-pair, and she/he would like to have specificities about the finer grained entity, the $\lambda$ must be set to a low value.
+By contrast, if he do not mind to have some of her/his entities defined as a mixture of others, he can set $\lambda$ to a high value.
+However, very low values of $\lambda$ should be avoided if the number of entities is high compared to the number of units, as this will lead to an overfitting of regression coefficients and will result in the association of very rare and specific words with entities.
+
+Finally, the biggest weakness of this framework yet is the difficulty to validate its pertinence.
+Several other case studies, with results carefully scrutinized regarding prior knowledge, should be undertaken in order to see if it result are solid, but this type of experiments are expansive both in time and explanation length.
+Another idea could be to use an annotated corpora such as in (REF), where human annotators already classified character relationships in various categories, and to see if the presented method can actually retrieve the different categories.
+Such an experiment can be promising, but it currently need highly performative automatic tools in order to detect and unify character entities occurrences, which is currently missing.
+Nevertheless, first case studies gave promising results for this framework, and its flexibility could lead to various applications.
 

### 2022-10-12 article/paper1.tex
write paper

@@
 
-In the field of \emph{Digital Humanities}, \emph{Distant Reading} tools (REF) allow researchers to quickly gain knowledge on textual corpora without actually reading them.
-Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summary large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus (REF).
+In the field of \emph{Digital Humanities}, \emph{Distant Reading} tools \cite{Moretti2014} allow researchers to quickly gain knowledge on textual corpora without actually reading them.
+Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summarize large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus \cite{Underwood2017}.
 Methods in this case rely heavily on Big Data and make an extensive use of Machine Learning, often with the help of supervised methods.
-In the second case, researchers use computational methods to underline hidden structures in a small corpus or even a lone text, which helps them to refine their understanding of this corpora and reinforce stated hypotheses (REF).
+In the second case, researchers use computational methods to underline hidden structures in a small corpus or even a lone text, which helps them to refine their understanding of this corpora and reinforce stated hypotheses \cite{Eve2017}.
 Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpora are small, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results.
@@
 
-When a lone (or a few) textual narrative is analyzed, a particular effort is made into studying \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book.
+When a lone (or a few) textual narrative is analyzed, a particular effort is made into studying \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book \cite{Schmid2010}.
 Researchers are often interested by characterizing them and see how they are articulated to one another in the story.
-Various computational tools can help them in this tasks, to name a few, Named Entity Recognition tools (REF), Automatic Character Networks Extraction (REF), Sentiment Analysis (REF), Topic Modeling (REF), Textometry (REF), and Word Embeddings (REF).
+Various computational tools can help them in this tasks, to name a few, Named Entity Recognition tools \cite{Agarwal2013, Chaturvedi2017, Li2022}, Automatic Character Networks Extraction \cite{Labatut2019}, Sentiment Analysis and Topic Modeling \cite{Min2019}, Textometry \cite{Novakova2019}, and Word Embeddings \cite{Grayson2016, Heuser2017, Kerr2017}.
 All these methods have been used in order to explicitly show hidden structures constructed by the author in her/his work.
@@
 
-The idea behind this methodology comes from the field of automatic extraction and analysis of \emph{character networks} from literacy works (REF).
-When building character networks from a textual narrative, the most widespread method consists in dividing the studied work into $n$ \emph{textual units} $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting characters co-occurrences in these units (REF).
+The idea behind this methodology comes from the field of automatic extraction and analysis of \emph{character networks} from literacy works (see \cite{Labatut2019} for a survey).
+When building character networks from a textual narrative, one of the most widespread methods consists in dividing the studied work into $n$ \emph{narrative units} or \emph{contexts} $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting the number of units where characters co-occurred \cite{Elsner2012, Lee2012, Rochat2014, Grener2017, Min2019}.
 Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters.
 However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
-Various improvements where proposed in order to weight or sign (or both) the edges in the character networks, such as using Sentiment Analysis (REF) Topic Modeling (REF), or BLABLA (REF).
-A particular inspiration for the current work is the article by (REF), where authors also analyzed characters in \emph{Les Misérables} by building various signed and weighted networks, with the help of Sentiment Analysis and Topic Modeling.
+Various improvements where proposed in order to weight \cite{Sack2014} or sign \cite{Krishnan2015} (or both \cite{Min2019}) the edges in the character networks.
+A particular inspiration for the current work is the article by Min and Park \cite{Min2019}, where authors also analyzed characters in \emph{Les Misérables} by building various signed and weighted networks, with the help of Sentiment Analysis and Topic Modeling.
 The current framework was build by expanding this idea of refining character relationships while keeping exploring directions as wide as possible.
-Embeddings appeared to us to be the proper tool for achieving this.
+Embeddings \cite{Incitti2023} appeared to us to be the proper tool for achieving this.
 As a matter of fact, with embeddings, the textual contents of units are transformed into workable mathematical objects (the vectors), usable for various tasks, while conserving a maximum of information.
@@
 
-Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it, such as Topic Modeling (REF), Sentiment Analysis (REF), or Textometry (REF) methods.
+Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it.
 Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
@@
 
-Using \emph{Correspondence Analysis} (\textbf{CA}) in order to analyze textual resources has a long tradition (REF).
+Using \emph{Correspondence Analysis} (\textbf{CA}) in order to analyze textual resources has a long tradition \cite{Lebart2019}.
 It has the advantage to naturally provide an embedding space, the factorial map, where units are placed alongside word vectors, and allows the interpretation of the placement of units in terms of word frequency profiles.
@@
 
-\emph{Pre-trained Word Vectors}$  $ (\textbf{WV}), based on methods such as Word2Vec (REF), Glove (REF), or fastText (REF), have recently received great attention from various fields (REFS).
-They are generally obtained through a training on a very large corpora, such as Wikipedia (REF) or Common Crawl (REF), and the resulting embedding contains a large quantity of word vectors.
-As shown by multiple studies (REF), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in various applications (REF).
+\emph{Pre-trained Word Vectors}$  $ (\textbf{WV}), based on methods such as Word2Vec \cite{Mikolov2013}, GloVe \cite{Pennington2014}, fastText \cite{Bojanowski2017}, or Bert \cite{Devlin2018} have received great attention from various fields in the last decade.
+They are generally obtained through a training on a very large corpora, such as Wikipedia or Common Crawl, and the resulting embedding contains a large quantity of word vectors.
+As shown by multiple studies (see \cite{Li2017} for a survey), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in various applications.
+We will focus here on \emph{static} word embeddings, where word vectors are fixed and do not depends on their context, like Word2Vec or fastText, because we need to have a interpretable regions of the embedding space.
 
-There exists multiple methods in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF), based on pre-trained word vectors.
-These derived vectors are often used to apply a classification or clustering algorithm  (REF) on the newly embedded objects, or to query information (REF).
+There exists multiple methods in order to find vectors for a \emph{group of words}, such as sentences \cite{Grener2017, Arora2017}, paragraphs \cite{Le2014}, or documents \cite{Kusner2015}, based on pre-trained word vectors.
+These derived vectors are often used to apply a classification or clustering algorithm on the newly embedded objects, or to query information \cite{Kusner2015, Arora2017}.
 In order to derive vectors for groups of words, the majority of methods use the frequencies of words in the objects, i.e.
 a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to standardize vectors.
-In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit sizes and gives state-of-the-art results in many tasks.
+In the present article, we use a methodology proposed in \cite{Arora2017} as it is compatible with multiple unit sizes and gives state-of-the-art results in many tasks.
 
@@
 
-Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}.} (REF) NER tools.
+Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}.} NER tools \cite{Akbik2018}.
 In order to unify character and to further refine the detected characters list, we used hand-made lists of character and aliases from NER results.
@@
 
-The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} (REF) trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word-vectors $m$ is 2 millions and the dimension of the vector space is $300$.
+The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} \cite{Bojanowski2017} trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word-vectors $m$ is 2 millions and the dimension of the vector space is $300$.
 
@@
 Here again, we see that associated words for the \textbf{WV} give a general tone to tomes and entities, while \textbf{CA} results are more specific and related to particular events which occurred for characters.
-As expected, volume constants give a quick summary of each volumes, especially with the \textbf{CA-REG} method (e.g.
+As expected, words associated with volume constants give a short overview of each volumes, especially with the \textbf{CA-REG} method (e.g.
 $V_2$ for the Battle of Waterloo, $V_4$ for the barricade event).
@@
 Finally, the biggest weakness of this framework yet is the difficulty to validate its pertinence.
-Several other case studies, with results carefully scrutinized regarding prior knowledge, should be undertaken in order to see if it result are solid, but this type of experiments are expansive both in time and explanation length.
-Another idea could be to use an annotated corpora such as in (REF), where human annotators already classified character relationships in various categories, and to see if the presented method can actually retrieve the different categories.
-Such an experiment can be promising, but it currently need highly performative automatic tools in order to detect and unify character entities occurrences, which is currently missing.
+Several other case studies, with results carefully scrutinized regarding prior knowledge, should be undertaken in order to see if it result are solid, but this type of experiments are expansive both in time and human resources.
+Another idea could be to use an annotated corpora such as in \cite{Massey2015}, where human annotators already classified character relationships in various categories.
+We could, e.g., see if the presented method can actually retrieve these categories by assigning relationship entities to the category-word with the highest similarity value.
+Such an experiment can be promising, but it requires an efficient automatic entity tagger, in order to detect and especially unify characters in a large quantity of documents, and unfortunately, this tool do not exist yet.
 Nevertheless, first case studies gave promising results for this framework, and its flexibility could lead to various applications.
@@
 \end{align*}
-For a detailed interpretation of these different quantities, see (REF).
+For a detailed interpretation of these different quantities, see \cite{Lebart2019}.
 
@@
 
-This methods is justified and detailed in (REF).
+This methods is justified and detailed in \cite{Arora2017}.
 Let $\mathbf{w}_1, \ldots, \mathbf{w}_v$ be pre-trained word vectors which appear in the studied corpus, and the $(n \times v)$ table $\mathbf{N}$ counting the frequency of these words in the $n$ textual units.
@@
 %% Define the bibliography file to be used
+\bibliographystyle{apalike}
 \bibliography{charnet}
@@
 \end{document}
-
-%%
-%% End of file

### 2022-10-12 article/paper1.tex
write paper

@@
 
-In the field of \emph{Digital Humanities}, \emph{Distant Reading} tools \cite{Moretti2014} allow researchers to quickly gain knowledge on textual corpora without actually reading them.
-Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summarize large quantities of texts, in order to quickly structure information or to deliver a speech over the whole studied corpus \cite{Underwood2017}.
+In the field of Digital Humanities, \emph{Distant Reading} tools \cite{Moretti2014} allow researchers to quickly gain knowledge on textual corpora without actually reading them.
+Purposes of these methods are various, but can be mainly categorized into two groups: in the first case, these methods are used in order to tag, classify, or summarize large quantities of documents, in order to quickly structure information or to deliver a speech over the whole studied corpus \cite{Underwood2017}.
 Methods in this case rely heavily on Big Data and make an extensive use of Machine Learning, often with the help of supervised methods.
-In the second case, researchers use computational methods to underline hidden structures in a small corpus or even a lone text, which helps them to refine their understanding of this corpora and reinforce stated hypotheses \cite{Eve2017}.
-Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpora are small, analyses are closer to the work, and methods must be more transparent in order to appropriately interpret results.
+In the second case, researchers use computational methods to underline hidden structures in a small corpus or even a single document, which helps them to refine their understanding of this corpus or to validate hypotheses \cite{Eve2017}.
+Methods in this setting can also rely on Machine Learning, but must typically be build with more caution and attention to details: corpora are smaller, analyses are closer to the work, and methods must transparent in order to appropriately interpret results.
 The use of exploratory tools and unsupervised methods is also preferred in this context, as it is less desirable to base methods on information coming from large external corpora.
-The proposed method typically belong to this second group of methods, as it is unsupervised and work on a single document.
+The proposed method in this article typically belongs to the second group, as it is unsupervised and can be applied on a single document.
 
-When a lone (or a few) textual narrative is analyzed, a particular effort is made into studying \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book \cite{Schmid2010}.
-Researchers are often interested by characterizing them and see how they are articulated to one another in the story.
+When a single (or a few) \emph{literary work} is analyzed, a common practice is to study \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book \cite{Schmid2010}.
+Researchers are frequently interested in characterizing them and seeing how they are articulated to one another in the story.
 Various computational tools can help them in this tasks, to name a few, Named Entity Recognition tools \cite{Agarwal2013, Chaturvedi2017, Li2022}, Automatic Character Networks Extraction \cite{Labatut2019}, Sentiment Analysis and Topic Modeling \cite{Min2019}, Textometry \cite{Novakova2019}, and Word Embeddings \cite{Grayson2016, Heuser2017, Kerr2017}.
@@
 It permits to find regularities and patterns, and can help to categorize particular narrative constructions, writing styles, or genres.
-These kind of methods can be great complement to classical analyses of literacy works as they allow to efficiently summarized information which is otherwise quite diffuse.
+These kind of methods can be great complement to classical analyses of literary works as they allow to efficiently summarized information which is otherwise quite diffuse.
 
-In this article, we propose a general framework in order to automatically characterize various narrative entities in a literacy work.
-The entire framework is exposed starting from a very wide perspective, which is how to organize the textual data, and is narrowed down to a very specific use, the study of character relationships in \emph{Les Misérables}, by Victor Hugo.
-Along this presentation, various choices are made to highlight a particular usage of this framework, but theses choices should be viewed as suggestion rather than rules: the real strength of this framework is its flexibility and the direction taken in this article is oriented for a particular task.
-To be more specific, we are interested here in using \emph{embeddings} in order to locate \emph{character relationships} alongside the vocabulary.
-Similarity measures can then be constructed between these words and the relationships, which can help a practitioner to characterize them.
+In this article, we propose a general framework in order to automatically characterize various narrative entities in a literary work.
+The entire framework is exposed starting from a wide perspective, which is how to organize the textual data, and is narrowed down to a specific use, the study of character relationships in \emph{Les Misérables}, by Victor Hugo.
+Along this presentation, various choices are made to highlight a particular usage of this framework, but theses choices should be viewed as suggestion rather than rules: the real strength of this framework is its flexibility and the direction taken in this article is oriented for a defined task.
+To be more specific, we will show how to use \emph{embeddings} in order to locate \emph{character relationships} alongside the vocabulary.
+An association measure can then be constructed between these words and the relationships, which can help a practitioner to characterize the latters.
 Four variations of this method are proposed, and are tested on \emph{Les Misérables}.
 
-The idea behind this methodology comes from the field of automatic extraction and analysis of \emph{character networks} from literacy works (see \cite{Labatut2019} for a survey).
+The idea behind this framework comes from the field of automatic extraction and analysis of \emph{character networks} from literacy works (see \cite{Labatut2019} for a survey).
 When building character networks from a textual narrative, one of the most widespread methods consists in dividing the studied work into $n$ \emph{narrative units} or \emph{contexts} $u_1, \ldots, u_n$, which can be, e.g., sentences, paragraphs, or chapters, and then counting the number of units where characters co-occurred \cite{Elsner2012, Lee2012, Rochat2014, Grener2017, Min2019}.
 Usually, the text constituting these units is discarded and the resulting network displays edges which roughly represent an aggregated number of interactions between characters.
-However, by doing so, the aggregation occurs on various type of interactions and will give little information about the type of relationship which exist between characters.
+However, by doing so, the aggregation occurs on various type of interactions and gives little information about the type of relationship which exist between characters.
 Various improvements where proposed in order to weight \cite{Sack2014} or sign \cite{Krishnan2015} (or both \cite{Min2019}) the edges in the character networks.
-A particular inspiration for the current work is the article by Min and Park \cite{Min2019}, where authors also analyzed characters in \emph{Les Misérables} by building various signed and weighted networks, with the help of Sentiment Analysis and Topic Modeling.
-The current framework was build by expanding this idea of refining character relationships while keeping exploring directions as wide as possible.
+A particular inspiration for the current work is the article by Min and Park (2019) \cite{Min2019}, where authors also analyzed characters in \emph{Les Misérables} by building various signed and weighted networks, with the help of Sentiment Analysis and Topic Modeling.
+The current framework was build by expanding this idea of refining character relationships by formalizing the data structure and keeping directions of exploration as wide as possible.
 Embeddings \cite{Incitti2023} appeared to us to be the proper tool for achieving this.
@@
 The current article is structured as followed.
-Section \ref{methodology} define the methodology, with section \ref{data} defining the data organization, section  \ref{unit_embeddings} describing how to embed textual units, and section \ref{entity_embeddings} deriving entity vectors lying in the same space as units.
-In section \ref{case_studie}, we present the methods and results for the case study of character relationship embeddings in \emph{Les Misérables}, and section \ref{conclusion} draw conclusions and perspectives about this work.
+Section \ref{methodology} define the framework, with section \ref{data} defining the data organization, section  \ref{unit_embeddings} describing how to embed textual units, and section \ref{entity_embeddings} deriving entity vectors lying in the same space as units.
+In section \ref{case_studie}, we present the specific methodology and results for the case study of character relationships in \emph{Les Misérables}, and section \ref{conclusion} draw conclusions and perspectives about this work.
 All (Python) scripts and datasets used in this article, as well as extended results, can be found in the dedicated GitHub repository.\footnote{\url{https://github.com/gguex/char2char_vectors}.}
 
-\section{Methodology}
+\section{Framework}
 \label{methodology}
@@
 
-In this article, the textual narrative is divided in $n$ \emph{textual units} $u_1, \ldots, u_n$, and is represented through two tables.
+In this article, a textual narrative is divided in $n$ \emph{textual units} $u_1, \ldots, u_n$, and is represented through two tables.
 The first one is well known in the field of textual analysis, and consists in the $(n \times v)$ \emph{unit-word contingency table} $\mathbf{N}$, as represented by Table 1, where $v$ is the vocabulary size.
@@
 	\label{cont_table}
-	\caption{A snippet of the contingency table $\mathbf{N}$ extracted from \emph{les Misérables}.
+	\caption{A snippet of the unit-word contingency table $\mathbf{N}$ extracted from \emph{les Misérables}.
 Rows are chapters, columns are words in the vocabulary, and cell $n_{ij}$ counts the number of time word $j$ appear in chapter $i$.}
@@
 It has a size of $(n \times p)$ where $p$ is the number of \emph{narrative entities} found in the text and cells $e_{ij}$ indicates the presence, or the count for a weighted version, of entity $j$ in unit $i$.
-An narrative entity, in the context of this article, can be loosely defined in order to be flexible for various types of works or analyses.
-It can roughly be seen as a recurring narrative object, which can contain one or more characters.
-For example, it can be a location, a character, a pair of characters (or even a triplet, a quadruplet, etc.), an oriented character interaction (e.g.
+An narrative entity, in the context of this article, can be loosely defined in order to be flexible for various types of texts or analyses.
+It can roughly be seen as a recurring object with some importance in the narration.
+For example, it can be a location, an object, a character, a pair of characters (or even a triplet, a quadruplet, etc.), an oriented character interaction (e.g.
 a dialog), or even a particular recurring event containing multiple characters (e.g.
 a meeting).
-In this article, we mostly consider character and pair of characters as entities, as shown in Table 2.
-Note that we consider that a character or a pair of characters are present in the unit if character names (or aliases) are detected above a fixed threshold.
-A weighted version of this table, where $e_{ij}$ contain the number of occurrences of the entity $j$ in the unit $i$, is also possible and formulas are written accordingly.
+In this article, we mostly consider character and pairs of characters as entities, as shown in Table 2.
+Note that in the present case, we consider that a character or a pair of characters are present in the unit if character names (or aliases) are detected above a fixed threshold.
+A weighted version of this table, where $e_{ij}$ contains the number of occurrences of the entity $j$ in the unit $i$, is also possible.
+However, equations presented in this article are written for the presence/absence version.
 
@@
 	\label{occ_table}
-	\caption{A snippet of the entities table $\mathbf{E}$ extracted from \emph{les Misérables}.
+	\caption{A snippet of the unit-entity table $\mathbf{E}$ extracted from \emph{les Misérables}.
 Rows are chapters, columns are characters (top) and character-pairs (bottom), and cell $e_{ij}$ denotes if $j$ appear in chapter $i$.}
@@
 
-This data organization already gives an orientation to the subsequent analyses and should be kept in mind of the practitioner.
+This data organization already gives an orientation to subsequent analyses, and should be kept in mind of the practitioner.
 Textual unit are now considered as \emph{individuals} (in the statistical terminology), defined by their \emph{variables} contained in the different columns of both tables.
-Moreover, subsequent analyses are oriented in searching how the entity table $\mathbf{E}$ has an influence over the contingency table $\mathbf{N}$, i.e.
+Moreover, subsequent analyses are oriented in searching how the unit-entity table $\mathbf{E}$ has an influence over the unit-word table $\mathbf{N}$, i.e.
 searching which words are over-represented or under-represented knowing entities in the unit.
-While authors use characters in order to build the narrative, we, to a certain extent, work backward: we are searching how character appearances and interactions in the textual unit act on her/his choice of words.
-If the extraction method permits it, a practitioner should include all entities which she/he desire to study.
+While an authors uses characters in order to build her/his narrative, we, to a certain extent, work backward: we are searching how character appearances and interactions in the textual unit act on her/his choice of words.
+If the extraction method permits it, a practitioner should include all entities which she/he desires to study.
 Here, for example, the choice to include character-pairs along with characters is motivated by the fact that we are interested in studying character relationships.
@@
 The use of a contingency table $\mathbf{N}$ to represent the textual resource present in the units denotes a \emph{Bag-of-Words} approach.
-Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which allows the use of various kind of statistical methods.
-The next section shows a particular direction on how to use this table, with the help of \emph{embeddings}.
+Using this approach loses the information relative to the order of words in the units, but permits to transform a chain of characters, improper to statistical analyses, into a contingency table, a well studied mathematical object which allows the use of various kind of computational methods.
+The next section shows a particular direction on how to use this table, with the help of embeddings.
 
@@
 Various methods can be performed on the contingency table $\mathbf{N}$ in order to extract information from it.
-Here, we make to choice to extract a lower dimensional, numeric representation of each units, in other words, an \emph{embedding of textual units}.
+Here, we make to choice to extract a lower dimensional, numeric representation of each unit, in other words, a \emph{textual unit vector} located in an \emph{embedding space}.
 \\
 In section \ref{entity_embeddings}, these vectors of textual units are used as anchor points in order to also embed entities into the same space.
-Therefore, it is crucial that an interpretation about the directions or the regions of this embedding is possible, in order to properly interpret the localization of entity vectors (the relative position of entity vectors among themselves is generally insufficient).
+Therefore, it is crucial that an interpretation about the directions or the regions of this embedding space is possible, in order to properly interpret the localization of entity vectors (the relative position of entity vectors among themselves is generally insufficient).
 For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, entities can be characterized.
@@
 
-The association between a particular unit $i$ and a word $j$ is expressed through the scalar product between their vectors $s_{ij} := \mathbf{x}^\top_i \mathbf{w}_j$, which act as a similarity measure.
+An \emph{association score} between a particular unit $i$ and a word $j$ is expressed through the scalar product between their vectors 
+\begin{equation}
+a_{ij} := \mathbf{x}^\top_i \mathbf{w}_j.
+\end{equation}
 A positive (resp.
-negative) similarity denotes a over-representation (resp.
+negative) association score denotes a over-representation (resp.
 under-representation) of the word $j$ in $i$, which permit to find lists of words characterizing the different units.
-Observe that in this article, this similarity is rather computed between a word vector and a entity vector, since the latter, as we will see in section \ref{entity_embeddings}, lies in the same space as unit vectors.
+Observe that in this article, this association score is rather computed between a word vector and a entity vector, since the latter, as we will see in section \ref{entity_embeddings}, lies in the same space as unit vectors.
+We could also track how units (or entities) are dissimilar to each others by using this time the Euclidean distance between vectors.
 
@@
 It means that the particular tone of the whole studied text might be hidden in this analysis and only the variation around this tone will be revealed.
-It might lead to the situation where the (absolute) feeling experienced by the reader will not appear in this analysis, e.g.
-a sad character in a sad book will appear joyful if he is less sad than the mean tone.
-This could becomes problematic when this method is used sequentially to study multiple works: particularities of each book will be hidden.
+It might lead to the situation where the (absolute) feeling experienced by the reader will not appear in this analysis, e.g., a sad character in a sad book might appear joyful if he is less sad than the mean tone.
+This can become problematic when this method is used sequentially to study multiple works: particularities of each book will be hidden.
 Another limitation with this approach is that the words helping the interpretation of units (and entities) are contained in the studied text.
@@
 They are generally obtained through a training on a very large corpora, such as Wikipedia or Common Crawl, and the resulting embedding contains a large quantity of word vectors.
-As shown by multiple studies (see \cite{Li2017} for a survey), these vectors are placed in order to reflect semantic and syntactic similarities between words, and are used in various applications.
-We will focus here on \emph{static} word embeddings, where word vectors are fixed and do not depends on their context, like Word2Vec or fastText, because we need to have a interpretable regions of the embedding space.
+As shown by multiple studies (see \cite{Li2017} for a survey), these vectors are placed in order to reflect semantic and syntactic relationships between words, and are used in various applications.
+We focus here on \emph{static} word embeddings, where word vectors are fixed and do not depends on their context, obtained by, e.g., fastText.
+The reason is that we need to have interpretable regions in an unchanging embedding space.
 
-There exists multiple methods in order to find vectors for a \emph{group of words}, such as sentences \cite{Grener2017, Arora2017}, paragraphs \cite{Le2014}, or documents \cite{Kusner2015}, based on pre-trained word vectors.
+Multiple methods exist which use pre-trained word vectors in order to derive vectors for a \emph{group of words}, such as sentences \cite{Grener2017, Arora2017}, paragraphs \cite{Le2014}, or documents \cite{Kusner2015}.
 These derived vectors are often used to apply a classification or clustering algorithm on the newly embedded objects, or to query information \cite{Kusner2015, Arora2017}.
-In order to derive vectors for groups of words, the majority of methods use the frequencies of words in the objects, i.e.
+In order to derive these vectors, the majority of methods use frequencies of words found in objects, i.e.
 a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and to standardize vectors.
-In the present article, we use a methodology proposed in \cite{Arora2017} as it is compatible with multiple unit sizes and gives state-of-the-art results in many tasks.
+In the present article, we use a methodology proposed in \cite{Arora2017} as it is compatible with multiple unit sizes and gives good results in many tasks.
+Thus, textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.
 
-Textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.
-The main way to interpret units with this method is to use the cosine similarity between its corresponding vector $\mathbf{x}_i$ and every word-vectors $\mathbf{w}_j$, as defined by $s_{ij} := \frac{\mathbf{x}_i^\top \mathbf{w}_j}{\sqrt{\mathbf{x}_i^\top \mathbf{x}_i \mathbf{w}_j^\top \mathbf{w}_j}}$.
-The cosine similarity also permits to compare units between themselves.
+An \emph{association score} can again be computed between an unit (or an entity) vector $\mathbf{x}_i$ and word vector $\mathbf{w}_j$ through the cosine similarity, defined by 
+\begin{equation}
+a_{ij} := \frac{\mathbf{x}_i^\top \mathbf{w}_j}{\sqrt{\mathbf{x}_i^\top \mathbf{x}_i \mathbf{w}_j^\top \mathbf{w}_j}}
+\end{equation}
+Note that, with word vectors, this cosine similarity also permits to compare units (or entities) between themselves.
 
 With the pre-trained word vector method, the unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ (and entity vectors in section \ref{entity_embeddings}) lie in an \emph{absolute space} defined by the pre-trained word vectors.
-Comparison between different texts are therefore more pertinent in this space and comparison with words absent from the corpus can be made.
-However, it is still possible that all units from a given text will be located in the same region of the space, if the style of the text is particular.
-In this case, the list of most associated word-vectors might be similar for every unit, and the analysis will not give satisfying results.
-This effect is fortunately limited by the centration of unit-vectors which occurs in the method describe in Appendix \ref{wv_details}.
+Comparison between different texts are therefore more pertinent and associations with words absent from the corpus can be made.
+However, it is possible that all units from a given text will be located in the same region of the space if the vocabulary used in it is very specific.
+In this case, the list of most associated word vectors might be similar for every unit, and the analysis will not give satisfying results.
+This effect is fortunately limited by the centration of unit vectors which occurs in the method described in Appendix \ref{wv_details}.
 
@@
 
-The main goal of this article is not to analyze units, but rather the entities, i.e.
-the $p$ columns of table $\mathbf{E}$.
-While we used the table $\mathbf{N}$ to build our embeddings of units, we now use the table $\mathbf{E}$ in order to build the entity vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ relatively to unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$.
-
-Two propositions of method are made: the \emph{centroids method} (\textbf{CENT}) is describe in section \ref{centroid} and the \emph{regressions method} (\textbf{REG}) is explained in section \ref{regression}.
-Both methods work with the aforementioned embeddings of units.
+The main goal of this article is not to analyze units, but rather entities, i.e., the $p$ columns of table $\mathbf{E}$.
+While we use the table $\mathbf{N}$ to build embeddings of units, we utilize the table $\mathbf{E}$ in order to build the entity vectors $\mathbf{y}_1, \ldots, \mathbf{y}_p$ relatively to unit vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$.
+Two propositions of methods are made: the \emph{centroids method} (\textbf{CENT}), described in section \ref{centroid}; and the \emph{regressions method} (\textbf{REG}), explained in section \ref{regression}.
+Both methods can be combined with the embeddings of units defined in the previous section.
 
@@
 
-This method is the most trivial and is based on the following intuition: an entity is characterized by all units in which it appears.
-In other words, we can define the vector $\mathbf{y}_k$ for character-object object $k$ as
+This method is the most trivial and is based on the following intuition: an entity is characterized equally by all units in which it appears.
+In other words, we can define the vector $\mathbf{y}_k$ for entity $k$ as
 \begin{equation}
-\mathbf{y}_k = \sum_{i=1}^n \frac{e_{ik}}{e_{\bullet k}} \mathbf{x}_i
+\mathbf{y}_k = \sum_{i=1}^n f_i e_{ik} \mathbf{x}_i
 \end{equation}
-i.e.
-the center of mass, or \emph{centroid}, of the units containing the entity, weighted by the relative weight $\frac{e_{ik}}{e_{\bullet k}}$.
+where $f_i = \frac{n_{i \bullet}}{n_{\bullet \bullet}}$ is the relative weight of unit $i$.
+$\mathbf{y}_k$ indicates the center of mass, or \emph{centroid}, of the units containing the entity.
 This way of building entity vectors is closely related to the treatment of \emph{supplementary variables} found in \textbf{CA}: these variables do not act in the choice of factorial axis, but can still be represented afterward.
@@
 \\
-An important remark about the centroid method, is that entity vectors positions are \emph{additive}, which means that we have
+An important remark about the centroid method, is that entity vectors positions are \emph{additive}, i.e. we have
 \begin{equation}
-e_{ik} = \sum_{g \in \mathcal{G}} e_{ig}, \forall i \implies \mathbf{y}_k = \sum_{g \in \mathcal{G}} \frac{e_{\bullet g}}{e_{\bullet k}} \mathbf{y}_g,
+e_{ik} = \sum_{g \in \mathcal{G}} e_{ig}, \forall i \implies \mathbf{y}_k = \sum_{g \in \mathcal{G}} \mathbf{y}_g,
 \end{equation}
 where $\mathcal{G}$ is a subset of entities.
-This property can be interpreted as followed: if a character $k$ can be divided among different situations $g$ (the character alone, the character in interaction with another character, etc.), the character vector $\mathbf{y}_k$ is in fact the centroid of all vectors $\mathbf{y}_g$ of these situations.
+This property can be interpreted as followed: if a character $k$ can be divided among different situations $g$ (the character alone, the character in interaction with another character, etc.), the character vector $\mathbf{y}_k$ is in fact the sum of all vectors $\mathbf{y}_g$ of these situations.
 This is not necessary an undesirable property, but it implies that the specificities of the lone character might be hidden if he is often registered in an interaction.
@@
 Now, dependent variables in regression models still need to be defined.
-In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the embeddings, and each regression is constructed to predict the $\alpha$-th coordinate of each units by using variables in the table $\mathbf{E}$.
-In a matrix notation, all models can be written as
+In fact, we are doing $d$ regressions, with $d$ the number of dimensions of the embedding, and each regression is constructed to predict the $\alpha$-th coordinate of units by using binary variables in the table $\mathbf{E}$.
+In matrix notation, all regression models can be written as
 \begin{align}
@@
 \end{align}
-where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit-vectors (on rows), $\widetilde{\mathbf{E}}$ is the matrix $\mathbf{E}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{\Sigma}$ the $(n \times \alpha)$ matrix containing normal errors.
+where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit vectors (on rows), $\widetilde{\mathbf{E}}$ is the matrix $\mathbf{E}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{\Sigma}$ the $(n \times \alpha)$ matrix containing normal errors.
 
@@
 \end{equation}
-where $\textbf{Diag}(\mathbf{f})$ is the diagonal matrix containing weights of units $\mathbf{f} = \left( \frac{n_{i \bullet}}{n_{\bullet \bullet}} \right)$, $\lambda > 1$ is the regularization coefficient, and $\mathbf{I}_{(p+1)}$ is the identity matrix of size $((p+1) \times (p+1))$.
+where $\textbf{Diag}(\mathbf{f})$ is the diagonal matrix containing weights of units $\mathbf{f} = \left( f_i \right)$, $\lambda > 1$ is the regularization coefficient, and $\mathbf{I}_{(p+1)}$ is the identity matrix of size $((p+1) \times (p+1))$.
 
-An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{E}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) (with a contraction and a different weighting scheme).
+An interesting effect of the regularization coefficient is that if $\lambda$ is high, equation (\ref{reg_sol}) becomes $\mathbf{Y} \approx \frac{1}{\lambda} \widetilde{\mathbf{E}}^\top \textbf{Diag}(\mathbf{f}) \mathbf{X}$, which is similar to equation (\ref{cent_sol}) with a contraction term $\lambda$.
 In fact, the regressions method with a regularized term interpolate between the hypothesis where we suppose that every entity should be considered independently (with $\lambda \to 0$), to the hypothesis of additive mixture between entities (with $\lambda \to \infty$), as discussed in section \ref{centroid}.
@@
 In order to see if the methods give coherent results, we have to carefully scrutinized and compared them with previous knowledge of the studied work.
-For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present here only one case studies: \emph{Les Misérables} by Victor Hugo.
+For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present here only one case study: \emph{Les Misérables} by Victor Hugo.
 The choice of this work is motivated by the fact that it is a large corpus, well-known, immensely studied, and containing various colorful characters and characters relationships.
@@
 The entities considered in table $\mathbf{E}$ (Figure \ref{occ_table}) are single character (54 entities) and character pairs (547 entities), resulting in a table of size $365 \times 601$.
-A character or a character-pairs presence is considered present iff characters are detected at least 2 times in the chapter.
+A character or a character pair is considered present iff characters are detected at least 2 times in the chapter.
 
 Note that, in section \ref{diachronic}, we also tested experiments with entities consisting in character and character-pairs as found in each volumes (e.g.
-Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate specific volume vocabulary.
+Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate volume specific vocabulary.
 This new table $\mathbf{E}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
@@
 
-The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} \cite{Bojanowski2017} trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word-vectors $m$ is 2 millions and the dimension of the vector space is $300$.
+The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} \cite{Bojanowski2017} trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word vectors $m$ is 2 millions and the dimension of the vector space is $300$.
 
-Note that, in addition to having two table 4 variations for the methods, 2 tables $\mathbf{E}$ and $\mathbf{E}_\text{vol}$, and a considerable number of entities, results can also be presented in various ways (similarities between entities, between entities and words, etc.).
+Note that, in addition to having 2 tables $\mathbf{E}$ and $\mathbf{E}_\text{vol}$, 4 variations for the methods, and a considerable number of entities, results can also be presented in various ways (similarities between entities, associations between entities and words, etc.).
 Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of top associated words for a subset of entities (section \ref{diachronic}).
@@
 	\label{word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) to a selected set of entities, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.
+	\caption{The 5 most associated words (association score in parentheses) to a selected set of entities, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.
 Words appearing at least two times within the same method are in bold.}
@@
 
-The first results in this section is to examine the most associated words with a subset of entities, as measured by the similarities defined in section \ref{unit_embeddings}.
+The first results in this section is to examine the most associated words with a subset of entities, as measured by the association score defined in section \ref{unit_embeddings}.
 Results can be found in Table 3 for all methods.
@@
 We can first observe that \textbf{CA} methods seems to summarize entities with a vocabulary closer to the work, while \textbf{WV} methods tend to frequently use words with a wider scope, with notably more verbs.
-It results in having the \textbf{WV} giving a general feeling for the tone used for describing characters and relationships, while the \textbf{CA} method can depict very specific objects, location or event associated with these entities.
-This behavior can understood by the nature of unit embeddings: in the \textbf{WV} embedding, word-vectors are fixed and do not consider the actual frequencies of words found in the studied corpora.
+It results in having the \textbf{WV} methods giving a general feeling for the tone used for describing characters and relationships, while the \textbf{CA} methods can depict very specific objects, locations or events associated with these entities.
+This behavior can be understood by the nature of unit embeddings: in the \textbf{WV} embedding, word vectors are fixed and do not take into account the actual frequencies of words found in the studied corpora.
 A character can be close to a word appearing only a few times (or none) in the corpus if this word is located near the vocabulary associated with this character, as semantically similar words are located in the same region of space.
@@
 	\label{CA_CENT_obj_words}
-	\caption{The 5 most associated entities (similarity in parentheses) to a selected set of words, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.}
+	\caption{The 5 most associated entities (association score in parentheses) to a selected set of words, regarding \textbf{CA-CENT}, \textbf{CA-REG}, \textbf{WV-CENT}, and \textbf{WV-REG} methods.}
 \end{table*}
@@
 Note that another way to represent these results is through weighted signed networks, as found in Figure 1 (for \textbf{CA-REG}).
-The network structure represent the number of time characters are detected together (which do not depend on the query), and the signed weights (edge color) display similarities between character relationship (edges) and the queried word.
+The network structure represent the number of times characters are detected together (which do not depend on the query), and the signed weights (edge color) display association score between character relationship (edges) and the queried word.
 This representation gives a quick visual support in order to explore the studied work and could be implemented as a standalone program.
@@
 	\label{TIME_REG_word_vs_obj}
-	\caption{The 5 most associated words (similarity in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).}
+	\caption{The 5 most associated words (association score in parentheses) vs volumes constant, Valjen, Cosette, and Cosette-Valjean, as found in each tome regarding the \textbf{CA-REG} and \textbf{WV-REG} methods ($\lambda = 0.01$).}
 \end{table*}
@@
 These results are obtained from the table $\mathbf{E}_\text{vol}$ where entities are considered different based on the volume.
-By doing so, it permits to track the evolution of similarities along the book.
+By doing so, it permits to track the evolution of association scores along the book.
 Additionally to entities, we can also define constant term $V_i$ for each volumes $i$, which absorbs the associated words with each volume.
@@
 As a rules of thumbs, the number of entities should ideally be lower than the number of textual units.
-However, even with an exceeding number of entities (like in our case study, where we had 547 entities for 365 units), if some entities appear rarely, analyses are still possible.
+However, even with an exceeding number of entities (like in our case study, where we had 601 and 1124 entities for 365 units), if some entities appear rarely, analyses are still possible.
 Note that the version of the table $\mathbf{E}$ containing counts of entities rather than presence among each units was also tested in experiments, but gave similar results for the studied corpus.
 
-The choice of using embeddings, where units, entities and words are located, is motivated by the fact that the resulting space permits many types of exploration.
-As presented in this article, we can extract some of the most (or least) associated words with each entity or rank entities according to a word query.
-Nevertheless, other types of exploration could be made.
-Entities could be placed along a particular axis in the space, define with a set of positive and a set of negative words in order to highlight a particular contrast (good-bad, like in sentiment analysis, introvert-extrovert, friend-enemy, etc.).
+The choice of using embeddings, where units, entities and words are located, is motivated by the fact that the resulting space permits many types of explorations.
+As presented in this article, we can extract some of the most (or least) associated words with each entity or rank entities according to a word query, but other types of measurements could also be made.
+Entities could be placed along a particular axis in the space, define with a set of positive and a set of negative words, in order to highlight a particular contrast (positive-negative, like in sentiment analysis, introvert-extrovert, friend-enemy, etc.).
 This approach could also be combined with a clustering of the words, or a Topic Modeling methods, thus permitting to define interpretable regions of the embedding space.
 Relative location of entities could also be used in order to cluster or classify them.
-All these leads could be explored by subsequent researches.
+All these leads can be explored by subsequent researches.
 
@@
 \textbf{CA} highlights particular words associated with entities, very specific to the studied work and the narrative events found in it, while \textbf{WV} give a feel of the general tone in the text when these entities are present.
-This difference is explained by the fact that \textbf{CA} focuses on words appearing within the work, with possibly very different location to semantically similar words, while \textbf{WV} word-vectors are positioned regarding their semantic and syntactic similarities.
+This difference is explained by the fact that \textbf{CA} focuses on words appearing within the work, with possibly very different location to semantically similar words, while \textbf{WV} word vectors are positioned regarding their semantic and syntactic similarities.
 A entity located in the \textbf{WV} space will then be in a semantic or syntactic region, and its characterizing words should all be related.
@@
 The choice for this hyperparameter $\lambda$ depends on what the practitioner want from his results.
-If her/his entities are defined that some of them are completely included into other, such as character and character-pair, and she/he would like to have specificities about the finer grained entity, the $\lambda$ must be set to a low value.
+If her/his entities are defined such that some of them are completely included into other, such as character and character-pair, and she/he would like to have specificities about the finer grained entity, the $\lambda$ must be set to a low value.
 By contrast, if he do not mind to have some of her/his entities defined as a mixture of others, he can set $\lambda$ to a high value.
@@
 Another idea could be to use an annotated corpora such as in \cite{Massey2015}, where human annotators already classified character relationships in various categories.
-We could, e.g., see if the presented method can actually retrieve these categories by assigning relationship entities to the category-word with the highest similarity value.
+We could, e.g., see if the presented method can actually retrieve these categories by assigning relationship entities to the category-word with the highest association value.
 Such an experiment can be promising, but it requires an efficient automatic entity tagger, in order to detect and especially unify characters in a large quantity of documents, and unfortunately, this tool do not exist yet.

### 2022-10-12 article/paper1.tex
write article

@@
 %% The "title" command^
-\title{Characterizing narrative entities with embeddings : a case study of character relationships in Les Misérables}
+\title{A framework for embedding entities in a textual narrative: a case study on Les Misérables}
 
@@
 When a single (or a few) \emph{literary work} is analyzed, a common practice is to study \emph{narrative entities} (characters, event, location, etc.) used by the author in her/his book \cite{Schmid2010}.
-Researchers are frequently interested in characterizing them and seeing how they are articulated to one another in the story.
+Researchers are frequently interested in depicting them and in seeing how they interact with each other in the story.
 Various computational tools can help them in this tasks, to name a few, Named Entity Recognition tools \cite{Agarwal2013, Chaturvedi2017, Li2022}, Automatic Character Networks Extraction \cite{Labatut2019}, Sentiment Analysis and Topic Modeling \cite{Min2019}, Textometry \cite{Novakova2019}, and Word Embeddings \cite{Grayson2016, Heuser2017, Kerr2017}.
@@
 To be more specific, we will show how to use \emph{embeddings} in order to locate \emph{character relationships} alongside the vocabulary.
-An association measure can then be constructed between these words and the relationships, which can help a practitioner to characterize the latters.
+An association measure can then be constructed between these words and the relationships, which can help a practitioner to depict the latters.
 Four variations of this method are proposed, and are tested on \emph{Les Misérables}.
@@
 	\caption{A snippet of the unit-entity table $\mathbf{E}$ extracted from \emph{les Misérables}.
-Rows are chapters, columns are characters (top) and character-pairs (bottom), and cell $e_{ij}$ denotes if $j$ appear in chapter $i$.}
+Rows are chapters, columns are characters (top) and character pairs (bottom), and cell $e_{ij}$ denotes if $j$ appear in chapter $i$.}
 \end{table}
@@
 If the extraction method permits it, a practitioner should include all entities which she/he desires to study.
-Here, for example, the choice to include character-pairs along with characters is motivated by the fact that we are interested in studying character relationships.
-A character-pair can roughly be seen as an interaction between two characters, and this interaction should be considered as an object of its own: the presence of this interaction in a unit do not result in having a mixture of words used for each character, but rather gives a specific flavor to the unit.
+Here, for example, the choice to include character pairs along with characters is motivated by the fact that we are interested in studying character relationships.
+A character pair can roughly be seen as an interaction between two characters, and this interaction should be considered as an object of its own: the presence of this interaction in a unit do not result in having a mixture of words used for each character, but rather gives a specific flavor to the unit.
 
@@
 Therefore, it is crucial that an interpretation about the directions or the regions of this embedding space is possible, in order to properly interpret the localization of entity vectors (the relative position of entity vectors among themselves is generally insufficient).
-For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, entities can be characterized.
+For that reason, we focus on embeddings of textual units which also contain \emph{vectors of words}: by examining the positions of entities relatively to word vectors, entities can be depicted.
 We propose two embeddings verifying this condition: Section \ref{ca_method} describes \emph{Correspondence Analysis (\textbf{CA})} and section \ref{wv_method} focuses on \emph{Pre-trained Word Vectors (\textbf{WV})}.
@@
 \end{align}
-where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit vectors (on rows), $\widetilde{\mathbf{E}}$ is the matrix $\mathbf{E}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each regression is contained on a column), and $\mathbf{\Sigma}$ the $(n \times \alpha)$ matrix containing normal errors.
+where $\mathbf{X} = (x_{i\alpha})$ is the $(n \times d)$ matrix containing unit vectors (on rows), $\widetilde{\mathbf{E}}$ is the matrix $\mathbf{E}$ with an first additional column of $1$ for the intercept, $\mathbf{B} = (\beta_{k\alpha})$ is the $((p+1) \times d)$ matrix containing intercepts and regression coefficients (each column corresponds to one regression), and $\mathbf{\Sigma}$ the $(n \times \alpha)$ matrix containing normal errors.
 
-Estimates $\widehat{\mathbf{B}} = (\widehat{\beta}_{k\alpha})$ for the intercept and coefficient regressions are in fact the researched embeddings for entities as well as for the intercept representing the general tone of the studied text.
-We therefore denote these estimates with $\mathbf{Y} = (y_{k\alpha})$ in the following, with the convention $y_{0\alpha}$ for intercept coefficients.
+Intercepts and coefficients estimations $\widehat{\mathbf{B}} = (\widehat{\beta}_{k\alpha})$ can be considered as our embeddings for entities as well as for the intercept, which represents the general tone of the studied text.
+We therefore denote these estimates with $\mathbf{Y} = (y_{k\alpha})$ in the following, with the notation convention $y_{0\alpha}$ for intercept coordinate $\alpha$.
 
@@
 Moreover, the quadratic error rate should also be weighted by the number of tokens in each unit.
-Including all this, we find the solution for our character-based vectors $\mathbf{y}_0, \mathbf{y}_1, \ldots, \mathbf{y}_p$ contained in rows of $\mathbf{Y}$ with
+Including all this, we find the solution for our intercept and entity vectors $\mathbf{y}_0, \mathbf{y}_1, \ldots, \mathbf{y}_p$, contained in the rows of $\mathbf{Y}$, with
 \begin{equation}
@@
 
-For the moment, it is not possible to evaluate the presented methods by the use of some measurements, which would allow to test its validity on various corpora.
+At the time of writing, it is not possible to evaluate the exposed framework with some kind of metric, which would allow to test its pertinence on various corpora.
 In order to see if the methods give coherent results, we have to carefully scrutinized and compared them with previous knowledge of the studied work.
-For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present here only one case study: \emph{Les Misérables} by Victor Hugo.
+For this reason, and because of method variations and multiplicity of the results (and lack of place), we chose to present only one case study: the analysis of characters and relationships in \emph{Les Misérables}, by Victor Hugo.
 The choice of this work is motivated by the fact that it is a large corpus, well-known, immensely studied, and containing various colorful characters and characters relationships.
-It is therefore a solid choice to clearly illustrate the potential of the presented methodology.
+It is therefore a solid choice to clearly illustrate the potential of the exposed framework.
 
@@
 
-We chose to use chapter as textual units.
+We chose to use chapters as textual units.
 The table $\mathbf{N}$ (Figure \ref{cont_table}) was build by considering words appearing at least $20$ times in the text and resulted in a table of size $365$ chapters $\times$ $1974$ words.
@@
 Characters were detected using \emph{Flair}\footnote{\url{https://github.com/flairNLP/flair}.} NER tools \cite{Akbik2018}.
-In order to unify character and to further refine the detected characters list, we used hand-made lists of character and aliases from NER results.
+In order to unify characters and to further refine the results, we used hand-made lists of character names and aliases from NER results.
 It resulted in the detection of 54 characters.
-The entities considered in table $\mathbf{E}$ (Figure \ref{occ_table}) are single character (54 entities) and character pairs (547 entities), resulting in a table of size $365 \times 601$.
-A character or a character pair is considered present iff characters are detected at least 2 times in the chapter.
+The entities considered in table $\mathbf{E}$ (Figure \ref{occ_table}) are composed of 54 single characters and 547 character pairs, resulting in a table of size $365 \times 601$.
+A character (resp.
+a pair of characters) is considered present if it is (resp.
+both are) detected at least 2 times in the chapter.
 
-Note that, in section \ref{diachronic}, we also tested experiments with entities consisting in character and character-pairs as found in each volumes (e.g.
-Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different objects), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate volume specific vocabulary.
-This new table $\mathbf{E}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words describing volumes, characters, and character relationships.
+Note that, in section \ref{diachronic}, we also tested experiments with entities consisting in characters and character pairs as found in each volumes (e.g.
+Cosette-Valjean in volume one and Cosette-Valjean in volume two are now two different entities), with the addition of volume constants ($V_i=1$ in volume $i$ and $V_i=0$ in other volumes) in order to isolate volume specific vocabulary.
+This new table $\mathbf{E}_\text{vol}$, containing $1124$ entities, permits to see a diachronic evolution of words associated with volumes, characters, and character relationships.
 
@@
 
-There are two types of methods for unit embeddings, \textbf{CA} (section \ref{ca_method}) and \textbf{WV} (section \ref{wv_method}), as well as two methods for entity embeddings, \textbf{CENT} (section \ref{centroid}) and \textbf{REG} (section \ref{regression}), making a total of 4 possibles ways for obtaining final embeddings.
+There are two types of methods for unit embeddings, \textbf{CA} (section \ref{ca_method}) and \textbf{WV} (section \ref{wv_method}), as well as two methods to derive entity embeddings from them, \textbf{CENT} (section \ref{centroid}) and \textbf{REG} (section \ref{regression}), making a total of 4 possibles ways for obtaining entity embeddings.
 
-The \textbf{CA} method is fully automated, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} \cite{Bojanowski2017} trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word vectors $m$ is 2 millions and the dimension of the vector space is $300$.
+The \textbf{CA} method do not need any external data, and results in vectors in a $364$-dimensional space, while the $\textbf{WV}$ methods is based on pre-trained word vectors using \emph{fastText} \cite{Bojanowski2017} trained on Common Crawl.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}.} For French, the number of word vectors is 2 millions and the dimension of the vector space is $300$.
 
-Note that, in addition to having 2 tables $\mathbf{E}$ and $\mathbf{E}_\text{vol}$, 4 variations for the methods, and a considerable number of entities, results can also be presented in various ways (similarities between entities, associations between entities and words, etc.).
-Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of top associated words for a subset of entities (section \ref{diachronic}).
-We invite curious readers to consult results for all words and entities, which can be found in our GitHub repository.\footnote{the "results" folder in \url{https://github.com/gguex/char2char_vectors}.}
+Note that, in addition to having 2 tables $\mathbf{E}$ and $\mathbf{E}_\text{vol}$, 4 methods, and a considerable number of words and entities, results can also be presented in various ways (similarities between entities, associations between entities and words, etc.).
+Thus, we chose to show here a selection of results for the each method: the 5 most associated words regarding a subset of entities (section \ref{words}), the 5 most associated entities regarding a subset of words (section \ref{objects}), and a diachronic study of the 5 most associated words for a subset of entities (section \ref{diachronic}).
+We invite curious readers to consult results for all words and entities, which can be found in our GitHub repository.\footnote{in the "results" folder in \url{https://github.com/gguex/char2char_vectors}.}
 
@@
 A character can be close to a word appearing only a few times (or none) in the corpus if this word is located near the vocabulary associated with this character, as semantically similar words are located in the same region of space.
-By contrast, \textbf{CA} will generally takes into account word frequencies along with specificities in order to describe an entity, and very specific words can define particular regions of space.
+By contrast, \textbf{CA} will generally takes into account word frequencies along with specificities in order to describe an entity, and semantically similar words can be located far away from each others.
 
@@
 
-\subsubsection{The most associated characters-based objects for a subset of words}
+\subsubsection{The most associated entities for a subset of words}
 \label{objects}
@@
 
-These results are extracted from the transposed table from the last, and display the most associated entities to a selected set of words.
+These results are extracted from a transposed table, and display the most associated entities to a selected set of words.
 They can be found in Table 4.
-This type of results can be seen as queries, made from a single word, which output the most associated entities in the work related to that query.
+This type of results can be seen as queries, made from a single word by a practitioner, which output the most associated entities in the work related to that query.
 We chose here to show top entities related to words "aimer", "rue", "justice" and "guerre", as they represent some of the main topics of the book.
@@
 
-\subsubsection{A diachronic study of the most associated words for a subset of character-based objects}
+\subsubsection{A diachronic study of the most associated words for a subset of entities}
 \label{diachronic}
@@
 By doing so, it permits to track the evolution of association scores along the book.
-Additionally to entities, we can also define constant term $V_i$ for each volumes $i$, which absorbs the associated words with each volume.
+Additionally to entities, we can also define a constant term $V_i$ for each volumes $i$, which absorbs the associated words with each volume.
 Results for constants and a subset of entities (Valjean, Cosette, Cosette-Valjean) can be found in Table 5.
-Note that we did not show \textbf{CONT} results in this table, as they are similar to the one found in Table 3 : words are often repeated themselves for different objects and are less convincing.
+Note that we did not show \textbf{CENT} results in this table, as they are similar to the one found in Table 3: words are often repeated for different entities and are less convincing.
 
-Here again, we see that associated words for the \textbf{WV} give a general tone to tomes and entities, while \textbf{CA} results are more specific and related to particular events which occurred for characters.
+Here again, we see that associated words for the \textbf{WV} give the general tone of tomes and entities, while \textbf{CA} results are more specific and related to particular events which occurred for characters.
 As expected, words associated with volume constants give a short overview of each volumes, especially with the \textbf{CA-REG} method (e.g.
@@
 Shakespeare plays) and it seems important to define units with at least a paragraph size (after preprocessing) in order to represent them accurately.
-Choosing small units might be able to successfully capture word specificities related to a small subset of entities, but their direction becomes almost orthogonal one to another if the size of units is too small.
-This situation results in taking into account the "noise" in subsequent analysis, typically denoting an overfitting regime with an high variance and low bias.
+Choosing small units might be able to successfully capture word specificities related to a small subset of entities, but unit vectors become almost orthogonal one to another if the size of units is too small.
+This situation results in an overfitting regime with an high variance and low bias, i.e.
+units positions can be very different with the difference of only a few rare words.
 By contrast, large units will result in an underfitting regime, with a low variance and high bias, failing to capture entities specificities, but more robust to particularities in word usages.
@@
 The second choice is to select which entities to study.
-This choice is of course driven by the studied problematic, but is also limited by the automatic extraction tools available.
+This choice is of course driven by the problematic, but is also limited by the automatic extraction tools available.
 These entities can be quite various, but must appear frequently in the work in order to be placed correctly in the embedding space.
@@
 a narrator), as it will already be represented by the origin in the $\mathbf{CENT}$ method or as the constant term in the $\mathbf{REG}$ method.
-As a rules of thumbs, the number of entities should ideally be lower than the number of textual units.
+As a rule of thumbs, the number of entities should ideally be lower than the number of textual units.
 However, even with an exceeding number of entities (like in our case study, where we had 601 and 1124 entities for 365 units), if some entities appear rarely, analyses are still possible.
@@
 Entities could be placed along a particular axis in the space, define with a set of positive and a set of negative words, in order to highlight a particular contrast (positive-negative, like in sentiment analysis, introvert-extrovert, friend-enemy, etc.).
-This approach could also be combined with a clustering of the words, or a Topic Modeling methods, thus permitting to define interpretable regions of the embedding space.
+This approach could also be combined with a clustering of the words, or a Topic Modeling method, thus permitting to further refine the different regions in the embedding space.
 Relative location of entities could also be used in order to cluster or classify them.
-All these leads can be explored by subsequent researches.
+All these leads can be explored in future researches.
 
 The difference in the choice between \textbf{CA} and \textbf{WV} embeddings appears quite clearly in the results.
-\textbf{CA} highlights particular words associated with entities, very specific to the studied work and the narrative events found in it, while \textbf{WV} give a feel of the general tone in the text when these entities are present.
-This difference is explained by the fact that \textbf{CA} focuses on words appearing within the work, with possibly very different location to semantically similar words, while \textbf{WV} word vectors are positioned regarding their semantic and syntactic similarities.
+\textbf{CA} highlights particular words associated with entities, very specific to the studied work and the narrative events found in it, while \textbf{WV} gives a general feeling of the tone of the text when these entities are present.
+This difference is explained by the fact that \textbf{CA} focuses on words appearing within the work, with possibly very different locations to semantically similar words, while \textbf{WV} word vectors are positioned regarding their semantic and syntactic similarities.
 A entity located in the \textbf{WV} space will then be in a semantic or syntactic region, and its characterizing words should all be related.
 Results show that \textbf{CA} methods generally perform better to quickly interpret entities among the narrative, but might bit limited for some applications.
-As a matter of fact, the advantage of \textbf{WV} embedding is that its space is absolute, permitting the comparison of results between sequentially studied texts, and also contains a larger vocabulary in its embedding.
-This last property could be used in order to use a fixed list of relationship attribute (e.g., friend, enemy, family, colleague), which do not necessarily appear in every text in the studied corpus, in order to categorized character relationships.
+As a matter of fact, the advantage of \textbf{WV} embeddings is that its space is absolute, permitting the comparison of results between sequentially studied texts, and also contains a larger vocabulary in its embedding.
+This last property could be used in order to use a fixed list of relationship attributes (e.g., friend, enemy, family, colleague), which do not necessarily appear in every text in the studied corpus, in order to categorized character relationships.
 
-The choice between the \textbf{CENT} method and the \textbf{REG} method is relatively easy: thanks to its hyperparameter $\lambda$, the \textbf{REG} method can give similar results to the \textbf{CENT} method when $\lambda$ is high (with only a contraction of entity vectors), but also give more "perpendicular" word affinities between entities when $\lambda$ is low.
+The choice between the \textbf{CENT} method and the \textbf{REG} method is relatively easy: thanks to its hyperparameter $\lambda$, the \textbf{REG} method can give similar results than the \textbf{CENT} method when $\lambda$ is high (with only a contraction of entity vectors), but also gives more "perpendicular" sets of words describing entities when $\lambda$ is low.
 Thus, it is clearly a superior choice in order to give a variety of results.
-The choice for this hyperparameter $\lambda$ depends on what the practitioner want from his results.
-If her/his entities are defined such that some of them are completely included into other, such as character and character-pair, and she/he would like to have specificities about the finer grained entity, the $\lambda$ must be set to a low value.
-By contrast, if he do not mind to have some of her/his entities defined as a mixture of others, he can set $\lambda$ to a high value.
-However, very low values of $\lambda$ should be avoided if the number of entities is high compared to the number of units, as this will lead to an overfitting of regression coefficients and will result in the association of very rare and specific words with entities.
+The choice for this hyperparameter $\lambda$ depends on what the practitioner desire.
+If her/his entities are defined such that some of them are completely included into others, such as character and character pair, and she/he would like to have specificities about the finer grained entity, the $\lambda$ must be set to a low value.
+By contrast, if he do not mind in having some of her/his entities described like a mixture of others, she/he can set $\lambda$ to a high value.
+However, very low values of $\lambda$ should be avoided if the number of entities is high compared to the number of units, as this will lead to an overfitting of regression coefficients and result in the association of very rare and specific words with entities.
 
 Finally, the biggest weakness of this framework yet is the difficulty to validate its pertinence.
-Several other case studies, with results carefully scrutinized regarding prior knowledge, should be undertaken in order to see if it result are solid, but this type of experiments are expansive both in time and human resources.
-Another idea could be to use an annotated corpora such as in \cite{Massey2015}, where human annotators already classified character relationships in various categories.
-We could, e.g., see if the presented method can actually retrieve these categories by assigning relationship entities to the category-word with the highest association value.
-Such an experiment can be promising, but it requires an efficient automatic entity tagger, in order to detect and especially unify characters in a large quantity of documents, and unfortunately, this tool do not exist yet.
+Several other case studies, with results carefully scrutinized regarding prior knowledge, should be undertaken in order to see if results are trustworthy, but this type of experiments are expansive both in time and human resources.
+Another idea could be to use annotated corpora such as described in \cite{Massey2015}, where human annotators classified character relationships in various categories.
+For example, we could see if the presented method can actually retrieve these categories by assigning relationships to the category-word with the highest association score.
+Such experiments are promising, but it requires an efficient automatic entity tagger, in order to detect and especially unify characters in a large quantity of documents, and unfortunately, this tool do not exist yet.
 Nevertheless, first case studies gave promising results for this framework, and its flexibility could lead to various applications.

### 2022-10-12 WV_lesMiserables.py

@@ -117,7 +117,10 @@ corpus.remove_units_without_words()
 corpus.remove_occurrences_with_frequency(1e-10)
 
 # Compute the unit vectors
+# choice 1
+#unit_coord = build_occurrences_vectors(dt_matrix.T, word_coord)
 
+# choice 2
 weighting_param = 0.01
 word_weights = corpus.units_words.to_numpy().sum(axis=0)
 word_weights = word_weights / sum(word_weights)
@@ -232,20 +235,18 @@ for to_explore_word in word_names:
 
 # Words vs Objects - centroids
 words_vs_occurrences.to_csv("results/WV_CENT_words_vs_objects.csv")
+# Words vs Objects - centroids (limited char)
+form_lim_words_vs_occurrences.to_csv("results/WV_CENT_words_vs_objects_LIMITED.csv")
 # Words vs Objects - regression
 words_vs_regressions.to_csv("results/WV_REG_words_vs_objects.csv")
+# Words vs Objects - regression (limited char)
+form_lim_words_vs_regressions.to_csv("results/WV_REG_words_vs_objects_LIMITED.csv")
+
 # Objects vs Words - centroids
 occurrences_vs_words.to_csv("results/WV_CENT_objects_vs_words.csv")
+# Objects vs Words - centroids (limited words)
+form_lim_occurrences_vs_words.to_csv("results/WV_CENT_objects_vs_words_LIMITED.csv", index=False)
 # Objects vs Words - regression
 regressions_vs_words.to_csv("results/WV_REG_objects_vs_words.csv")
-
-# -- For article
-
-form_lim_words_vs_occurrences.iloc[:, :5].to_csv("results/for_article/WV_CENT_words_vs_objects_LIMITED_1.csv",
-                                                 index=False)
-form_lim_words_vs_occurrences.iloc[:, 5:].to_csv("results/for_article/WV_CENT_words_vs_objects_LIMITED_2.csv",
-                                                 index=False)
-form_lim_words_vs_regressions.iloc[:, :5].to_csv("results/for_article/WV_REG_words_vs_objects_LIMITED_1.csv",
-                                                 index=False)
-form_lim_words_vs_regressions.iloc[:, 5:].to_csv("results/for_article/WV_REG_words_vs_objects_LIMITED_2.csv",
-                                                 index=False)
+# Objects vs Words - regression (limited words)
+form_lim_regressions_vs_words.to_csv("results/WV_REG_objects_vs_words_LIMITED.csv", index=False)

### 2022-10-13 0.1_book_char_detection.py
updated git

@@ -1,22 +1,0 @@
-from booknlp.booknlp import BookNLP
-import torch
-
-# Empty cache for memory
-torch.cuda.empty_cache()
-
-# The model pipeline
-model_params = {"pipeline": "entity", "model": "big"}
-
-# The model
-booknlp = BookNLP("en", model_params)
-
-# Input file to process
-input_file = "corpora/booknlp_corpora/candide.txt"
-
-# Output directory to store resulting files in
-output_directory = "corpora/booknlp_corpora_characters"
-
-# File within this directory will be named ${book_id}.entities, ${book_id}.tokens, etc.
-book_id = "candide"
-
-booknlp.process(input_file, output_directory, book_id)

### 2022-10-13 0.2_preprocess_booknlp_results.py

@@ -1,59 +1,0 @@
-import pandas as pd
-import re
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-min_occurrences_threshold = 2
-book_name = "candide"
-
-# -------------------------------
-#   Code
-# -------------------------------
-
-# Load entities and token list
-entities_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.entities", sep="\t")
-token_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.tokens", sep="\t")
-
-# Remove -1 entities and keep characters
-entities_df = entities_df.loc[(entities_df.COREF > 0) & (entities_df.cat == "PER")]
-
-# Build a dictionary for unique entities
-id_to_name = {}
-for entity_id in set(entities_df.COREF):
-    entity_df = entities_df.loc[entities_df.COREF == entity_id]
-    if len(entity_df) >= min_occurrences_threshold:
-        id_shortest_name = entity_df.text.str.len().idxmin()
-        entity_short_name = entity_df.text.loc[id_shortest_name]
-        id_to_name[entity_id] = entity_short_name.lower().strip()
-
-# Characters list
-characters = list(set(id_to_name.values()))
-
-# To create a dataframe
-output_data = []
-# Loop on sentence id
-for sentence_id in token_df.sentence_ID.unique():
-    # Select the sentence id
-    sentence_df = token_df[token_df.sentence_ID == sentence_id]
-    # Get paragraph id
-    paragraph_id = sentence_df.paragraph_ID.min()
-    # Get sentence
-    text = " ".join([re.sub("['_]", " ", word) for word in sentence_df.word if word != "\ufeff"])
-    # Get characters ids
-    char_ids = [int(char_id) for char_id
-                in list(entities_df.join(sentence_df, on="start_token", how="right").COREF.dropna())]
-
-    # Build row and append to dataframe
-    row_dict = {char: 0 for char in characters}
-    for char_id in char_ids:
-        if char_id in id_to_name:
-            row_dict[id_to_name[char_id]] += 1
-    row_dict["paragraph_id"] = paragraph_id
-    row_dict["text"] = text
-    output_data.append(row_dict)
-
-# Build dataframe and save it
-results_df = pd.DataFrame(output_data, columns=["paragraph_id", "text"] + characters)
-results_df.to_csv(f"corpora/relationship_preprocessed/{book_name}.tsv", sep="\t")

### 2022-10-13 1.0_preprocess_lesMiserables.py

@@ -1,122 +1,0 @@
-import os
-import pandas as pd
-import numpy as np
-from flair.models import SequenceTagger
-from flair.data import Sentence
-from tqdm import tqdm
-import re
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Input folder path
-input_corpus_path = "corpora/LesMiserables_fr/text"
-
-# Ouput folder path
-output_tsv_path = "corpora/LesMiserables_fr/LesMiserables.tsv"
-
-# Keywords for division
-division_keywords = ["Chapitre", "Livre"]
-
-# Target character file
-target_characters_path = "corpora/LesMiserables_fr/LesMiserables_characters.txt"
-
-# Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
-
-# -------------------------------
-#   Code
-# -------------------------------
-
-# Read characters
-with open(target_characters_path) as target_character_file:
-    target_characters = target_character_file.readlines()
-target_characters = [target_character.strip() for target_character in target_characters]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Get tomes
-tomes = os.listdir(input_corpus_path)
-tomes.sort()
-
-# Create dataframe for results
-target_characters.sort()
-columns_name = ["tome", *[kwd.lower() for kwd in division_keywords], "text", *target_characters]
-final_df = pd.DataFrame(columns=columns_name)
-
-# Setting tagger and divisions keywords (finer - coarser)
-flair_tagger = SequenceTagger.load("fr-ner")
-
-
-# Function for character treatment
-def recognise_character(tested_characters, ref_characters, ref_aliases):
-    # For the output
-    output_characters = []
-    # Loop on characters
-    for tested_character in tested_characters:
-        # Check if target_character is in character
-        target_characters_present = [ref_character for ref_character in ref_characters
-                                     if ref_character in tested_character]
-        if len(target_characters_present) > 0:
-            output_characters.append(max(target_characters_present))
-        else:
-            # Check if an alias key is in character
-            aliases_present = [ref_alias for ref_alias in ref_aliases.keys() if ref_alias in tested_character]
-            if len(aliases_present) > 0:
-                output_characters.append(ref_aliases[max(aliases_present)])
-
[…]

### 2022-10-13 1.1_preprocess_NotreDame.py

@@ -1,122 +1,0 @@
-import pandas as pd
-import numpy as np
-from flair.models import SequenceTagger
-from flair.data import Sentence
-from tqdm import tqdm
-import re
-from nltk.tokenize import word_tokenize
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Input folder path
-input_corpus_path = "corpora/NotreDame_fr/text/NotreDame.txt"
-
-# Ouput folder path
-output_tsv_path = "corpora/NotreDame_fr/NotreDame.tsv"
-
-# Keywords for division
-division_keywords = ["Chapitre", "LIVRE"]
-
-# Target character file
-target_characters_path = "corpora/NotreDame_fr/NotreDame_characters.txt"
-
-# Aliases file
-aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
-
-# -------------------------------
-#   Code
-# -------------------------------
-
-# Read characters
-with open(target_characters_path) as target_character_file:
-    target_characters = target_character_file.readlines()
-target_characters = [target_character.strip() for target_character in target_characters]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Create dataframe for results
-target_characters.sort()
-columns_name = [*[kwd.lower() for kwd in division_keywords], "text", *target_characters]
-final_df = pd.DataFrame(columns=columns_name)
-
-# Setting tagger and divisions keywords (finer - coarser)
-flair_tagger = SequenceTagger.load("fr-ner")
-
-
-# Function for character treatment
-def recognise_character(tested_characters, ref_characters, ref_aliases):
-    # For the output
-    output_characters = []
-    # Loop on characters
-    for tested_character in tested_characters:
-        # Check if target_character is in character
-        target_characters_present = [ref_character for ref_character in ref_characters
-                                     if ref_character in tested_character]
-        if len(target_characters_present) > 0:
-            output_characters.append(max(target_characters_present))
-        else:
-            # Check if an alias key is in character
-            aliases_present = [ref_alias for ref_alias in ref_aliases.keys() if ref_alias in tested_character]
-            if len(aliases_present) > 0:
-                output_characters.append(ref_aliases[max(aliases_present)])
-
-    # Return result
-    return output_characters
-
-
-# Counter for division
-divisions_counters = np.repeat(0, len(division_keywords))
-
[…]

### 2022-10-13 1.2_preprocess_Hamlet.py

@@ -1,181 +1,0 @@
-import re
-
-import numpy as np
-import pandas as pd
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Input/output paths
-input_corpus_path = "corpora/Hamlet/Hamlet.txt"
-output_tsv_path = "corpora/Hamlet/Hamlet.tsv"
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-# Loading the corpus
-with open(input_corpus_path) as corpus_file:
-    corpus_lines = corpus_file.readlines()
-
-# Detect character
-act_presences = []
-scene_presences = []
-speaking_characters = []
-speaking_lines = []
-entrances = []
-actions = []
-for id_line, line in enumerate(corpus_lines):
-
-    # Detect act or scene
-    act_bool = ("ACT" in line)
-    scene_bool = ("SCENE" in line)
-    # Detect entrance
-    entrance_detect = re.search("^(Enter|Re-enter) ", line)
-    # Detect action
-    action_detect = re.search("^\[\_", line)
-    # Detect character
-    char_detect = re.search("[A-Z `'’]{3,}\.", line)
-
-    # Potential adding
-    speaking_character = ""
-    speaking_line = ""
-    entrance = ""
-    action = ""
-
-    # Check if entrance
-    if entrance_detect is not None:
-        entrance = line[entrance_detect.span()[1]:]
-    # Check if action
-    elif action_detect is not None:
-        action = line[action_detect.span()[1]:-3]
-    elif (not act_bool) and (not scene_bool):
-        if char_detect is not None:
-            speaking_character = char_detect.group()[:-1]
-            speaking_line = line[char_detect.span()[1]:]
-        else:
-            speaking_line = line
-
-    # Save results
-    act_presences.append(act_bool)
-    scene_presences.append(scene_bool)
-    speaking_characters.append(speaking_character)
-    speaking_lines.append(speaking_line)
-    entrances.append(entrance)
-    actions.append(action)
-
-# Get the characters
-unique_character = [char.lower().strip() for char in set(speaking_characters) if char != ""]
-unique_character = list(set(unique_character))
-unique_character.remove("all")
-unique_character.remove("first player")
-unique_character.append("player")
-unique_character.remove("both")
-unique_character.remove("lords")
-
-# Treat entrances
-list_of_entrances = []
-for entrance in entrances:
-    if "a King and a Queen" in entrance:
-        char_detected = ["player king", "player queen"]
-    elif "two Clowns" in entrance:
[…]

### 2022-10-13 1.3_preprocess_Romeo&Juliet.py

@@ -1,183 +1,0 @@
-import re
-
-import numpy as np
-import pandas as pd
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Input/output paths
-input_corpus_path = "corpora/Romeo&Juliet/Romeo&Juliet.txt"
-output_tsv_path = "corpora/Romeo&Juliet/Romeo&Juliet.tsv"
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-# Loading the corpus
-with open(input_corpus_path) as corpus_file:
-    corpus_lines = corpus_file.readlines()
-
-# Detect character
-act_presences = []
-scene_presences = []
-speaking_characters = []
-speaking_lines = []
-entrances = []
-actions = []
-for id_line, line in enumerate(corpus_lines):
-
-    # Strip line
-    line = line.strip()
-    # Detect act or scene
-    act_bool = ("ACT" in line)
-    scene_bool = ("SCENE" in line)
-    # Detect entrance
-    entrance_detect = re.search("^(Enter|Re-enter) ", line)
-    # Detect action
-    action_detect = re.search("^\[\_", line)
-    # Detect character
-    char_detect = re.search("[A-Z `'’]{3,}\.", line)
-
-    # Potential adding
-    speaking_character = ""
-    speaking_line = ""
-    entrance = ""
-    action = ""
-
-    # Check if entrance
-    if entrance_detect is not None:
-        entrance = line[entrance_detect.span()[1]:]
-    # Check if action
-    elif action_detect is not None:
-        action = line[action_detect.span()[1]:-3]
-    elif (not act_bool) and (not scene_bool):
-        if char_detect is not None:
-            speaking_character = char_detect.group()[:-1]
-            speaking_line = line[char_detect.span()[1]:]
-        else:
-            speaking_line = line
-
-    # Save results
-    act_presences.append(act_bool)
-    scene_presences.append(scene_bool)
-    speaking_characters.append(speaking_character)
-    speaking_lines.append(speaking_line)
-    entrances.append(entrance)
-    actions.append(action)
-
-# Get the characters
-unique_character = [char.lower().strip() for char in set(speaking_characters) if char != ""]
-unique_character = list(set(unique_character))
-
-# Treat entrances
-list_of_entrances = []
-for entrance in entrances:
-    if "a King and a Queen" in entrance:
-        char_detected = ["player king", "player queen"]
-    elif "two Clowns" in entrance:
-        char_detected = ["first clown", "second clown"]
-    else:
[…]

### 2022-10-13 1.4_preprocess_text.py

@@ -1,47 +1,0 @@
-import pandas as pd
-import spacy
-from local_functions import process_text
-from tqdm import tqdm
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/booknlp_preprocessed/candide.tsv"
-# Outfile
-output_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
-# Language ("fr" or "en")
-language = "en"
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-# Load the dataframe
-corpus_df = pd.read_csv(corpus_tsv_path, sep="\t", index_col=0)
-
-# Get the texts
-texts = corpus_df["text"]
-
-# Load the spacy model depending on language
-if language == "fr":
-    nlp = spacy.load("fr_core_news_lg")
-else:
-    nlp = spacy.load("en_core_web_lg")
-
-# Process the text
-processed_texts = []
-for text in tqdm(texts):
-    text_pp = nlp(text)
-    lemmas_pp = " ".join([word.lemma_ for word in text_pp if word.lemma_.strip() != ""])
-    processed_texts.append(process_text(lemmas_pp))
-
-# Change the text to the processed text
-corpus_df["text"] = processed_texts
-
-# Remove empty lines
-corpus_df = corpus_df[corpus_df["text"] != ""]
-
-# Save the new corpus
-corpus_df.to_csv(output_tsv_path, sep="\t")

### 2022-10-13 2.0_CA_lesMiserables.py

@@ -1,353 +1,0 @@
-from local_functions import *
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
-# Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 20
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 1
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter (0.1)
-regularization_parameter = 1
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
-interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
[…]

### 2022-10-13 2.2_CA_NotreDame.py

@@ -1,148 +1,0 @@
-from local_functions import *
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/NotreDame_fr/NotreDame_tokens.tsv"
-# Aliases file
-aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 10
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 1
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
-interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
-corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
-
-# Make occurrences binary
[…]

### 2022-10-13 2.3_CA_Hamlet.py

@@ -1,137 +1,0 @@
-from local_functions import *
-from nltk.corpus import stopwords
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/Hamlet/Hamlet_tokens.tsv"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 2
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-used_stop_words = stopwords.words('english')
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns)]
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Build interactions and add them to data
-interaction_occurrences = build_directed_interactions(list(corpus.meta_variables.speaking), corpus.occurrences,
-                                                      max_interaction_degree)
-corpus.occurrences = interaction_occurrences
-
-# Make occurrences binary
-corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
-
-# Make the occurrences across a meta
-corpus.update_occurrences_across_meta(meta_for_occurrences)
-
-# Make sure no units are empty
-corpus.remove_units_without_words()
-#corpus.remove_units_without_occurrences()
-corpus.remove_occurrences_with_frequency(1e-10)
-corpus.remove_words_with_frequency(1e-10)
-
-# Get units weights
-f_row = corpus.n_tokens / corpus.n_tokens.sum()
-
[…]

### 2022-10-13 2.4_CA_Romeo&Juliet.py

@@ -1,137 +1,0 @@
-from nltk.corpus import stopwords
-from local_functions import *
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/Romeo&Juliet/Romeo&Juliet_tokens.tsv"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 3
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-# -------------------------------
-#  Code
-# -------------------------------
-
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-used_stop_words = stopwords.words('english')
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns)]
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Build interactions and add them to data
-interaction_occurrences = build_directed_interactions(list(corpus.meta_variables.speaking), corpus.occurrences,
-                                                      max_interaction_degree)
-corpus.occurrences = interaction_occurrences
-
-# Make occurrences binary
-corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
-
-# Make the occurrences across a meta
-corpus.update_occurrences_across_meta(meta_for_occurrences)
-
-# Make sure no units are empty
-corpus.remove_units_without_words()
-#corpus.remove_units_without_occurrences()
-corpus.remove_occurrences_with_frequency(1e-10)
-corpus.remove_words_with_frequency(1e-10)
-
-# Get units weights
-f_row = corpus.n_tokens / corpus.n_tokens.sum()
-
[…]

### 2022-10-13 3.0_WV_lesMiserables.py

@@ -1,197 +1,0 @@
-from local_functions import *
-from gensim.models import KeyedVectors
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
-# Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 3
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 0.01
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
[…]

### 2022-10-13 3.1_WV_NotreDame.py

@@ -1,197 +1,0 @@
-from local_functions import *
-from gensim.models import KeyedVectors
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/NotreDame_fr/NotreDame.tsv"
-# Aliases file
-aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 1
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
[…]

### 2022-10-13 3.2_WV_booknlp.py

@@ -1,168 +1,0 @@
-from local_functions import *
-from gensim.models import KeyedVectors
-from nltk.corpus import stopwords
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
-# Word vectors to use
-word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
-# Set aggregation level (None for each line)
-aggregation_level = "paragraph_id"
-# Minimum occurrences for words
-min_word_frequency = 5
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 5
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-# Regularization parameter
-regularization_parameter = 1
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-used_stop_words = stopwords.words('english')
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns)]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
-
-# Make a threshold for the minimum vocabulary and remove units without words
-corpus.remove_words_with_frequency(min_word_frequency)
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
-interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
-corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
-
-# Make occurrences binary
-corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
-
-# Make the occurrences across a meta
-corpus.update_occurrences_across_meta(meta_for_occurrences)
-
-# Make sure no units are empty
-corpus.remove_units_without_words()
-corpus.remove_units_without_occurrences()
[…]

### 2022-10-13 4.0_NMF_lesMiserables.py

@@ -1,121 +1,0 @@
-from sklearn.decomposition import NMF, LatentDirichletAllocation
-from sklearn.feature_extraction.text import TfidfVectorizer
-from local_functions import *
-
-# -------------------------------
-#  Parameters
-# -------------------------------
-
-# Corpus tsv path
-corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
-# Aliases file
-aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
-# Set aggregation level (None for each line)
-aggregation_level = "chapitre"
-# Max interactions
-max_interaction_degree = 2
-# The minimum occurrences for an object to be considered
-min_occurrences = 3
-# Use a meta variable to build occurrences (None for original)
-meta_for_occurrences = None
-
-# -------------------------------
-#  Loading
-# -------------------------------
-
-# Load stopwords
-with open("aux_files/frenchST.txt") as stopwords_file:
-    used_stop_words = stopwords_file.readlines()
-used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
-
-# Read aliases
-with open(aliases_path) as aliases_file:
-    aliases = aliases_file.readlines()
-aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
-
-# Load dataframe
-corpus = CharacterCorpus()
-corpus.load_corpus(corpus_tsv_path)
-
-# Get character names
-character_names = [process_text(character_name)
-                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
-
-# -------------------------------
-#  Processing
-# -------------------------------
-
-# Aggregate on the level
-corpus.aggregate_on(aggregation_level)
-
-# Construct the unit-term matrix and remove rare words
-corpus.build_units_words(TfidfVectorizer(max_df=0.95, min_df=2, max_features=2000, stop_words=used_stop_words))
-
-# Remove characters from words
-corpus.remove_words(character_names)
-
-# Build interactions and add them to data
-interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
-corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
-
-# Make occurrences binary
[…]

### 2022-10-13 other_scripts/0.1_book_char_detection.py
add other_scripts

@@ -1,0 +1,22 @@
+from booknlp.booknlp import BookNLP
+import torch
+
+# Empty cache for memory
+torch.cuda.empty_cache()
+
+# The model pipeline
+model_params = {"pipeline": "entity", "model": "big"}
+
+# The model
+booknlp = BookNLP("en", model_params)
+
+# Input file to process
+input_file = "corpora/booknlp_corpora/candide.txt"
+
+# Output directory to store resulting files in
+output_directory = "corpora/booknlp_corpora_characters"
+
+# File within this directory will be named ${book_id}.entities, ${book_id}.tokens, etc.
+book_id = "candide"
+
+booknlp.process(input_file, output_directory, book_id)

### 2022-10-13 other_scripts/0.2_preprocess_booknlp_results.py

@@ -1,0 +1,59 @@
+import pandas as pd
+import re
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+min_occurrences_threshold = 2
+book_name = "candide"
+
+# -------------------------------
+#   Code
+# -------------------------------
+
+# Load entities and token list
+entities_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.entities", sep="\t")
+token_df = pd.read_csv(f"corpora/relationship_corpora_characters/{book_name}.tokens", sep="\t")
+
+# Remove -1 entities and keep characters
+entities_df = entities_df.loc[(entities_df.COREF > 0) & (entities_df.cat == "PER")]
+
+# Build a dictionary for unique entities
+id_to_name = {}
+for entity_id in set(entities_df.COREF):
+    entity_df = entities_df.loc[entities_df.COREF == entity_id]
+    if len(entity_df) >= min_occurrences_threshold:
+        id_shortest_name = entity_df.text.str.len().idxmin()
+        entity_short_name = entity_df.text.loc[id_shortest_name]
+        id_to_name[entity_id] = entity_short_name.lower().strip()
+
+# Characters list
+characters = list(set(id_to_name.values()))
+
+# To create a dataframe
+output_data = []
+# Loop on sentence id
+for sentence_id in token_df.sentence_ID.unique():
+    # Select the sentence id
+    sentence_df = token_df[token_df.sentence_ID == sentence_id]
+    # Get paragraph id
+    paragraph_id = sentence_df.paragraph_ID.min()
+    # Get sentence
+    text = " ".join([re.sub("['_]", " ", word) for word in sentence_df.word if word != "\ufeff"])
+    # Get characters ids
+    char_ids = [int(char_id) for char_id
+                in list(entities_df.join(sentence_df, on="start_token", how="right").COREF.dropna())]
+
+    # Build row and append to dataframe
+    row_dict = {char: 0 for char in characters}
+    for char_id in char_ids:
+        if char_id in id_to_name:
+            row_dict[id_to_name[char_id]] += 1
+    row_dict["paragraph_id"] = paragraph_id
+    row_dict["text"] = text
+    output_data.append(row_dict)
+
+# Build dataframe and save it
+results_df = pd.DataFrame(output_data, columns=["paragraph_id", "text"] + characters)
+results_df.to_csv(f"corpora/relationship_preprocessed/{book_name}.tsv", sep="\t")

### 2022-10-13 other_scripts/1.0_preprocess_lesMiserables.py

@@ -1,0 +1,122 @@
+import os
+import pandas as pd
+import numpy as np
+from flair.models import SequenceTagger
+from flair.data import Sentence
+from tqdm import tqdm
+import re
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Input folder path
+input_corpus_path = "corpora/LesMiserables_fr/text"
+
+# Ouput folder path
+output_tsv_path = "corpora/LesMiserables_fr/LesMiserables.tsv"
+
+# Keywords for division
+division_keywords = ["Chapitre", "Livre"]
+
+# Target character file
+target_characters_path = "corpora/LesMiserables_fr/LesMiserables_characters.txt"
+
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+
+# -------------------------------
+#   Code
+# -------------------------------
+
+# Read characters
+with open(target_characters_path) as target_character_file:
+    target_characters = target_character_file.readlines()
+target_characters = [target_character.strip() for target_character in target_characters]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Get tomes
+tomes = os.listdir(input_corpus_path)
+tomes.sort()
+
+# Create dataframe for results
+target_characters.sort()
+columns_name = ["tome", *[kwd.lower() for kwd in division_keywords], "text", *target_characters]
+final_df = pd.DataFrame(columns=columns_name)
+
+# Setting tagger and divisions keywords (finer - coarser)
+flair_tagger = SequenceTagger.load("fr-ner")
+
+
+# Function for character treatment
+def recognise_character(tested_characters, ref_characters, ref_aliases):
+    # For the output
+    output_characters = []
+    # Loop on characters
+    for tested_character in tested_characters:
+        # Check if target_character is in character
+        target_characters_present = [ref_character for ref_character in ref_characters
+                                     if ref_character in tested_character]
+        if len(target_characters_present) > 0:
+            output_characters.append(max(target_characters_present))
+        else:
+            # Check if an alias key is in character
+            aliases_present = [ref_alias for ref_alias in ref_aliases.keys() if ref_alias in tested_character]
+            if len(aliases_present) > 0:
+                output_characters.append(ref_aliases[max(aliases_present)])
+
[…]

### 2022-10-13 other_scripts/1.1_preprocess_NotreDame.py

@@ -1,0 +1,122 @@
+import pandas as pd
+import numpy as np
+from flair.models import SequenceTagger
+from flair.data import Sentence
+from tqdm import tqdm
+import re
+from nltk.tokenize import word_tokenize
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Input folder path
+input_corpus_path = "corpora/NotreDame_fr/text/NotreDame.txt"
+
+# Ouput folder path
+output_tsv_path = "corpora/NotreDame_fr/NotreDame.tsv"
+
+# Keywords for division
+division_keywords = ["Chapitre", "LIVRE"]
+
+# Target character file
+target_characters_path = "corpora/NotreDame_fr/NotreDame_characters.txt"
+
+# Aliases file
+aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
+
+# -------------------------------
+#   Code
+# -------------------------------
+
+# Read characters
+with open(target_characters_path) as target_character_file:
+    target_characters = target_character_file.readlines()
+target_characters = [target_character.strip() for target_character in target_characters]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Create dataframe for results
+target_characters.sort()
+columns_name = [*[kwd.lower() for kwd in division_keywords], "text", *target_characters]
+final_df = pd.DataFrame(columns=columns_name)
+
+# Setting tagger and divisions keywords (finer - coarser)
+flair_tagger = SequenceTagger.load("fr-ner")
+
+
+# Function for character treatment
+def recognise_character(tested_characters, ref_characters, ref_aliases):
+    # For the output
+    output_characters = []
+    # Loop on characters
+    for tested_character in tested_characters:
+        # Check if target_character is in character
+        target_characters_present = [ref_character for ref_character in ref_characters
+                                     if ref_character in tested_character]
+        if len(target_characters_present) > 0:
+            output_characters.append(max(target_characters_present))
+        else:
+            # Check if an alias key is in character
+            aliases_present = [ref_alias for ref_alias in ref_aliases.keys() if ref_alias in tested_character]
+            if len(aliases_present) > 0:
+                output_characters.append(ref_aliases[max(aliases_present)])
+
+    # Return result
+    return output_characters
+
+
+# Counter for division
+divisions_counters = np.repeat(0, len(division_keywords))
+
[…]

### 2022-10-13 other_scripts/1.2_preprocess_Hamlet.py

@@ -1,0 +1,181 @@
+import re
+
+import numpy as np
+import pandas as pd
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Input/output paths
+input_corpus_path = "corpora/Hamlet/Hamlet.txt"
+output_tsv_path = "corpora/Hamlet/Hamlet.tsv"
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+# Loading the corpus
+with open(input_corpus_path) as corpus_file:
+    corpus_lines = corpus_file.readlines()
+
+# Detect character
+act_presences = []
+scene_presences = []
+speaking_characters = []
+speaking_lines = []
+entrances = []
+actions = []
+for id_line, line in enumerate(corpus_lines):
+
+    # Detect act or scene
+    act_bool = ("ACT" in line)
+    scene_bool = ("SCENE" in line)
+    # Detect entrance
+    entrance_detect = re.search("^(Enter|Re-enter) ", line)
+    # Detect action
+    action_detect = re.search("^\[\_", line)
+    # Detect character
+    char_detect = re.search("[A-Z `'’]{3,}\.", line)
+
+    # Potential adding
+    speaking_character = ""
+    speaking_line = ""
+    entrance = ""
+    action = ""
+
+    # Check if entrance
+    if entrance_detect is not None:
+        entrance = line[entrance_detect.span()[1]:]
+    # Check if action
+    elif action_detect is not None:
+        action = line[action_detect.span()[1]:-3]
+    elif (not act_bool) and (not scene_bool):
+        if char_detect is not None:
+            speaking_character = char_detect.group()[:-1]
+            speaking_line = line[char_detect.span()[1]:]
+        else:
+            speaking_line = line
+
+    # Save results
+    act_presences.append(act_bool)
+    scene_presences.append(scene_bool)
+    speaking_characters.append(speaking_character)
+    speaking_lines.append(speaking_line)
+    entrances.append(entrance)
+    actions.append(action)
+
+# Get the characters
+unique_character = [char.lower().strip() for char in set(speaking_characters) if char != ""]
+unique_character = list(set(unique_character))
+unique_character.remove("all")
+unique_character.remove("first player")
+unique_character.append("player")
+unique_character.remove("both")
+unique_character.remove("lords")
+
+# Treat entrances
+list_of_entrances = []
+for entrance in entrances:
+    if "a King and a Queen" in entrance:
+        char_detected = ["player king", "player queen"]
+    elif "two Clowns" in entrance:
[…]

### 2022-10-13 other_scripts/1.3_preprocess_Romeo&Juliet.py

@@ -1,0 +1,183 @@
+import re
+
+import numpy as np
+import pandas as pd
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Input/output paths
+input_corpus_path = "corpora/Romeo&Juliet/Romeo&Juliet.txt"
+output_tsv_path = "corpora/Romeo&Juliet/Romeo&Juliet.tsv"
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+# Loading the corpus
+with open(input_corpus_path) as corpus_file:
+    corpus_lines = corpus_file.readlines()
+
+# Detect character
+act_presences = []
+scene_presences = []
+speaking_characters = []
+speaking_lines = []
+entrances = []
+actions = []
+for id_line, line in enumerate(corpus_lines):
+
+    # Strip line
+    line = line.strip()
+    # Detect act or scene
+    act_bool = ("ACT" in line)
+    scene_bool = ("SCENE" in line)
+    # Detect entrance
+    entrance_detect = re.search("^(Enter|Re-enter) ", line)
+    # Detect action
+    action_detect = re.search("^\[\_", line)
+    # Detect character
+    char_detect = re.search("[A-Z `'’]{3,}\.", line)
+
+    # Potential adding
+    speaking_character = ""
+    speaking_line = ""
+    entrance = ""
+    action = ""
+
+    # Check if entrance
+    if entrance_detect is not None:
+        entrance = line[entrance_detect.span()[1]:]
+    # Check if action
+    elif action_detect is not None:
+        action = line[action_detect.span()[1]:-3]
+    elif (not act_bool) and (not scene_bool):
+        if char_detect is not None:
+            speaking_character = char_detect.group()[:-1]
+            speaking_line = line[char_detect.span()[1]:]
+        else:
+            speaking_line = line
+
+    # Save results
+    act_presences.append(act_bool)
+    scene_presences.append(scene_bool)
+    speaking_characters.append(speaking_character)
+    speaking_lines.append(speaking_line)
+    entrances.append(entrance)
+    actions.append(action)
+
+# Get the characters
+unique_character = [char.lower().strip() for char in set(speaking_characters) if char != ""]
+unique_character = list(set(unique_character))
+
+# Treat entrances
+list_of_entrances = []
+for entrance in entrances:
+    if "a King and a Queen" in entrance:
+        char_detected = ["player king", "player queen"]
+    elif "two Clowns" in entrance:
+        char_detected = ["first clown", "second clown"]
+    else:
[…]

### 2022-10-13 other_scripts/1.4_preprocess_text.py

@@ -1,0 +1,47 @@
+import pandas as pd
+import spacy
+from local_functions import process_text
+from tqdm import tqdm
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/booknlp_preprocessed/candide.tsv"
+# Outfile
+output_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
+# Language ("fr" or "en")
+language = "en"
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+# Load the dataframe
+corpus_df = pd.read_csv(corpus_tsv_path, sep="\t", index_col=0)
+
+# Get the texts
+texts = corpus_df["text"]
+
+# Load the spacy model depending on language
+if language == "fr":
+    nlp = spacy.load("fr_core_news_lg")
+else:
+    nlp = spacy.load("en_core_web_lg")
+
+# Process the text
+processed_texts = []
+for text in tqdm(texts):
+    text_pp = nlp(text)
+    lemmas_pp = " ".join([word.lemma_ for word in text_pp if word.lemma_.strip() != ""])
+    processed_texts.append(process_text(lemmas_pp))
+
+# Change the text to the processed text
+corpus_df["text"] = processed_texts
+
+# Remove empty lines
+corpus_df = corpus_df[corpus_df["text"] != ""]
+
+# Save the new corpus
+corpus_df.to_csv(output_tsv_path, sep="\t")

### 2022-10-13 other_scripts/2.0_CA_lesMiserables.py

@@ -1,0 +1,353 @@
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 1
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter (0.1)
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
[…]

### 2022-10-13 other_scripts/2.1_CA_lesMiserables_Network.py

@@ -1,0 +1,190 @@
+from local_functions import *
+import pickle
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 20
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter (0.1)
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Get the main characters
+main_char_idx = np.where((corpus.occurrences >= min_occurrences).to_numpy().sum(axis=0) > 10)
+main_char_names = np.array(corpus.occurrences.columns)[main_char_idx]
[…]

### 2022-10-13 other_scripts/2.2_CA_NotreDame.py

@@ -1,0 +1,148 @@
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/NotreDame_fr/NotreDame_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 10
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 1
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
+# Make occurrences binary
[…]

### 2022-10-13 other_scripts/2.3_CA_Hamlet.py

@@ -1,0 +1,137 @@
+from local_functions import *
+from nltk.corpus import stopwords
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/Hamlet/Hamlet_tokens.tsv"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 2
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+used_stop_words = stopwords.words('english')
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns)]
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Build interactions and add them to data
+interaction_occurrences = build_directed_interactions(list(corpus.meta_variables.speaking), corpus.occurrences,
+                                                      max_interaction_degree)
+corpus.occurrences = interaction_occurrences
+
+# Make occurrences binary
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+
+# Make the occurrences across a meta
+corpus.update_occurrences_across_meta(meta_for_occurrences)
+
+# Make sure no units are empty
+corpus.remove_units_without_words()
+#corpus.remove_units_without_occurrences()
+corpus.remove_occurrences_with_frequency(1e-10)
+corpus.remove_words_with_frequency(1e-10)
+
+# Get units weights
+f_row = corpus.n_tokens / corpus.n_tokens.sum()
+
[…]

### 2022-10-13 other_scripts/2.4_CA_Romeo&Juliet.py

@@ -1,0 +1,137 @@
+from nltk.corpus import stopwords
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/Romeo&Juliet/Romeo&Juliet_tokens.tsv"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/en_fasttext.model"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 3
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+# -------------------------------
+#  Code
+# -------------------------------
+
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+used_stop_words = stopwords.words('english')
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns)]
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Build interactions and add them to data
+interaction_occurrences = build_directed_interactions(list(corpus.meta_variables.speaking), corpus.occurrences,
+                                                      max_interaction_degree)
+corpus.occurrences = interaction_occurrences
+
+# Make occurrences binary
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+
+# Make the occurrences across a meta
+corpus.update_occurrences_across_meta(meta_for_occurrences)
+
+# Make sure no units are empty
+corpus.remove_units_without_words()
+#corpus.remove_units_without_occurrences()
+corpus.remove_occurrences_with_frequency(1e-10)
+corpus.remove_words_with_frequency(1e-10)
+
+# Get units weights
+f_row = corpus.n_tokens / corpus.n_tokens.sum()
+
[…]

### 2022-10-13 other_scripts/3.0_WV_lesMiserables.py

@@ -1,0 +1,197 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 3
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 0.01
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
[…]

### 2022-10-13 other_scripts/3.1_WV_NotreDame.py

@@ -1,0 +1,197 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/NotreDame_fr/NotreDame.tsv"
+# Aliases file
+aliases_path = "corpora/NotreDame_fr/NotreDame_aliases.txt"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 1
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
[…]

### 2022-10-13 other_scripts/3.2_WV_booknlp.py

@@ -1,0 +1,168 @@
+from local_functions import *
+from gensim.models import KeyedVectors
+from nltk.corpus import stopwords
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/booknlp_preprocessed/candide_tokens.tsv"
+# Word vectors to use
+word_vectors_path = "/home/gguex/Documents/data/pretrained_word_vectors/fr_fasttext.model"
+# Set aggregation level (None for each line)
+aggregation_level = "paragraph_id"
+# Minimum occurrences for words
+min_word_frequency = 5
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 5
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+# Regularization parameter
+regularization_parameter = 1
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+used_stop_words = stopwords.words('english')
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns)]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(CountVectorizer(stop_words=used_stop_words))
+
+# Make a threshold for the minimum vocabulary and remove units without words
+corpus.remove_words_with_frequency(min_word_frequency)
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
+# Make occurrences binary
+corpus.occurrences = 1*(corpus.occurrences >= min_occurrences)
+
+# Make the occurrences across a meta
+corpus.update_occurrences_across_meta(meta_for_occurrences)
+
+# Make sure no units are empty
+corpus.remove_units_without_words()
+corpus.remove_units_without_occurrences()
[…]

### 2022-10-13 other_scripts/4.0_NMF_lesMiserables.py

@@ -1,0 +1,121 @@
+from sklearn.decomposition import NMF, LatentDirichletAllocation
+from sklearn.feature_extraction.text import TfidfVectorizer
+from local_functions import *
+
+# -------------------------------
+#  Parameters
+# -------------------------------
+
+# Corpus tsv path
+corpus_tsv_path = "corpora/LesMiserables_fr/LesMiserables_tokens.tsv"
+# Aliases file
+aliases_path = "corpora/LesMiserables_fr/LesMiserables_aliases.txt"
+# Set aggregation level (None for each line)
+aggregation_level = "chapitre"
+# Max interactions
+max_interaction_degree = 2
+# The minimum occurrences for an object to be considered
+min_occurrences = 3
+# Use a meta variable to build occurrences (None for original)
+meta_for_occurrences = None
+
+# -------------------------------
+#  Loading
+# -------------------------------
+
+# Load stopwords
+with open("aux_files/frenchST.txt") as stopwords_file:
+    used_stop_words = stopwords_file.readlines()
+used_stop_words = [process_text(stop_word) for stop_word in used_stop_words]
+
+# Read aliases
+with open(aliases_path) as aliases_file:
+    aliases = aliases_file.readlines()
+aliases = {alias.split(",")[0].strip(): alias.split(",")[1].strip() for alias in aliases}
+
+# Load dataframe
+corpus = CharacterCorpus()
+corpus.load_corpus(corpus_tsv_path)
+
+# Get character names
+character_names = [process_text(character_name)
+                   for character_name in list(corpus.occurrences.columns) + list(aliases.keys())]
+
+# -------------------------------
+#  Processing
+# -------------------------------
+
+# Aggregate on the level
+corpus.aggregate_on(aggregation_level)
+
+# Construct the unit-term matrix and remove rare words
+corpus.build_units_words(TfidfVectorizer(max_df=0.95, min_df=2, max_features=2000, stop_words=used_stop_words))
+
+# Remove characters from words
+corpus.remove_words(character_names)
+
+# Build interactions and add them to data
+interaction_occurrences = build_interactions(corpus.occurrences, max_interaction_degree)
+corpus.occurrences = pd.concat([corpus.occurrences, interaction_occurrences], axis=1)
+
+# Make occurrences binary
[…]
